% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Aitken, Alexander C.

@article{aitken__alexander_c:16,
year={1968},
author={Whittaker, J. M. and Bartlett, M. S.},
title={{A}lexander {C}raig {A}itken, 1 {A}pril 1895-3 {N}ovember 1967},
journal={Biogr. Mems. Fell. R. Soc.},
pages={1-14},
volume={14},
url={http://www.jstor.org/stable/769436},
}

@article{aitken__alexander_c:17,
year={1973},
author={Kidson, H. P.},
title={{A}lexander {C}raig {A}itken: {N}ew {Z}ealand{'}s greatest mathematician.},
journal={New Zealand Math. Mag.},
pages={129-133},
volume={10},
}

@article{aitken__alexander_c:18,
year={1995},
author={Fenton, P.},
title={{A}. {C}. {A}itken (1895-1967)},
journal={Austral. Math. Soc. Gaz.},
pages={21-23},
volume={22(1)},
}

@article{aitken__alexander_c:19,
year={1995},
author={Fenton, P.},
title={{A}lexander {C}raig {A}itken (1895-1967)},
journal={New Zealand Math. Soc. Newslett.},
pages={20-21},
}

@incollection{aitken__alexander_c:20,
year={1996},
author={Tee, G. J.},
title={{A}lexander {C}raig {A}itken, 1895-1967},
pages={11-19},
crossref={booktitle:proceedings-of-the-ac-aitken-centenary-conference},
}

@incollection{aitken__alexander_c:22,
year={1999},
author={Fenton, P. C.},
title={{A}lexander {C}raig {A}itken (1895-1967).},
pages={73-75},
crossref={booktitle:history-of-statistics-in-new-zealand},
}

@misc{aitken__alexander_c:23,
year={2002},
author={Anonymous},
title={{U}ntitled},
addendum={Former Fellows of the Royal Society of Edinburgh, 1783-2002, p. 10},
url={http://www.royalsoced.org.uk/cms/files/fellows/biographical_index/fells_indexp1.pdf},
}

@incollection{aitken__alexander_c:25,
year={2003},
author={O'Connor, J. J. and Robertson, E. F.},
title={{A}lexander {C}raig {A}itken},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Aitken.html},
}

@incollection{aitken__alexander_c:24,
year={2004},
author={Whittaker, J. M. and McConnell, A.},
title={{A}itken, {A}lexander {C}raig (1895-1967)},
crossref={booktitle:oxford-dictionary-of-national-biography-in-association-with-the-british-academy-from-the-earliest-times-to-the-year-2000},
url={http://www.oxforddnb.com/view/article/30357},
}

@incollection{aitken__alexander_c:21,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@book{aitken__alexander_c:28,
year={1963},
author={Aitken, A. C.},
title={{G}allipoli to the {S}omme: {R}ecollections of a {N}ew {Z}ealand {I}nfantryman},
publisher={Oxford Univ. Press},
}

@book{aitken__alexander_c:29,
year={1995},
author={Aitken, A. C.},
title={{T}o {C}atch the {S}pirit: {T}he {M}emoir of {A}. {C}. {A}itken, with a biographical introduction by {P}. {C}. {F}enton.},
publisher={Univ. Otago Press},
}

@misc{aitken__alexander_c:102117,
year={1967},
author={Anonymous},
title={{U}ntitled},
addendum={The Times, Nov. 6, 1967, p. 10g; Nov. 7, 1967, p. 12h; Nov. 22, 1967, p. 12h},
}

@misc{aitken__alexander_c:26,
year={1966},
author={Edinburgh University Senate},
title={{E}dinburgh{'}s tribute to {A}. {C}. {A}itkin},
publisher={The MacTutor History of Mathematics archive},
url={http://www.gap-system.org/~history/Extras/Edinburgh_Aitken_tribute.html},
}

@article{aitken__alexander_c:9,
year={1968},
author={Silverstone, H.},
title={{A}lexander {C}raig {A}itken, {M}.{A}., {D}.{S}c., {L}{I}.{D}., {F}.{R}.{S}.{E}., {F}.{R}.{S}. (1895-1967)},
journal={J. Roy. Statist. Soc. Ser. A},
pages={259-261},
volume={131},
url={http://www.jstor.org/stable/2343867},
}

@article{aitken__alexander_c:11,
year={1968},
author={Copson, E. T. and Kendall, D. G. and Miller, J. C. P. and Ledermann, W.},
title={{A}. {C}. {A}itken},
journal={Proc. Edinburgh Math. Soc. (2)},
pages={151-176},
volume={16},
}
\end{filecontents}

\begin{document}

\Name{Aitken, Alexander C.} \Deceased
\ID{aitken__alexander_c}
\AltID{aitken__alexander}



\DOB{1895-04-01}
\DOD{1967-11-03}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Alexander_Aitken}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/aitken.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=23845}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:aitken.alexander-craig}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=18577}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/53958568}{Microsoft Academic: Aitken, A. C.}


\subsection*{Education}
\Degree{1925}{D.Sc.}{University of Edinburgh}[Smoothing Of Data]<http://genealogy.math.ndsu.nodak.edu/id.php?id=18577>


\subsection*{Honors}
\Honor{1925}{The Royal Society of Edinburgh, Fellow}
\Honor{1936}{The Royal Society, Fellow}
\Honor{1947}{IMS Fellow}
\Honor{1964}{The Royal Society of Literature, Fellow}


\subsection*{Biographies}
\Biography{aitken__alexander_c:16}
\Biography{aitken__alexander_c:17}
\Biography{aitken__alexander_c:18}
\Biography{aitken__alexander_c:19}
\Biography{aitken__alexander_c:20}
\Biography{aitken__alexander_c:22}
\Biography{aitken__alexander_c:23}
\Biography{aitken__alexander_c:25}
\Biography{aitken__alexander_c:24}
\Biography{aitken__alexander_c:21}


\subsection*{Memoirs}
\Memoir{aitken__alexander_c:28}
\Memoir{aitken__alexander_c:29}


\subsection*{Obituary}
\Obituary{aitken__alexander_c:102117}


\subsection*{Memorials}
\InMemoriam{aitken__alexander_c:26}
\InMemoriam{aitken__alexander_c:9}
\InMemoriam{aitken__alexander_c:11}
\end{document}