\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Akaike, Hirotugu

@article{akaike__hirotugu:13,
year={1995},
author={Findley, D. F. and Parzen, E.},
title={{A} conversation with {H}irotugu {A}kaike},
journal={Statist. Sci.},
pages={104-117},
volume={10},
}

@article{akaike__hirotugu:14,
year={2008},
author={Kitagawa, G.},
title={{C}ontributions of {P}rofessor {H}irotugu {A}kaike in statistical science},
journal={J. Japan Statist. Soc.},
pages={119-130},
volume={38},
}

@article{akaike__hirotugu:1234,
year={2011},
author={Kitagawa, Genshiro},
title={{C}ontribution of {P}rof. {H}. {A}kaike to statistical modeling of complex systems},
}

@article{akaike__hirotugu:7,
year={2010},
author={Tong, H.},
title={{H}irotugu {A}kaike, 1927-2009},
journal={IMS Bulletin},
pages={9},
volume={39(5)},
}

@article{akaike__hirotugu:8,
year={2010},
author={Tong, H.},
title={{P}rofessor {H}irotugu {A}kaike, 1927-2009},
journal={J. Roy. Statist. Soc. Ser. A},
pages={451-454},
volume={173},
}

@article{akaike__hirotugu:9,
year={2010},
author={Kitagawa, G.},
title={{I}n memory of {H}irotugu {A}kaike},
journal={Eur. J. Control},
pages={307-308},
volume={16},
}

@article{akaike__hirotugu:10,
year={2010},
author={Konishi, S. and Kitagawa, G.},
title={{P}reface: {S}pecial issue in honor of {D}r. {H}irotugu {A}kaike},
journal={Ann. Inst. Statist. Math.},
pages={1-2},
volume={62},
}

@misc{akaike__hirotugu:238061,
year={2011},
author={Anonymous},
title={{U}ntitled},
}
\end{filecontents}

\begin{document}

\Name{Akaike, Hirotugu}
\DOB{1927-11-05}
\DOD{2009-08-04}


\subsection*{Honors}
\Honor{1988}{IMS Fellow}
\Honor{2006}{Kyoto Prize}


\subsection*{Biographies}
\Biography{akaike__hirotugu:13}
\Biography{akaike__hirotugu:14}
\Biography{akaike__hirotugu:1234}


\subsection*{Memorials}
\InMemoriam{akaike__hirotugu:7}
\InMemoriam{akaike__hirotugu:8}
\InMemoriam{akaike__hirotugu:9}
\InMemoriam{akaike__hirotugu:10}
\InMemoriam{akaike__hirotugu:238061}
\end{document}