\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Anderson, Oskar J. V.

@incollection{anderson__oskar:13,
year={1968},
author={Fels, E. M.},
title={{A}nderson, {O}skar {N}.},
crossref={booktitle:international-encyclopedia-of-the-social-sciences},
}

@incollection{anderson__oskar:14,
year={1978},
author={Fels, E. M.},
title={{A}nderson, {O}skar {N}.},
pages={1-3},
crossref={booktitle:international-encyclopedia-of-statistics},
}

@inwebcollection{anderson__oskar:20,
year={2000},
author={O'Connor, J. J. and Robertson, E. F.},
title={{O}skar {J}ohann {V}iktor {A}nderson},
note={MacTutor biography},
}

@incollection{anderson__oskar:16,
year={2001},
author={Strecker, H. and Strecker, R.},
title={{O}skar {A}nderson},
pages={377-381},
crossref={booktitle:statisticians-of-the-centuries},
}

@incollection{anderson__oskar:15,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@incollection{anderson__oskar:17,
year={2008},
author={Sheynin, O. B.},
title={{A}nderson, {O}skar {J}ohann {V}iktor},
pages={154-155},
volume={1},
crossref={booktitle:complete-dictionary-of-scientific-biography},
}

@incollection{anderson__oskar:18,
year={2008},
author={Strecker, H. L.},
title={{A}nderson, {O}skar {N}ikolayevich (1887-1960).},
crossref={booktitle:new-palgrave-dictionary-of-economics},
}

@misc{anderson__oskar:19,
year={year?},
author={Anonymous},
title={{O}skar {A}nderson},
publisher={Kiel {U}niversity},
booktitle={Famous {S}cholars from {K}iel},
}

@article{anderson__oskar:10,
year={1960},
author={Sagaroff, S. and Isserlis, L.},
title={{O}skar {A}nderson, 1887-1960},
journal={J. Roy. Statist. Soc. Ser. A},
pages={518-519},
volume={123},
}

@article{anderson__oskar:12,
year={1960},
author={Sagaroff, S.},
title={{N}achruf f\"{u}r {O}skar {A}nderson},
journal={Metrika},
pages={89-94},
volume={3},
}

@article{anderson__oskar:8,
year={1961},
author={Wold, H.},
title={{O}skar {A}nderson, 1887-1960},
journal={Ann. Math. Statist.},
pages={651-660},
volume={32},
}

@article{anderson__oskar:9,
year={1961},
author={Tintner, G.},
title={{T}he statistical work of {O}skar {A}nderson. {J}.},
journal={Amer. Statist.},
pages={273-280},
volume={56},
}

@article{anderson__oskar:11,
year={1961},
author={Fels, E.},
title={{O}skar {A}nderson, 1887-1960},
journal={Econometrica},
pages={74-79},
volume={29},
}
\end{filecontents}

\begin{document}

\subsection*{Honors}
\Honor{1957}{IMS Fellow}


\subsection*{Biographies}
\Biography{anderson__oskar:13}
\Biography{anderson__oskar:14}
\Biography{anderson__oskar:20}
\Biography{anderson__oskar:16}
\Biography{anderson__oskar:15}
\Biography{anderson__oskar:17}
\Biography{anderson__oskar:18}
\Biography{anderson__oskar:19}


\subsection*{Memorials}
\InMemoriam{anderson__oskar:10}
\InMemoriam{anderson__oskar:12}
\InMemoriam{anderson__oskar:8}
\InMemoriam{anderson__oskar:9}
\InMemoriam{anderson__oskar:11}
\end{document}