% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Anscombe, Francis J.

@incollection{anscombe__francis_j:13,
year={2006},
author={Brillinger, D. R.},
title={{A}nscombe, {F}rancis {J}ohn},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@misc{anscombe__francis_j:517314,
year={2001},
author={Anonymous},
title={{U}ntitled},
addendum={Francis John Anscombe, 83, mathematician and professor. The New York Times, Oct. 25, 2001},
}

@misc{anscombe__francis_j:215993,
year={2001},
author={Anonymous},
title={{U}ntitled},
addendum={In Memoriam: Professor Francis John Anscombe. Yale Office of Public Affairs and Communications, Oct. 23, 2001},
url={http://opac.yale.edu/news/article.aspx?id=5247},
}

@article{anscombe__francis_j:10,
year={2002},
author={Anscombe, F. R. and Anscombe, P.},
title={{U}ntitled},
journal={IMS Bulletin},
pages={17},
volume={31(1)},
}

@article{anscombe__francis_j:11,
year={2003},
author={Cox, D. R.},
title={{F}rank {A}nscombe},
journal={J. Roy. Statist. Soc. Ser. D},
pages={679-680},
volume={52},
url={http://www.jstor.org/stable/4128135},
}
\end{filecontents}

\begin{document}

\Name{Anscombe, Francis J.} \Deceased
\ID{anscombe__francis_j}
\AltID{anscombe__francis}

\DisplayName{Anscombe, Francis}


\DOB{1918-05-13}
\DOD{2001-10-17}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Francis_Anscombe}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/anscombe.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=26375}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:anscombe.francis-john}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=62936}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/12763083}{Microsoft Academic: Anscombe, F. J.}
\Profile{http://en.wikipedia.org/wiki/F.J._Anscombe}{Wikipedia}


\subsection*{Education}
\Degree{1943}{M.A.}{University of Cambridge}<http://genealogy.math.ndsu.nodak.edu/id.php?id=62936>


\subsection*{Honors}
\Honor{1951}{IMS Fellow}
\Honor{1982}{R. A. Fisher Lecturer}


\subsection*{Biography}
\Biography{anscombe__francis_j:13}


\subsection*{Obituaries}
\Obituary{anscombe__francis_j:517314}
\Obituary{anscombe__francis_j:215993}


\subsection*{Memorials}
\InMemoriam{anscombe__francis_j:10}
\InMemoriam{anscombe__francis_j:11}
\end{document}