% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Asmussen, Søren

@misc{asmussen__soren:776183,
year={2011},
author={Anonymous},
title={{U}ntitled},
addendum={Glynn, P., Mikosch, T., Rolski, T., and Rubinstein, R. (2011). S{\o}ren Asmussen. In New Frontiers in Applied Probability: A Festschrift for S{\o}ren Asmussen (P. Glynn, T. Mikosch, and T. Rolski, eds.) pp. vii-ix. Applied Probability Trust, Sheffield, England},
}

@misc{asmussen__soren:462124,
year={2011},
author={Anonymous},
title={{U}ntitled},
addendum={Glynn, P., Mikosch, T., and Rolski, T., eds. (2011). New Frontiers in Applied Probability: A Festschrift for S{\o}ren Asmussen. Applied Probability Trust, Sheffield, England},
}
\end{filecontents}

\begin{document}

\Name{Asmussen, S{\o}ren}
\ID{asmussen__soren}




\Homepage{http://home.imf.au.dk/asmus/}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=191110}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:asmussen.soren}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=44815}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/53783434}{Microsoft Academic: Asmussen, Soren}
\Profile{http://academic.research.microsoft.com/Author/1584562}{Microsoft Academic: Asmussen, S{\o}ren}


\subsection*{Education}
\Degree{1977}{Ph.D.}{K{\o}benhavns Universitet}<http://genealogy.math.ndsu.nodak.edu/id.php?id=44815>


\subsection*{Honors}
\Honor{2003}{IMS Fellow}{For leadership and distinction in research within applied probability and statistics as well as editorial service to the profession}
\Honor{2010}{John von Neumann Theory Prize}


\subsection*{Biography}
\Biography{asmussen__soren:776183}


\subsection*{Festschrift}
\Festschrift{asmussen__soren:462124}
\end{document}