% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Banerjee, Kali S.

@article{banerjee__k_s:8,
year={2002},
author={Sinha, B. K.},
title={{K}ali {S}hankar {B}anerjee, 1914-2002},
journal={IMS Bulletin},
pages={10},
volume={31(4)},
}

@misc{banerjee__k_s:304515,
year={2002},
author={Anonymous},
title={{U}ntitled},
addendum={Sinha, B. K. (2002). Kali S. Banerjee (1914-2002). International Statistical Institute Newsletter, Vol. 26(3), p. 7},
}

@misc{banerjee__k_s:377417,
year={2002},
author={Anonymous},
title={{U}ntitled},
addendum={Kali S. Banerjee. UDaily, University of Delaware, Jul. 17,2002},
url={http://www.udel.edu/PR/UDaily/01-02/banerjee.html},
}

@misc{banerjee__k_s:497021,
year={2002},
author={Anonymous},
title={{U}ntitled},
addendum={Sinha, B. K. (2002). Kali Shankar Banerjee. IMS Bulletin, Vol. 31(4), p. 10},
}
\end{filecontents}

\begin{document}

\Name{Banerjee, Kali S.} \Deceased
\ID{banerjee__k_s}
\AltID{banerjee__k}

\DisplayName{Banerjee, K. S.}


\DOB{1914-09-17}
\DOD{2002-04-09}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Kali_S._Banerjee}{Wikipedia}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=30505}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:banerjee.kali-s}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=43898}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/53010343}{Microsoft Academic: Banerjee, K. S.}
\Profile{http://academic.research.microsoft.com/Author/54244912}{Microsoft Academic: Banerjee, Kali S.}
\Profile{http://academic.research.microsoft.com/Author/54244911}{Microsoft Academic: Banerjee, K. S.}


\subsection*{Education}
\Degree{year?}{Ph.D.}{}<http://genealogy.math.ndsu.nodak.edu/id.php?id=43898>


\subsection*{Honors}
\Honor{1970}{IMS Fellow}


\subsection*{Memorials}
\InMemoriam{banerjee__k_s:8}
\InMemoriam{banerjee__k_s:304515}
\InMemoriam{banerjee__k_s:377417}
\InMemoriam{banerjee__k_s:497021}
\end{document}