% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Barnard, George A.

@article{barnard__george_a:13,
year={1988},
author={DeGroot, M. H.},
title={{A} conversation with {G}eorge {A}. {B}arnard},
journal={Statist. Sci.},
pages={196-212},
volume={3},
url={http://www.jstor.org/stable/2245568},
}

@incollection{barnard__george_a:14,
year={2005},
author={Lindley, D. V.},
title={{B}arnard, {G}eorge {A}lfred},
crossref={booktitle:encyclopedia-of-biostatistics},
}

@misc{barnard__george_a:169312,
year={2002},
author={Lindley, D.},
title={{G}eorge {B}arnard, anti-establishment statistician concerned with quality control},
addendum={The Guardian, Aug. 9, 2002},
}

@misc{barnard__george_a:163624,
year={2002},
author={Anonymous},
title={{P}rofessor {G}eorge {B}arnard},
addendum={The Times, Aug. 16, 2002},
}

@article{barnard__george_a:10,
year={2002},
author={Lindley, D. V.},
title={{U}ntitled},
journal={IMS Bulletin},
pages={8},
volume={31(5)},
}

@article{barnard__george_a:11,
year={2003},
author={Lindley, D. V.},
title={{P}rofessor {G}eorge {A}. {B}arnard, 1915-2002},
journal={J. Roy. Statist. Soc. Ser. D},
pages={231-234},
volume={52},
url={http://www.jstor.org/stable/4128249},
}
\end{filecontents}

\begin{document}

\Name{Barnard, George A.} \Deceased
\ID{barnard__george_a}
\AltID{barnard__george}

\DisplayName{Barnard, George}


\DOB{1915-09-23}
\DOD{2002-08-09}
\DOD{2002-07-30}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/George_Alfred_Barnard}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/barnard.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=31350}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:barnard.george-a}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=82303}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/12884931}{Microsoft Academic: Barnard, George A.}
\Profile{http://academic.research.microsoft.com/Author/52859646}{Microsoft Academic: Barnard, G. A.}


\subsection*{Education}
\Degree{1936}{Princeton}{University}<http://genealogy.math.ndsu.nodak.edu/id.php?id=82303>


\subsection*{Honors}
\Honor{1958}{Guy Medal in Silver}
\Honor{1959}{IMS Fellow}
\Honor{1975}{Guy Medal in Gold}
\Honor{1976}{R. A. Fisher Lecturer}


\subsection*{Biographies}
\Biography{barnard__george_a:13}
\Biography{barnard__george_a:14}


\subsection*{Obituaries}
\Obituary{barnard__george_a:169312}
\Obituary{barnard__george_a:163624}


\subsection*{Memorials}
\InMemoriam{barnard__george_a:10}
\InMemoriam{barnard__george_a:11}
\end{document}