% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Bartlett, Maurice S.

@article{bartlett__maurice_s:18,
year={1989},
author={Olkin, I.},
title={{A} conversation with {M}aurice {B}artlett},
journal={Statist. Sci.},
pages={151-163},
volume={4},
url={http://www.jstor.org/stable/2245349},
}

@article{bartlett__maurice_s:19,
year={2004},
author={Whittle, P.},
title={{M}aurice {S}tevenson {B}artlett, 18 {J}une 1910-8 {J}anuary 2002},
journal={Biogr. Mems. Fell. R. Soc.},
pages={15-33},
volume={50},
url={http://www.jstor.org/stable/4140507},
}

@incollection{bartlett__maurice_s:20,
year={2005},
author={Armitage, P.},
title={{B}artlett, {M}aurice {S}tevenson},
crossref={booktitle:encyclopedia-of-biostatistics},
}

@incollection{bartlett__maurice_s:21,
year={2006},
author={Whittle, P.},
title={{B}artlett, {M}aurice {S}tevenson (1910-2002)},
crossref={booktitle:oxford-dictionary-of-national-biography-in-association-with-the-british-academy-from-the-earliest-times-to-the-year-2000},
url={http://www.oxforddnb.com/view/article/76690},
}

@incollection{bartlett__maurice_s:22,
year={2006},
author={Gani, J.},
title={{B}artlett, {M}aurice {S}tevenson},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@incollection{bartlett__maurice_s:24,
year={2006},
author={Williams, R. H. and Zimmerman, D. W. and Ross, D. C. and Zumbo, B. D.},
title={{M}aurice {B}artlett: {T}ime series and multivariate statistics},
address={Raleigh, NC},
publisher={Boson Books},
}

@incollection{bartlett__maurice_s:23,
year={2011},
author={O'Connor, J. J. and Robertson, E. F.},
title={{M}aurice {S}tevenson {B}artlett},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Bartlett.html},
}

@incollection{bartlett__maurice_s:9,
year={1982},
author={Bartlett, M. S.},
title={{C}hance and change},
pages={42-60},
crossref={booktitle:making-of-statisticians},
}

@book{bartlett__maurice_s:8,
year={1975},
author={Anonymous},
title={{P}erspectives in {P}robability and {S}tatistics: {P}apers in {H}onor of {M}. {S}. {B}artlett on the {O}ccasion of his {S}ixty-fifth {B}irthday},
publisher={Applied Probability Trust},
}

@misc{bartlett__maurice_s:565927,
year={2002},
author={Whittle, P.},
title={{M}aurice {B}artlett},
addendum={The Independent, Feb. 2, 2002},
}

@article{bartlett__maurice_s:11,
year={2002},
author={Besag, J. and Clifford, P.},
title={{M}aurice {B}artlett},
journal={IMS Bulletin},
pages={15},
volume={31(3)},
}

@article{bartlett__maurice_s:12,
year={2002},
author={Gani, J.},
title={{P}rofessor {M}. {S}. {B}artlett {F}{R}{S}, 1910-2002},
journal={J. Roy. Statist. Soc. Ser. D},
pages={399-402},
volume={51},
url={http://www.jstor.org/stable/3650283},
}

@article{bartlett__maurice_s:13,
year={2002},
author={Gani, J.},
title={{M}aurice {S}tevenson {B}artlett},
journal={J. Appl. Probab.},
pages={664-670},
volume={39},
url={http://www.jstor.org/stable/3216089},
}

@misc{bartlett__maurice_s:686220,
year={2002},
author={Cox, D. R.},
title={{M}aurice {S}. {B}artlett (1910-2002)},
addendum={International Statistical Institute Newsletter, Vol. 26(2), p. 5},
}

@misc{bartlett__maurice_s:648428,
year={2002},
author={Besag, J. and Clifford, P.},
title={{M}aurice {S}. {B}artlett},
addendum={IMS Bulletin, Vol. 31(3), p. 15},
}
\end{filecontents}

\begin{document}

\Name{Bartlett, Maurice S.} \Deceased
\ID{bartlett__maurice_s}
\AltID{bartlett__maurice}

\DisplayName{Bartlett, Maurice}


\DOB{1910-06-18}
\DOD{2002-01-08}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/M._S._Bartlett}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/bartlett.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=31960}{MathSciNet}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=58066}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/50273627}{Microsoft Academic: Bartlett, M. S.}


\subsection*{Education}
\Degree{year?}{Ph.D.}{University of Cambridge}<http://genealogy.math.ndsu.nodak.edu/id.php?id=58066>


\subsection*{Honors}
\Honor{National}{Academy of Sciences, Foreign Associate}
\Honor{1945}{IMS Fellow}
\Honor{1952}{Guy Medal in Silver}
\Honor{1961}{The Royal Society, Fellow}
\Honor{1964}{R. A. Fisher Lecturer}
\Honor{1969}{Guy Medal in Gold}


\subsection*{Biographies}
\Biography{bartlett__maurice_s:18}
\Biography{bartlett__maurice_s:19}
\Biography{bartlett__maurice_s:20}
\Biography{bartlett__maurice_s:21}
\Biography{bartlett__maurice_s:22}
\Biography{bartlett__maurice_s:24}
\Biography{bartlett__maurice_s:23}


\subsection*{Autobiography}
\Autobiography{bartlett__maurice_s:9}


\subsection*{Festschrift}
\Festschrift{bartlett__maurice_s:8}


\subsection*{Obituary}
\Obituary{bartlett__maurice_s:565927}


\subsection*{Memorials}
\InMemoriam{bartlett__maurice_s:11}
\InMemoriam{bartlett__maurice_s:12}
\InMemoriam{bartlett__maurice_s:13}
\InMemoriam{bartlett__maurice_s:686220}
\InMemoriam{bartlett__maurice_s:648428}
\end{document}