\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Bartlett, Maurice S.

@article{bartlett__maurice_s:18,
year={1989},
author={Olkin, I.},
title={{A} conversation with {M}aurice {B}artlett},
journal={Statist. Sci.},
pages={151-163},
volume={4},
}

@article{bartlett__maurice_s:19,
year={2004},
author={Whittle, P.},
title={{M}aurice {S}tevenson {B}artlett, 18 {J}une 1910-8 {J}anuary 2002},
journal={Biogr. Mems. Fell. R. Soc.},
pages={15-33},
volume={50},
}

@incollection{bartlett__maurice_s:20,
year={2005},
author={Armitage, P.},
title={{B}artlett, {M}aurice {S}tevenson},
crossref={booktitle:encyclopedia-of-biostatistics},
}

@incollection{bartlett__maurice_s:21,
year={2006},
author={Whittle, P.},
title={{B}artlett, {M}aurice {S}tevenson (1910-2002)},
}

@incollection{bartlett__maurice_s:22,
year={2006},
author={Gani, J.},
title={{B}artlett, {M}aurice {S}tevenson},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@incollection{bartlett__maurice_s:24,
year={2006},
author={Williams, R. H. and Zimmerman, D. W. and Ross, D. C. and Zumbo, B. D.},
title={{M}aurice {B}artlett: {T}ime series and multivariate statistics},
address={Raleigh, NC},
publisher={Boson Books},
}

@inwebcollection{bartlett__maurice_s:23,
year={2011},
author={O'Connor, J. J. and Robertson, E. F.},
title={{M}aurice {S}tevenson {B}artlett},
note={MacTutor biography},
}

@book{bartlett__maurice_s:8,
year={1975},
author={Anonymous},
title={{P}erspectives in {P}robability and {S}tatistics: {P}apers in {H}onor of {M}. {S}. {B}artlett on the {O}ccasion of his {S}ixty-fifth {B}irthday},
publisher={Applied Probability Trust},
}

@misc{bartlett__maurice_s:565927,
year={2002},
author={Anonymous},
title={{U}ntitled},
}

@article{bartlett__maurice_s:11,
year={2002},
author={Besag, J. and Clifford, P.},
title={{M}aurice {B}artlett},
journal={IMS Bulletin},
pages={15},
volume={31(3)},
}

@article{bartlett__maurice_s:12,
year={2002},
author={Gani, J.},
title={{P}rofessor {M}. {S}. {B}artlett {F}{R}{S}, 1910-2002},
journal={J. Roy. Statist. Soc. Ser. D},
pages={399-402},
volume={51},
}

@article{bartlett__maurice_s:13,
year={2002},
author={Gani, J.},
title={{M}aurice {S}tevenson {B}artlett},
journal={J. Appl. Probab.},
pages={664-670},
volume={39},
}

@misc{bartlett__maurice_s:686220,
year={2002},
author={Anonymous},
title={{U}ntitled},
}

@misc{bartlett__maurice_s:648428,
year={2002},
author={Anonymous},
title={{U}ntitled},
}
\end{filecontents}

\begin{document}

\subsection*{Education}
\Degree{year?}{Ph.D.}{University of Cambridge}{http://genealogy.math.ndsu.nodak.edu/id.php?id=58066}


\subsection*{Honors}
\Honor{National}{Academy of Sciences, Foreign Associate}
\Honor{1945}{IMS Fellow}
\Honor{1952}{Guy Medal in Silver}
\Honor{1961}{The Royal Society, Fellow}
\Honor{1964}{R. A. Fisher Lecturer}
\Honor{1969}{Guy Medal in Gold}


\subsection*{Biographies}
\Biography{bartlett__maurice_s:18}
\Biography{bartlett__maurice_s:19}
\Biography{bartlett__maurice_s:20}
\Biography{bartlett__maurice_s:21}
\Biography{bartlett__maurice_s:22}
\Biography{bartlett__maurice_s:24}
\Biography{bartlett__maurice_s:23}


\subsection*{Festschrift}
\Festschrift{bartlett__maurice_s:8}


\subsection*{Obituary}
\Obituary{bartlett__maurice_s:565927}


\subsection*{Memorials}
\InMemoriam{bartlett__maurice_s:11}
\InMemoriam{bartlett__maurice_s:12}
\InMemoriam{bartlett__maurice_s:13}
\InMemoriam{bartlett__maurice_s:686220}
\InMemoriam{bartlett__maurice_s:648428}
\end{document}