% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Bechhofer, Robert E.

@misc{bechhofer__robert_e:89842,
year={1996},
author={Anonymous},
title={{U}ntitled},
addendum={Obituary. Cornell Chronicle, May 23, 1996},
url={http://www.news.cornell.edu/chronicle/96/5.23.96/Bechhofer.html},
}

@article{bechhofer__robert_e:8,
year={1996},
author={Olkin, I. and Santner, T. J. and Tamhane, A. C.},
title={{R}obert {E}ric {B}echhofer: 1919-1996},
journal={IMS Bulletin},
pages={488-489},
volume={25},
}

@article{bechhofer__robert_e:9,
year={2009},
author={Goldsman, D.},
title={{S}ome personal thoughts on {R}obert {E}. {B}echhofer (1919-1996)},
journal={Amer. J. Math. Management Sci.},
pages={5-14},
volume={29},
}
\end{filecontents}

\begin{document}

\Name{Bechhofer, Robert E.} \Deceased
\ID{bechhofer__robert_e}
\AltID{bechhofer__robert}

\DisplayName{Bechhofer, Robert}


\DOB{1919-03-11}
\DOD{1996-05-13}


\subsection*{Profiles}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/bechhofer.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=33265}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:bechhofer.robert-e}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=85681}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/1240134}{Microsoft Academic: Bechhofer, Robert E.}


\subsection*{Education}
\Degree{year?}{?type?}{?school?}<http://genealogy.math.ndsu.nodak.edu/id.php?id=85681>


\subsection*{Honors}
\Honor{1961}{IMS Fellow}


\subsection*{Obituaries}
\Obituary{bechhofer__robert_e:89842}
\Obituary{bechhofer__robert_e:8}


\subsection*{In Memoriam}
\InMemoriam{bechhofer__robert_e:9}
\end{document}