% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Bhattacharya, Rabindra N.

@misc{bhattacharya__r_n:88712,
year={2003},
author={Athreya, K. and Majumdar, M. and Puri, M. and Waymire, E.},
title={{P}reface},
addendum={Probability, Statistics and Their Applications: Papers in Honor of Rabi Bhattacharya. Lecture Notes-Monograph Series, Vol. 41, pp. vii-viii. Institute of Mathematical Statistics, Beachwood, OH},
url={http://www.jstor.org/stable/4356202},
}

@misc{bhattacharya__r_n:170682,
year={2003},
author={Athreya, K. and Majumdar, M. and Puri, M. and Waymire, E.},
title={{P}robability, {S}tatistics and {T}heir {A}pplications: {P}apers in {H}onor of {R}abi {B}hattacharya.},
addendum={Lecture Notes-Monograph Series, Vol. 41. Institute of Mathematical Statistics, Beachwood, OH},
url={http://www.jstor.org/stable/i397632},
}
\end{filecontents}

\begin{document}

\Name{Bhattacharya, Rabindra N.}
\ID{bhattacharya__r_n}
\AltID{bhattacharya__r}

\DisplayName{Bhattacharya, R. N.}


\Homepage{http://math.arizona.edu/~rabi/}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=36460}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:bhattacharya.rabi-n}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=9687}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/12754338}{Microsoft Academic: Bhattacharya, Rabi N.}
\Profile{http://academic.research.microsoft.com/Author/52576615}{Microsoft Academic: Bhattacharya, R. N.}


\subsection*{Education}
\Degree{1967}{Ph.D.}{The University of Chicago}[Berry-Esseen Bounds for the Multi-Dimensional Central Limit Theorem]<http://genealogy.math.ndsu.nodak.edu/id.php?id=9687>


\subsection*{Honors}
\Honor{1979}{IMS Fellow}
\Honor{1996}{IMS Medallion Lecturer}


\subsection*{Biography}
\Biography{bhattacharya__r_n:88712}


\subsection*{Festschrift}
\Festschrift{bhattacharya__r_n:170682}
\end{document}