% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Birnbaum, Allan

@incollection{birnbaum__allan:12,
year={1978},
author={Lindley, D. V.},
title={{B}irnbaum, {A}llan},
pages={22-24},
crossref={booktitle:international-encyclopedia-of-statistics},
}

@incollection{birnbaum__allan:13,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@article{birnbaum__allan:7,
year={1977},
author={Anonymous},
title={{U}ntitled},
journal={IMS Bulletin},
pages={63},
volume={6},
}

@article{birnbaum__allan:8,
year={1977},
author={Godambe, V. P.},
title={{A}llan {B}irnbaum, 1923-1976},
journal={Amer. Statist.},
pages={178-179},
volume={31},
url={http://www.jstor.org/stable/2683544},
}

@article{birnbaum__allan:9,
year={1977},
author={Norton, B.},
title={{A}llan {D}. {B}irnbaum, 1923-1976},
journal={J. Roy. Statist. Soc. Ser. A},
pages={564-565},
volume={140},
url={http://www.jstor.org/stable/2345308},
}

@article{birnbaum__allan:10,
year={1977},
author={Giere, R. N.},
title={{A}llan {B}irnbaum{'}s conception of statistical evidence},
journal={Synthese},
pages={5-13},
volume={36},
url={http://www.jstor.org/stable/20115210},
}

@article{birnbaum__allan:11,
year={1982},
author={Barnard, G. A. and Godambe, V. P.},
title={{A}llan {B}irnbaum 1923-1976},
journal={Ann. Math. Statist.},
pages={1033-1039},
volume={10},
url={http://www.jstor.org/stable/2240706},
}
\end{filecontents}

\begin{document}

\Name{Birnbaum, Allan} \Deceased
\ID{birnbaum__allan}




\DOB{1923-05-27}
\DOD{1976-07-01}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Allan_Birnbaum}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/birnbaum.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=413961}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:birnbaum.allan}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=33041}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/18725131}{Microsoft Academic: Birnbaum, Allan}


\subsection*{Education}
\Degree{1954}{Ph.D.}{Columbia University}[Characterizations of Complete Classes of Tests of Some Multiparametric Hypotheses, with Applications to Likelihood Ratio Tests]<http://genealogy.math.ndsu.nodak.edu/id.php?id=33041>


\subsection*{Honors}
\Honor{1956}{IMS Fellow}


\subsection*{Biographies}
\Biography{birnbaum__allan:12}
\Biography{birnbaum__allan:13}


\subsection*{Death Notice}
\DeathNotice{birnbaum__allan:7}


\subsection*{Memorials}
\InMemoriam{birnbaum__allan:8}
\InMemoriam{birnbaum__allan:9}
\InMemoriam{birnbaum__allan:10}
\InMemoriam{birnbaum__allan:11}
\end{document}