% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Birnbaum, Z. William

@article{birnbaum__z_william:14,
year={1990},
author={Marshall, A. W.},
title={{A} conversation with {Z}. {W}illiam {B}irnbaum},
journal={Statist. Sci.},
pages={227-241},
volume={5},
url={http://www.jstor.org/stable/2245685},
}

@misc{birnbaum__z_william:16,
year={2000},
author={Anonymous},
title={{U}ntitled},
addendum={Biographical note, Guide to the Zygmunt William Birnbaum Papers, 1920-2000. Special Collections Division, University Libraries, University of Washington},
url={http://digital.lib.washington.edu/findingaids/view?docId=UA19_14_5266BirnbaumZygmunt.xml},
}

@misc{birnbaum__z_william:15,
year={2001},
author={Woyczy\'{n}ski, W. A.},
title={{S}eeking {B}irnbaum, or nine lives of a mathematician},
addendum={English version of Polish original in Wiadom. Mat., Vol. 33 (1997), pp. 137-154.},
journal={Math. Intelligencer},
pages={36-46},
volume={23(2)},
}

@incollection{birnbaum__z_william:17,
year={2011},
author={O'Connor, J. J. and Robertson, E. F.},
title={{Z}ygmunt {W}illiam {B}irnbaum},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Birnbaum.html},
}

@misc{birnbaum__z_william:18,
year={year?},
author={Birnbaum, William Z.},
title={{U}ntitled},
addendum={Zygmunt William Birnbaum Papers, 5266-001. Special Collections Division, University Libraries, University of Washington},
}

@misc{birnbaum__z_william:19,
year={year?},
author={Birnbaum, William Z.},
title={{U}ntitled},
addendum={Zygmunt William Birnbaum Photograph Collection, 679. Special Collections Division, University Libraries, University of Washington},
}

@incollection{birnbaum__z_william:8,
year={1982},
author={Birnbaum, Z. W.},
title={{F}rom pure mathematics to applied statistics},
pages={76-82},
crossref={booktitle:making-of-statisticians},
}

@article{birnbaum__z_william:9,
year={2001},
author={Anonymous},
title={{U}ntitled},
journal={Notices Amer. Math. Soc.},
pages={513},
volume={48},
}

@article{birnbaum__z_william:10,
year={2001},
author={Marshall, A. W. and Pyke, R. and Saunders, S. C.},
title={{Z}. {W}. ({B}ill) {B}irnbaum},
journal={IMS Bulletin},
pages={83-85},
volume={30},
}

@misc{birnbaum__z_william:564151,
year={2001},
author={Marshall, A. W. and Pyke, R. and Saunders, S. C.},
title={{Z}. {W}. {B}irnbaum (1903-2000)},
addendum={Department of Mathematics, University of Washington},
url={http://www.math.washington.edu/~sheetz/Obituaries/content_zwbirnbaum.html},
}
\end{filecontents}

\begin{document}

\Name{Birnbaum, Z. William} \Deceased
\ID{birnbaum__z_william}
\AltID{birnbaum__z}

\DisplayName{Birnbaum, Z. W.}


\DOB{1903-10-18}
\DOD{2000-12-15}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=37195}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:birnbaum.zygmunt-wilhelm}{zbMATH}
\Profile{http://zbmath.org/authors/?q=ai:birnbaum.z-william}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=28292}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/2601821}{Microsoft Academic: Birnbaum, Z. W.}


\subsection*{Education}
\Degree{1929}{Ph.D.}{University of Lw\'{o}w}<http://genealogy.math.ndsu.nodak.edu/id.php?id=28292>


\subsection*{Honors}
\Honor{1949}{IMS Fellow}
\Honor{1964}{IMS President}
\Honor{1984}{Samuel S. Wilks Award}


\subsection*{Biographies}
\Biography{birnbaum__z_william:14}
\Biography{birnbaum__z_william:16}
\Biography{birnbaum__z_william:15}
\Biography{birnbaum__z_william:17}


\subsection*{Archives}
\Archive{birnbaum__z_william:18}
\Archive{birnbaum__z_william:19}


\subsection*{Autobiography}
\Autobiography{birnbaum__z_william:8}


\subsection*{Death Notice}
\DeathNotice{birnbaum__z_william:9}


\subsection*{Obituary}
\Obituary{birnbaum__z_william:10}


\subsection*{In Memoriam}
\InMemoriam{birnbaum__z_william:564151}
\end{document}