\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Blackwell, David H.

@article{blackwell__david_h:31,
year={1986},
author={DeGroot, M. H.},
title={{A} conversation with {D}avid {B}lackwell},
journal={Statist. Sci.},
pages={40-53},
volume={1},
}

@misc{blackwell__david_h:41,
year={1993},
author={Anonymous},
title={{B}iography packet},
}

@book{blackwell__david_h:32,
year={1996},
author={Ferguson, T. S. and Shapley, L. S. and MacQueen, J. B.},
title={{S}tatistics, {P}robability and {G}ame {T}heory: {P}apers in {H}onor of {D}avid {B}lackwell.},
pages={v-xiv},
publisher={Institute of Mathematical Statistics},
volume={30},
}

@incollection{blackwell__david_h:33,
year={1996},
author={Anonymous},
title={{D}avid {H}arold {B}lackwell},
pages={12-16},
crossref={booktitle:distinguished-african-american-scientists-of-the-20th-century},
}

@misc{blackwell__david_h:455910,
year={1996},
author={Anonymous},
title={{U}ntitled},
}

@article{blackwell__david_h:34,
year={2003},
author={Agwu, N. and Smith, L. and Barry, A.},
title={{D}r. {D}avid {H}arold {B}lackwell, {A}frican {A}merican pioneer},
journal={Math. Mag.},
pages={3-14},
volume={76},
}

@article{blackwell__david_h:35,
year={2006},
author={Brown, E. N. and Bickel, P.},
title={{P}rofile: {D}avid {B}lackwell},
journal={IMS Bulletin},
pages={8},
volume={35(9)},
}

@incollection{blackwell__david_h:36,
year={2008},
author={Albers, D. J.},
title={{D}avid {B}lackwell},
pages={14-27},
crossref={booktitle:mathematical-people-profiles-and-interviews},
}

@article{blackwell__david_h:37,
year={2008},
author={Anonymous},
title={{D}avid {B}lackwell receives {H}onorary {D}octorate from {N}{C} {S}tate {U}niversity},
journal={IMS Bulletin},
pages={2},
volume={37(2)},
}

@article{blackwell__david_h:38,
year={2008},
author={Anonymous},
title={{D}avid {B}lackwell},
journal={Amstat News},
pages={37},
volume={Mar. 2008},
}

@inwebcollection{blackwell__david_h:45,
year={2008},
author={Anonymous},
title={{D}avid {H}arold {B}lackwell},
booktitle={Mathematicians of the {A}frican {D}iaspora},
}

@article{blackwell__david_h:39,
year={2009},
author={Cattau, D.},
title={{D}avid {B}lackwell, {`}{S}uperstar.{'}},
journal={Illinois Alumni Magazine},
pages={32-34},
}

@inwebcollection{blackwell__david_h:43,
year={2009},
author={O'Connor, J. J. and Robertson, E. F.},
title={{D}avid {H}arold {B}lackwell},
note={MacTutor biography},
}

@inwebcollection{blackwell__david_h:42,
year={2010},
author={Anonymous},
title={{D}avid {H}. {B}lackwell, 1919-2010},
publisher={American {S}tatistical {A}ssociation},
booktitle={Statisticians in {H}istory},
}

@inwebcollection{blackwell__david_h:44,
year={2010},
author={Hunter, M.},
title={{B}lackwell, {D}avid {H}arold (1919-2010)},
booktitle={Online {E}ncyclopedia of {S}ignificant {P}eople and {P}laces in {A}frican {A}merican {H}istory},
}

@inwebcollection{blackwell__david_h:40,
year={2012},
author={Erhan \c{C}inlar and Jim Pitman (eds.)},
title={{D}avid {B}lackwell},
address={Berkeley, CA},
publisher={Mathematical Sciences Publishers},
}

@misc{blackwell__david_h:957373,
year={2013},
author={Bickel, Peter},
title={{B}lackwell {L}ecture},
journal={IMS Bulletin},
}

@book{blackwell__david_h:8,
year={1996},
author={Ferguson, T. S. and Shapley, L. S. and MacQueen, J. B. (eds.)},
title={{S}tatistics, {P}robability and {G}ame {T}heory: {P}apers in {H}onor of {D}avid {B}lackwell.},
publisher={Institute of Mathematical Statistics},
volume={30},
}

@book{blackwell__david_h:9,
year={1999},
author={Foster, D. P. and Levine, D. K. and Vohra, R. V.  (eds.)},
title={{L}earning in games: {A} symposium in honor of {D}avid {B}lackwell},
pages={i, 1-316},
series={Games Econom. Behav.},
volume={29},
}

@misc{blackwell__david_h:47,
year={2003},
author={Blackwell, D.},
title={{A}n oral history with {D}avid {B}lackwell. {I}nterviews conducted by {N}. {W}ilmot in 2002 and 2003.},
publisher={Regional Oral History Office, The Bancroft Library, University of California, Berkeley},
}

@misc{blackwell__david_h:48,
year={year?},
author={Anonymous},
title={{D}avid {H}arold {B}lackwell: {N}ational {V}isonary},
booktitle={National {V}isionary {L}eadership {P}roject},
}

@article{blackwell__david_h:10,
year={2010},
author={Anonymous},
title={{D}avid {B}lackwell: 1919-2010},
journal={IMS Bulletin},
pages={2},
volume={39(7)},
}

@misc{blackwell__david_h:212647,
year={2010},
author={Anonymous},
title={{U}ntitled},
}

@misc{blackwell__david_h:133033,
year={2010},
author={Anonymous},
title={{U}ntitled},
}

@misc{blackwell__david_h:458020,
year={2010},
author={Anonymous},
title={{D}avid {B}lackwell dies at 91; mathematician, {U}{C} {B}erkeley{'}s first tenured black professor.},
}

@misc{blackwell__david_h:103613,
year={2010},
author={Sanders, Robert},
title={{E}minent statistician {D}avid {B}lackwell has died at 91.},
journal={UC Berkeley News Center},
volume={Jul. 15, 2010},
}

@misc{blackwell__david_h:15,
year={2010},
author={The MAA Mathematical Sciences Digital Library, Jul. 19, 2010},
title={{N}oted mathematician {D}avid {B}lackwell has died at 91.},
}

@misc{blackwell__david_h:63388,
year={2010},
author={Anonymous},
title={{D}avid {B}lackwell fought racism; became world-famous statistician},
journal={St. Louis Post-Dispatch},
volume={Jul. 14, 2010},
}

@misc{blackwell__david_h:593009,
year={2010},
author={Anonymous},
title={{D}avid {B}lackwell.},
journal={Amstat News},
pages={38},
volume={Aug. 2010},
}

@article{blackwell__david_h:17,
year={2010},
author={Roussas, G. G.},
title={{D}avid {B}lackwell, 1919-2010},
journal={IMS Bulletin},
pages={14},
volume={39(8)},
}

@article{blackwell__david_h:18,
year={2010},
author={Lockhart, D.},
title={{D}avid {B}lackwell, 1919-2010},
journal={Bernoulli News},
volume={17(2)},
}

@misc{blackwell__david_h:499703,
year={2010},
author={Mike Orkin and Robert Pisani},
title={{R}emembering {D}avid {B}lackwell.},
}

@article{blackwell__david_h:20,
year={2011},
author={Roussas, G. G., coord. ed.},
title={{A} tribute to {D}avid {B}lackwell},
journal={Notices Amer. Math. Soc.},
pages={912-928},
volume={58},
}

@article{blackwell__david_h:21,
year={2011},
author={Swift, R.},
title={{D}avid {B}lackwell},
journal={Math. Sci.},
pages={70-71},
volume={36(1)},
}

@article{blackwell__david_h:22,
year={2011},
author={G\'{o}mez Villegas, M. A.},
title={{D}avid {H}. {B}lackwell (1919-2010)},
journal={BEIO},
pages={85-87},
volume={27},
}
\end{filecontents}

\begin{document}

\subsection*{Education}
\Education{1925--35}{Centralia Public Schools}
\Education{1935--41}{University of Illinois}
\Degree{1938}{AB}{University of Illinois}
\Degree{1939}{AM}{University of Illinois}
\Degree{1941}{Ph.D.}{Mathematics, University of Illinois at Urbana-Champaign}{Properties of Markov Chains}{http://genealogy.math.ndsu.nodak.edu/id.php?id=4209}


\subsection*{Career}
\Position{1941--42}{Rosenwald Fellow}{ Institute for Advanced Study}
\Position{1942}{(Summer)}{ Assistant Statistician OPA}
\Position{1942--43}{Instructor}{ Southern University, Baton Rouge, LA}
\Position{1943--44}{Instructor}{  Clark College, Atlanta, Georgia}
\Position{1944--46}{Assistant Professor}{ Howard University, Washington, DC}
\Position{1946--47}{Associate Professor}{ Howard University, Washington, DC}
\Position{1947--54}{Professor and Head}{ Mathematics Department Howard University, Washington, DC}
\Position{1948--50}{(Summers)}{ Mathematician, Rand Corporation}
\Position{1950--51}{Visiting Professor}{ Stanford University}
\Position{1954--55}{Visiting Professor}{ University of California, Berkeley}
\Position{1955--73}{Professor of Statistics}{ University of California, Berkeley}
\Position{1957--61}{Chairman}{ Department of Statistics, University of California, Berkeley}
\Position{1973--75}{Director}{ University of California Study Center United Kingdom and Ireland (Education Abroad Program)}
\Position{1973--2010}{Professor of Mathematics and Statistics}{ University of California, Berkeley}


\subsection*{Honors}
\Honor{1971}{Faculty Research Lecturer, University of California, Berkeley}
\HonoraryDegree{1969}{D.Sc. }{Michigan State University}
\HonoraryDegree{1971}{D.Sc. }{Southern Illinois University}
\HonoraryDegree{1980}{D.Sc. }{Carnegie-Mellon University}
\HonoraryDegree{1987}{D.Sc. }{National University of Lesotho}
\HonoraryDegree{1988}{D.Sc. }{Amherst College}
\HonoraryDegree{1988}{D.Sc. }{Harvard University}
\HonoraryDegree{1990}{D.Sc. }{Howard University}
\HonoraryDegree{1990}{D.Sc. }{Yale University}
\HonoraryDegree{1990}{D.Sc. }{University of Warwick}
\HonoraryDegree{1991}{D.Sc. }{Syracuse University}
\HonoraryDegree{1992}{D.Sc. }{University of Southern California}
\Honor{1947}{IMS Fellow}
\Honor{1961}{Rietz Lecturer}
\Honor{1965}{National Academy of Sciences, Member}
\Honor{1968}{American Academy of Arts \& Sciences, Member}
\Honor{1969}{American Academy of Arts and Sciences, Fellow}
\Honor{1976}{Wald Lecturer}
\Honor{1979}{John von Neumann Theory Prize}
\Honor{1986}{R. A. Fisher Lecturer}
\Honor{1990}{American Philosophical Society, Member}
\Honor{1974}{W. W. Rouse Ball Lecturer, University of Cambridge, UK}
\Honor{1976}{Elected Honorary Fellow, Royal Statistical Society}
\Honor{1977}{Wald Lecturer, Institute of Mathematical Statistics}
\Honor{1979}{TIMS/ORSA John Von Neumann Theory Prize}
\Honor{1986}{R.A. Fisher Award, Committee of Presidents of Statistical Societies}
\Honor{1988}{The Berkeley Citation}


\subsection*{Professional Service}
\Service{1956}{President}{Institute of Mathematical Statistics}
\Service{1968--71}{Vice-President}{American Mathematical Society}
\Service{1972--73}{Chairman}{Berkeley}
\Service{1973}{President}{International Association for Statistics in the Physical Sciences}
\Service{1975--78}{President}{Bernoulli Society for Mathematical Statistics and Probability}
\Service{1975--77}{Vice-President}{International Statistical Institute}
\Service{1978}{Vice-President}{American Statistical Association}


\subsection*{Membership}
\Member{National Academy of Sciences}
\Member{American Association for Advancement of Science}
\Member{American Academy of Arts and Sciences}
\Member{Institute of Mathematical Statistics}
\Member{American Mathematical Society}
\Member{Royal Statistical Society}
\Member{American Philosophical Society}


\subsection*{Biographies}
\Biography{blackwell__david_h:31}
\Biography{blackwell__david_h:41}
\Biography{blackwell__david_h:32}
\Biography{blackwell__david_h:33}
\Biography{blackwell__david_h:455910}
\Biography{blackwell__david_h:34}
\Biography{blackwell__david_h:35}
\Biography{blackwell__david_h:36}
\Biography{blackwell__david_h:37}
\Biography{blackwell__david_h:38}
\Biography{blackwell__david_h:45}
\Biography{blackwell__david_h:39}
\Biography{blackwell__david_h:43}
\Biography{blackwell__david_h:42}
\Biography{blackwell__david_h:44}
\Biography{blackwell__david_h:40}
\Biography{blackwell__david_h:957373}


\subsection*{Festschriften}
\Festschrift{blackwell__david_h:8}
\Festschrift{blackwell__david_h:9}


\subsection*{Oral History}
\OralHistory{blackwell__david_h:47}
\OralHistory{blackwell__david_h:48}


\subsection*{Death Notice}
\DeathNotice{blackwell__david_h:10}


\subsection*{Obituaries}
\Obituary{blackwell__david_h:212647}
\Obituary{blackwell__david_h:133033}
\Obituary{blackwell__david_h:458020}
\Obituary{blackwell__david_h:103613}
\Obituary{blackwell__david_h:15}
\Obituary{blackwell__david_h:63388}
\Obituary{blackwell__david_h:593009}


\subsection*{Memorials}
\InMemoriam{blackwell__david_h:17}
\InMemoriam{blackwell__david_h:18}
\InMemoriam{blackwell__david_h:499703}
\InMemoriam{blackwell__david_h:20}
\InMemoriam{blackwell__david_h:21}
\InMemoriam{blackwell__david_h:22}
\end{document}