% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Blumenthal, Robert M.

@misc{blumenthal__robert_m:319083,
year={2013},
author={Anonymous},
title={{U}ntitled},
addendum={Bob Blumenthal: 1931-2012 (2013). IMS Bulletin, Vol. 42(1), p. 2},
}

@misc{blumenthal__robert_m:635920,
year={2013},
author={Anonymous},
title={{U}ntitled},
addendum={(2013). Notices Amer. Math. Soc., Vol. 60, p. 626},
}

@article{blumenthal__robert_m:1,
year={2013},
author={Ronald Getoor},
title={{O}bituary: {B}ob {B}lumenthal (1931-2012)},
journal={IMS Bulletin},
url={http://bulletin.imstat.org/wp-content/uploads/Bulletin42_3.pdf},
}

@misc{blumenthal__robert_m:430405,
year={2013},
author={Anonymous},
title={{U}ntitled},
addendum={Getoor, R. (2013). Bob Blumenthal, 1931-2012. IMS Bulletin, Vol. 42(3), pp. 7,9},
}
\end{filecontents}

\begin{document}

\Name{Blumenthal, Robert M.} \Deceased
\ID{blumenthal__robert_m}
\AltID{blumenthal__robert}

\DisplayName{Blumenthal, Robert}


\DOB{1931-02-07}
\DOD{2012-11-08}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=191743}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:blumenthal.robert-m}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=1863}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/10536719}{Microsoft Academic: Blumenthal, R. M.}
\Profile{http://academic.research.microsoft.com/Author/54986147}{Microsoft Academic: Blumenthal, R. M.}


\subsection*{Education}
\Degree{1956}{Ph.D.}{Cornell University}[An Extended Markov Property]<http://genealogy.math.ndsu.nodak.edu/id.php?id=1863>


\subsection*{Honors}
\Honor{1970}{IMS Fellow}


\subsection*{Death Notices}
\DeathNotice{blumenthal__robert_m:319083}
\DeathNotice{blumenthal__robert_m:635920}


\subsection*{Obituary}
\Obituary{blumenthal__robert_m:1}


\subsection*{In Memoriam}
\InMemoriam{blumenthal__robert_m:430405}
\end{document}