% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Bose, Raj Chandra

@misc{bose__r_c:733357,
year={1959},
author={Anonymous},
title={{U}ntitled},
addendum={Osmundsen, J. A. Major mathematical conjecture propounded 177 years ago is disproved; 3 mathematicians solve old puzzle. The New York Times, Apr. 26, 1959, pp. 1, 42},
}

@incollection{bose__r_c:20,
year={1973},
author={Bush, K. A.},
title={{B}ose as teacher---the early years},
pages={79-80},
crossref={booktitle:survey-of-combinatorial-theory},
}

@article{bose__r_c:21,
year={1982},
author={Frisinger, H. H.},
title={{R}aj {C}handra {B}ose: {U}niversal mathematician},
journal={Ga\c{n}ita Bh\={a}rat\={i}},
pages={83-89},
volume={4(3-4)},
}

@article{bose__r_c:24,
year={1998},
author={Shrikande, S. S.},
title={{R}. {C}. {B}ose memorial conference, {F}ort {C}ollins, {C}olorado; my reminiscences of {P}rofessor {R}. {C}. {B}ose and disproof of {E}uler{'}s conjecture},
journal={J. Statist. Plann. Inference},
pages={273-276},
volume={73},
}

@article{bose__r_c:25,
year={2003},
author={Yogananda, C. S.},
title={{R}aj {C}handra {B}ose (1901-1987)},
journal={Resonance},
pages={51},
volume={8(9)},
}

@incollection{bose__r_c:22,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@incollection{bose__r_c:23,
year={2011},
author={O'Connor, J. J. and Robertson, E. F.},
title={{R}aj {C}handra {B}ose},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Bose_Raj.html},
}

@article{bose__r_c:29,
year={2006},
author={Ray-Chaudhuri, D. K. and Rao, A. R. and Roy, B., eds.},
title={{R}. {C}. {B}ose {C}entennial {S}ymposium on {D}iscrete {M}athematics and {A}pplications},
addendum={Foreword by editors on p. 1463},
journal={Discrete Math.},
pages={1463-1636},
volume={306},
}

@incollection{bose__r_c:28,
year={1983},
author={Bose, R. C.},
title={{T}he early years; the middle years; the later years; recollections},
publisher={Pfizer, {U}niversity of {C}onnecticut-{S}torrs and {A}merican {S}tatistical {A}ssociation},
volume={D{S}005; {D}{S}006; {D}{S}007; {D}{S}008},
booktitle={Distinguished {S}tatistician {V}ideo {S}eries},
url={http://www.amstat.org},
}

@article{bose__r_c:9,
year={1988},
author={Anonymous},
title={{R}aj {C}handra {B}ose, 1901-1987},
journal={IMS Bulletin},
pages={50-52},
volume={17},
}

@article{bose__r_c:10,
year={1987},
author={Chatterjee, S. K. and Adhikary, B.},
title={{P}rofessor {R}. {C}. {B}ose: 1901-1987},
journal={Calcutta Statist. Assoc. Bull.},
pages={109-124},
volume={36},
}

@article{bose__r_c:11,
year={1988},
author={Boes, D. C. and Johnson, N. L. and Kuebler, R. R.},
title={{R}aj {C}handra {B}ose, 1901-1987},
journal={IMS Bulletin},
pages={50-51},
volume={17},
}

@article{bose__r_c:12,
year={1988},
author={Anonymous},
title={{R}aj {C}handra {B}ose (1901-1987)},
journal={Sankhy\={a}},
pages={4-6},
volume={50},
url={http://www.jstor.org/stable/25052518},
}

@article{bose__r_c:13,
year={1988},
author={Anonymous},
title={{P}rofessor {R}aj {C}handra {B}ose},
journal={J. Geom.},
pages={1-2},
volume={33},
}

@article{bose__r_c:14,
year={1990},
author={Draper, N. L.},
title={{R}aj {C}handra {B}ose},
journal={J. Roy. Statist. Soc. Ser. A},
pages={98-99},
volume={153},
url={http://www.jstor.org/stable/2983099},
}

@article{bose__r_c:15,
year={1992},
author={Nandi, P.},
title={{B}ose memorial session},
journal={Sankhy\={a}},
pages={i-viii},
volume={54},
}
\end{filecontents}

\begin{document}

\Name{Bose, Raj Chandra} \Deceased
\ID{bose__r_c}
\AltID{bose__raj}



\DOB{1901-06-19}
\DOD{1987-10-31}


\Homepage{http://en.wikipedia.org/wiki/R._C._Bose}
\Homepage{http://en.wikipedia.org/wiki/R._C._Bose}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/R._C._Bose}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/bose.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=39945}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:bose.raj-chandra}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=11936}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/54952840}{Microsoft Academic: Bose, R. C.}
\Profile{http://academic.research.microsoft.com/Author/12767786}{Microsoft Academic: Bose, R. C.}
\Profile{http://academic.research.microsoft.com/Author/23219270}{Microsoft Academic: Bose, R. C.}


\subsection*{Education}
\Degree{1947}{D.Litt.}{Calcutta University}<http://genealogy.math.ndsu.nodak.edu/id.php?id=11936>


\subsection*{Honors}
\Honor{1950}{IMS Fellow}
\Honor{1959}{Wald Lecturer}
\Honor{1972}{IMS President}
\Honor{1976}{National Academy of Sciences, Member}
\Honor{1977}{R. A. Fisher Lecturer}


\subsection*{Biographies}
\Biography{bose__r_c:733357}
\Biography{bose__r_c:20}
\Biography{bose__r_c:21}
\Biography{bose__r_c:24}
\Biography{bose__r_c:25}
\Biography{bose__r_c:22}
\Biography{bose__r_c:23}


\subsection*{Symposium}
\Symposium{bose__r_c:29}


\subsection*{DVD}
\DVD{bose__r_c:28}


\subsection*{Obituary}
\Obituary{bose__r_c:9}


\subsection*{Memorials}
\InMemoriam{bose__r_c:10}
\InMemoriam{bose__r_c:11}
\InMemoriam{bose__r_c:12}
\InMemoriam{bose__r_c:13}
\InMemoriam{bose__r_c:14}
\InMemoriam{bose__r_c:15}
\end{document}