% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Bowker, Albert H.

@article{bowker__albert_h:14,
year={1987},
author={Olkin, I.},
title={{A} conversation with {A}lbert {H}. {B}owker},
journal={Statist. Sci.},
pages={472-483},
volume={2},
url={http://www.jstor.org/stable/2245546},
}

@misc{bowker__albert_h:15,
year={1995},
author={Bowker, A.},
title={{S}ixth chancellor, {U}niversity of {C}alifornia, {B}erkeley, 1971-1980; statistician and national leader in the policies and politics of higher education},
addendum={Introduction by J. L. Hodges, interviews conducted by H. S. Nathan in 1991. University History Series. Regional Oral History Office, The Bancroft Library, University of California, Berkeley},
url={http://content.cdlib.org/ark:/13030/hb1p3001qq/},
}

@misc{bowker__albert_h:475699,
year={2008},
author={Anonymous},
title={{A}lbert {B}owker, 88, dies; ex-{C}{U}{N}{Y} head},
addendum={The New York Times, Jan. 23, 2008},
}

@misc{bowker__albert_h:104622,
year={2008},
author={Anonymous},
title={{U}{C} {B}erkeley chancellor got tough on protestors},
addendum={Los Angeles Times, Jan. 24, 2008},
}

@misc{bowker__albert_h:144638,
year={2008},
author={Anonymous},
title={{A}lbert {B}owker, innovative {U}{C} {B}erkeley chancellor during 1970s, dies at age 88},
addendum={UC Berkeley News Center, Jan. 20, 2008},
url={http://www.berkeley.edu/news/media/releases/2008/01/20_bowker.shtml},
}

@misc{bowker__albert_h:156108,
year={2008},
author={Anonymous},
title={{C}hancellor {E}meritus {A}lbert {B}owker, 1919-2008},
addendum={CUNY Newswire, The City University of New York, Jan. 22, 2008},
url={http://www1.cuny.edu/mu/forum/2008/01/22/statement-by-chairperson-schmidt-and-chancellor-goldstein},
}

@article{bowker__albert_h:12,
year={2008},
author={Anonymous},
title={{U}ntitled},
journal={Amstat News},
pages={39-40},
volume={Mar. 2008},
}
\end{filecontents}

\begin{document}

\Name{Bowker, Albert H.} \Deceased
\ID{bowker__albert_h}
\AltID{bowker__albert}

\DisplayName{Bowker, Albert}


\DOB{1919-09-18}
\DOD{2008-01-20}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=251000}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:bowker.albert-h}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=40901}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/24213959}{Microsoft Academic: Bowker, Albert H.}


\subsection*{Education}
\Degree{1949}{Ph.D.}{Columbia University}[Asymptotic Expansions for the Distribution of Certain Likelihood Ratio Statistics]<http://genealogy.math.ndsu.nodak.edu/id.php?id=40901>


\subsection*{Honors}
\Honor{1962}{IMS Fellow}
\Honor{1962}{IMS President}


\subsection*{Biography}
\Biography{bowker__albert_h:14}


\subsection*{Oral History}
\OralHistory{bowker__albert_h:15}


\subsection*{Obituaries}
\Obituary{bowker__albert_h:475699}
\Obituary{bowker__albert_h:104622}
\Obituary{bowker__albert_h:144638}


\subsection*{Memorials}
\InMemoriam{bowker__albert_h:156108}
\InMemoriam{bowker__albert_h:12}
\end{document}