% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Box, George E. P.

@incollection{box__george_e_p:11,
year={2006},
author={O'Connor, J. J. and Robertson, E. F.},
title={{G}eorge {E}dward {P}elham {B}ox},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Box.html},
}

@misc{box__george_e_p:780385,
year={2013},
author={Anonymous},
title={{U}ntitled},
addendum={Champkin, J. (2013). George Box, (1919-2013): A wit, a kind man and a statistician. Significance, Vol. 10(3)},
url={http://www.significancemagazine.org/details/magazine/4938991/George-E_-P_-Box-19192013.html},
}

@misc{box__george_e_p:36812,
year={2013},
author={Anonymous},
title={{U}ntitled},
addendum={Sakai, J. Renowned statistician George Box dies at 93. News, University of Wisconsin-Madison, Apr. 10, 2013},
url={http://www.news.wisc.edu/21662},
}

@misc{box__george_e_p:652764,
year={2013},
author={Anonymous},
title={{U}ntitled},
addendum={Abraham, B. (2013). George Edward Pelham (G. E. P.) Box-1919-2013. International Statistical Institute},
url={http://www.isi-web.org/images/membership/George},
}

@misc{box__george_e_p:501513,
year={2013},
author={Anonymous},
title={{U}ntitled},
addendum={Yandell, B., Draper, N., Abraham, B., and Fung, C. (2013). George E. P. Box, 1919-2013. IMS Bulletin, Vol. 42(5), pp. 6-7},
}
\end{filecontents}

\begin{document}

\Name{Box, George E. P.} \Deceased
\ID{box__george_e_p}
\AltID{box__george}

\DisplayName{Box, George}


\DOB{1919-10-18}
\DOD{2013-03-28}


\Homepage{http://en.wikipedia.org/wiki/G._E._P._Box}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/George_E._P._Box}{Wikipedia}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=40500}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:box.george-p}{zbMATH}
\Profile{http://zbmath.org/authors/?q=ai:box.george-e-p}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=42226}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/238911}{Microsoft Academic: Box, G. E. P.}


\subsection*{Education}
\Degree{1953}{Ph.D.}{University of London}[Departures from Independence and Homoscedastisity in the Analysis of Variance and Related Statistical Analysis]<http://genealogy.math.ndsu.nodak.edu/id.php?id=42226>


\subsection*{Honors}
\Honor{1955}{IMS Fellow}
\Honor{1964}{Guy Medal in Silver}
\Honor{1972}{Samuel S. Wilks Award}
\Honor{1974}{American Academy of Arts and Sciences, Fellow}
\Honor{1974}{R. A. Fisher Lecturer}
\Honor{1980}{IMS President}
\Honor{1981}{Rietz Lecturer}
\Honor{1985}{The Royal Society, Fellow}
\Honor{1993}{Guy Medal in Gold}


\subsection*{Biography}
\Biography{box__george_e_p:11}


\subsection*{Obituary}
\Obituary{box__george_e_p:780385}


\subsection*{Memorials}
\InMemoriam{box__george_e_p:36812}
\InMemoriam{box__george_e_p:652764}
\InMemoriam{box__george_e_p:501513}
\end{document}