% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Bradley, Ralph A.

@article{bradley__ralph_a:11,
year={2001},
author={Hollander, M.},
title={{A} conversation with {R}alph {A}. {B}radley},
journal={Statist. Sci.},
pages={75-100},
volume={16},
url={http://www.jstor.org/stable/2676781},
}

@incollection{bradley__ralph_a:12,
year={2005},
author={Billard, L.},
title={{B}radley, {R}alph {A}.},
crossref={booktitle:encyclopedia-of-biostatistics},
}

@misc{bradley__ralph_a:972315,
year={2001},
author={Anonymous},
title={{U}ntitled},
addendum={Ralph Allan Bradley. Athens Banner-Herald, Nov. 1, 2001},
}

@misc{bradley__ralph_a:900569,
year={2001},
author={Anonymous},
title={{U}ntitled},
addendum={Hollander, M. (2001). Ralph Allan Bradley, 1923-2001. Newsletter, Department of Statistics, Florida State University, Vol. 5, Fall 2001},
url={http://stat.fsu.edu/newsletter/Fall2001.pdf},
}

@article{bradley__ralph_a:9,
year={2002},
author={Hollander, M.},
title={{R}alph {A}llan {B}radley},
journal={IMS Bulletin},
pages={16},
volume={31(1)},
}

@misc{bradley__ralph_a:761566,
year={2002},
author={Anonymous},
title={{U}ntitled},
addendum={Hollander, M. (2002). IMS Bulletin, Vol. 31(1), p. 16},
}
\end{filecontents}

\begin{document}

\Name{Bradley, Ralph A.} \Deceased
\ID{bradley__ralph_a}
\AltID{bradley__ralph}

\DisplayName{Bradley, Ralph}


\DOB{1923-11-28}
\DOD{2001-10-30}


\subsection*{Profiles}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/bradley.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=40820}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:bradley.ralph-allan}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=35100}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/12752617}{Microsoft Academic: Bradley, Ralph Allan}
\Profile{http://academic.research.microsoft.com/Author/54769348}{Microsoft Academic: Bradley, Ralph A.}


\subsection*{Education}
\Degree{1949}{Ph.D.}{The University of North Carolina at Chapel Hill}[Sampling Distributions for Non-Normal Universes]<http://genealogy.math.ndsu.nodak.edu/id.php?id=35100>


\subsection*{Honors}
\Honor{1960}{IMS Fellow}


\subsection*{Biographies}
\Biography{bradley__ralph_a:11}
\Biography{bradley__ralph_a:12}


\subsection*{Obituary}
\Obituary{bradley__ralph_a:972315}


\subsection*{Memorials}
\InMemoriam{bradley__ralph_a:900569}
\InMemoriam{bradley__ralph_a:9}
\InMemoriam{bradley__ralph_a:761566}
\end{document}