% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Cambanis, Stamatis

@incollection{cambanis__stamatis:11,
year={1998},
author={Kallianpur, G. and Leadbetter, R.},
title={{S}tamatis {C}ambanis---{A} glimpse of his life and work},
pages={xi-xvi},
crossref={booktitle:stochastic-processes-and-related-topics-in-memory-of-stamatis-cambanis-1943-1995},
}

@misc{cambanis__stamatis:7,
year={1995},
author={Anonymous},
title={{U}ntitled},
addendum={Former statistics chairman Stamatis Cambanis dies. University Gazette, University of North Carolina at Chapel Hill, Apr. 19, 1995},
url={http://gazette.unc.edu/archives/95apr19/file.14.html},
}

@article{cambanis__stamatis:8,
year={1995},
author={Leadbetter, R.},
title={{S}tamatis {C}ambanis, 1943-95},
journal={IMS Bulletin},
pages={231-232},
volume={24},
}

@article{cambanis__stamatis:9,
year={1996},
author={Karatzas, I.},
title={{S}tamatis {C}ambanis (1943-1995)},
journal={J. Appl. Probab.},
pages={284},
volume={33},
url={http://www.jstor.org/stable/3215285},
}

@misc{cambanis__stamatis:143728,
year={1996},
author={Anonymous},
title={{U}ntitled},
addendum={Stamatis Cambanis '69. Princeton Alumni Weekly. Sept. 11, 1996},
url={http://paw.princeton.edu/memorials/54/33/index.xml},
}
\end{filecontents}

\begin{document}

\Name{Cambanis, Stamatis} \Deceased
\ID{cambanis__stamatis}




\DOB{1943-07-08}
\DOD{1995-04-12}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=44510}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:cambanis.stamatis}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=18740}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/2863745}{Microsoft Academic: Cambanis, Stamatis}
\Profile{http://academic.research.microsoft.com/Author/54228590}{Microsoft Academic: Cambanis, Stamatis}


\subsection*{Education}
\Degree{1969}{Ph.D.}{Princeton University}[Representations of Stochastic Processes and Some of Their Applications]<http://genealogy.math.ndsu.nodak.edu/id.php?id=18740>


\subsection*{Honors}
\Honor{1984}{IMS Fellow}


\subsection*{Biography}
\Biography{cambanis__stamatis:11}


\subsection*{Death Notice}
\DeathNotice{cambanis__stamatis:7}


\subsection*{Obituary}
\Obituary{cambanis__stamatis:8}


\subsection*{Memorials}
\InMemoriam{cambanis__stamatis:9}
\InMemoriam{cambanis__stamatis:143728}
\end{document}