% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Carver, Harry C.

@incollection{carver__harry_c:10,
year={1961},
author={Anonymous},
title={{H}arry {C}lyde {C}arver},
publisher={University of {M}ichigan},
booktitle={Faculty {H}istory {P}roject},
url={http://um2017.org/faculty-history/faculty/harry-clyde-carver/memoir},
}

@article{carver__harry_c:11,
year={1986},
author={Craig, C. C.},
title={{E}arly days in statistics at {M}ichigan},
journal={Statist. Sci.},
pages={292-293},
volume={1},
url={http://www.jstor.org/stable/2245455},
}

@incollection{carver__harry_c:14,
year={1989},
author={Kaplan, W.},
title={{M}athematics at the {U}niversity of {M}ichigan},
pages={179-189},
crossref={booktitle:century-of-mathematics-in-america-part-iii},
}

@incollection{carver__harry_c:15,
year={1989},
author={Wilder, R. L.},
title={{R}eminiscences of mathematics {M}ichigan},
pages={191-204},
crossref={booktitle:century-of-mathematics-in-america-part-iii},
}

@article{carver__harry_c:13,
year={1996},
author={Stigler, S. M.},
title={{T}he history of statistics in 1993},
addendum={see pp. 245-246},
journal={Statist. Sci.},
pages={244-252},
volume={11},
url={http://www.jstor.org/stable/2246117},
}

@misc{carver__harry_c:12,
year={year?},
author={Anonymous},
title={{I}{M}{S} awards, {H}arry {C}. {C}arver {M}edal},
addendum={Institute of Mathematical Statistics},
url={http://www.imstat.org/awards/carver.html},
}

@misc{carver__harry_c:16,
year={year?},
author={Anonymous},
title={{U}ntitled},
addendum={Arnold Air Society Squadron, University of Michigan AFROTC Detachment 390},
url={http://www.umich.edu/~det390/aas.html},
}

@article{carver__harry_c:8,
year={1977},
author={Anonymous},
title={{U}ntitled},
journal={IMS Bulletin},
pages={61},
volume={6},
}

@article{carver__harry_c:9,
year={1978},
author={Craig, C. C.},
title={{H}arry {C}. {C}arver, 1890-1977},
journal={Ann. Statist},
pages={1-4},
volume={6},
url={http://www.jstor.org/stable/2958686},
}
\end{filecontents}

\begin{document}

\Name{Carver, Harry C.} \Deceased
\ID{carver__harry_c}
\AltID{carver__harry}



\DOB{1890-12-04}
\DOD{1977-01-30}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Harry_C._Carver}{Wikipedia}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=422391}{MathSciNet}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=7600}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/47158043}{Microsoft Academic: Carver, Harry C.}


\subsection*{Education}
\Degree{1915}{B.S.}{University of Michigan}<http://genealogy.math.ndsu.nodak.edu/id.php?id=7600>


\subsection*{Honors}
\Honor{before 1943}{IMS Fellow}


\subsection*{Biographies}
\Biography{carver__harry_c:10}
\Biography{carver__harry_c:11}
\Biography{carver__harry_c:14}
\Biography{carver__harry_c:15}
\Biography{carver__harry_c:13}
\Biography{carver__harry_c:12}
\Biography{carver__harry_c:16}


\subsection*{Death Notice}
\DeathNotice{carver__harry_c:8}


\subsection*{In Memoriam}
\InMemoriam{carver__harry_c:9}
\end{document}