% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Cochran, William G.

@incollection{cochran__william_g:29,
year={1980},
author={Anonymous},
title={{W}illiam {G}. {C}ochran, 1909-1980},
publisher={American {S}tatistical {A}ssociation},
booktitle={Statisticians in {H}istory},
url={http://www.amstat.org/about/statisticiansinhistory/index.cfm?fuseaction=biosinfo&BioID=21},
}

@article{cochran__william_g:25,
year={1987},
author={Hansen, M. and Mosteller, F.},
title={{W}illiam {G}emmell {C}ochran, {J}uly 15, 1909-{M}arch 29, 1980},
journal={Biographical Memoirs},
pages={60-89},
publisher={National Academies Press},
volume={56},
url={http://books.nap.edu/html/biomems/wcochran.pdf},
}

@incollection{cochran__william_g:30,
year={1996},
author={O'Connor, J. J. and Robertson, E. F.},
title={{W}illiam {G}emmell {C}ochran},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Cochran.html},
}

@incollection{cochran__william_g:26,
year={1997},
author={Watson, G. S.},
title={{C}ochran, {W}illiam {G}emmell},
pages={188-189},
crossref={booktitle:leading-personalities-in-statistical-sciences-from-the-17th-century-to-the-present},
}

@incollection{cochran__william_g:27,
year={2005},
author={Dempster, A. P.},
title={{C}ochran, {W}illiam {G}emmell},
crossref={booktitle:encyclopedia-of-biostatistics},
}

@incollection{cochran__william_g:28,
year={2008},
author={Anderson, R. L.},
title={{C}ochran, {W}illiam {G}emmell},
pages={171-173},
volume={17},
crossref={booktitle:complete-dictionary-of-scientific-biography},
}

@book{cochran__william_g:32,
year={1982},
author={Cochran, W. G.},
title={{C}ontributions to {S}tatistics},
addendum={Forward by F. Mosteller},
pages={vii-xiii},
publisher={Wiley},
}

@misc{cochran__william_g:33,
year={1978},
author={Cochran, W.},
title={{T}he status of {S}tatistics in 1940 as viewed from {I}owa {S}tate {C}ollege and the early years of the {P}h.{D}. program at {A}mes},
addendum={Distinguished Statistician Video Series, DS003. Pfizer, University of Connecticut-Storrs and American Statistical Association.},
url={http://www.amstat.org},
}

@article{cochran__william_g:8,
year={1980},
author={Anonymous},
title={{U}ntitled},
journal={IMS Bulletin},
pages={153},
volume={9},
}

@article{cochran__william_g:10,
year={1980},
author={Anderson, R. L.},
title={{W}illiam {G}emmell {C}ochran 1909-1980, {A} personal tribute},
journal={Biometrics},
pages={574-578},
volume={36},
url={http://www.jstor.org/stable/2556111},
}

@article{cochran__william_g:11,
year={1981},
author={Dempster, A. P. and Mosteller, F.},
title={{I}n memoriam, {W}illiam {G}emmell {C}ochran 1909-1980},
journal={Amer. Statist.},
pages={38},
volume={35},
url={http://www.jstor.org/stable/2683580},
}

@article{cochran__william_g:12,
year={1981},
author={Colton, T.},
title={{B}ill {C}ochran: {H}is contributions to medicine and public health and some personal recollections},
journal={Amer. Statist.},
pages={167-170},
volume={35},
url={http://www.jstor.org/stable/2683997},
}

@incollection{cochran__william_g:15,
year={1981},
author={Rao, P. S. R. S.},
title={{P}rofessor {W}illiam {G}emmell {C}ochran: {P}ioneer in statistics, outstanding scientist and a noble human being},
pages={3-7},
crossref={booktitle:current-topics-in-survey-sampling},
}

@incollection{cochran__william_g:16,
year={1981},
author={Hartley, H. O.},
title={{U}ntitled},
pages={9-14},
crossref={booktitle:current-topics-in-survey-sampling},
}

@article{cochran__william_g:9,
year={1982},
author={Watson, G. S.},
title={{W}illiam {G}emmell {C}ochran 1909-1980},
journal={Ann. Statist.},
pages={1-10},
volume={10},
url={http://www.jstor.org/stable/2240496},
}

@article{cochran__william_g:13,
year={1982},
author={Yates, F.},
title={{W}illiam {G}emmell {C}ochran, 1909-1980},
journal={J. Roy. Statist. Soc. Ser. A},
pages={521-523},
volume={145},
url={http://www.jstor.org/stable/2982120},
}

@article{cochran__william_g:14,
year={1983},
author={Dempster, A. P.},
title={{R}eflections on {W}. {G}. {C}ochran, 1909-1980},
journal={Internat. Statist. Rev.},
pages={321-322},
volume={51},
url={http://www.jstor.org/stable/1402591},
}

@book{cochran__william_g:17,
year={1984},
author={Anonymous},
title={{W}. {G}. {C}ochran{'}s {I}mpact on {S}tatistics},
publisher={Wiley},
}

@article{cochran__william_g:18,
year={2009},
author={Anonymous},
title={{C}ochran at 100},
journal={Harvard Gazette},
url={http://news.harvard.edu/gazette/story/2009/11/cochran-at-100/},
}
\end{filecontents}

\begin{document}

\Name{Cochran, William G.} \Deceased
\ID{cochran__william_g}
\AltID{cochran__william}



\DOB{1909-07-15}
\DOD{1980-03-29}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/William_Gemmell_Cochran}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/cochran.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=50115}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:cochran.william-g}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=25897}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/18129942}{Microsoft Academic: Cochran, William G.}
\Profile{http://academic.research.microsoft.com/Author/51085972}{Microsoft Academic: Cochran, W. G.}


\subsection*{Education}
\Degree{1931}{M.A.}{University of Glasgow}<http://genealogy.math.ndsu.nodak.edu/id.php?id=25897>


\subsection*{Honors}
\Honor{1936}{Guy Medal in Bronze}
\Honor{1946}{IMS President}
\Honor{1967}{Rietz Lecturer}
\Honor{1967}{Samuel S. Wilks Award}
\Honor{1971}{American Academy of Arts and Sciences, Fellow}
\Honor{1972}{R. A. Fisher Lecturer}
\Honor{1974}{National Academy of Sciences, Member}
\Honor{before 1943}{IMS Fellow}


\subsection*{Biographies}
\Biography{cochran__william_g:29}
\Biography{cochran__william_g:25}
\Biography{cochran__william_g:30}
\Biography{cochran__william_g:26}
\Biography{cochran__william_g:27}
\Biography{cochran__william_g:28}


\subsection*{Collected Works}
\CollectedWorks{cochran__william_g:32}


\subsection*{DVD}
\DVD{cochran__william_g:33}


\subsection*{Death Notice}
\DeathNotice{cochran__william_g:8}


\subsection*{Memorials}
\InMemoriam{cochran__william_g:10}
\InMemoriam{cochran__william_g:11}
\InMemoriam{cochran__william_g:12}
\InMemoriam{cochran__william_g:15}
\InMemoriam{cochran__william_g:16}
\InMemoriam{cochran__william_g:9}
\InMemoriam{cochran__william_g:13}
\InMemoriam{cochran__william_g:14}
\InMemoriam{cochran__william_g:17}
\InMemoriam{cochran__william_g:18}
\end{document}