% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Cox, Gertrude M.

@incollection{cox__gertrude_m:20,
year={1987},
author={Nichols, M.},
title={{G}ertrude {M}ary {C}ox (1900-1978).},
pages={26-29},
crossref={booktitle:women-of-mathematics-a-biobibliographic-sourcebook},
}

@article{cox__gertrude_m:21,
year={1990},
author={Anderson, R. L.},
title={{G}ertrude {M}ary {C}ox, {J}anuary 13, 1900-{O}ctober 17, 1978},
journal={Biographical Memoirs},
pages={116-132},
publisher={National Academies Press},
volume={59},
url={http://books.nap.edu/html/biomems/gcox.pdf},
}

@article{cox__gertrude_m:22,
year={1990},
author={Stinnett, S.},
title={{W}omen in statistics: {S}esquicentennial activities},
journal={Amer. Statist.},
pages={74-80},
volume={44},
url={http://www.jstor.org/stable/2684131},
}

@incollection{cox__gertrude_m:26,
year={1990},
author={Anonymous},
title={{G}ertrude {M}. {C}ox, 1900-1978},
addendum={duplicates {S}tinnett (1990)},
publisher={American {S}tatistical {A}ssociation},
booktitle={Statisticians in {H}istory},
url={http://www.amstat.org/about/statisticiansinhistory/index.cfm?fuseaction=biosinfo&BioID=2},
}

@incollection{cox__gertrude_m:24,
year={2001},
author={Anderson, R. L.},
title={{G}ertrude {M}ary {C}ox},
pages={475-478},
crossref={booktitle:statisticians-of-the-centuries},
}

@incollection{cox__gertrude_m:25,
year={2005},
author={Anderson, R. L.},
title={{C}ox, {G}ertrude {M}ary},
crossref={booktitle:encyclopedia-of-biostatistics},
}

@incollection{cox__gertrude_m:23,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@misc{cox__gertrude_m:716231,
year={2009},
author={Whitmore, R. W.},
title={{R}{T}{I} supports {C}ox race, honors namesake},
addendum={Amstat News, June 2009, p. 48},
}

@incollection{cox__gertrude_m:28,
year={2010},
author={O'Connor, J. J. and Robertson, E. F.},
title={{G}ertrude {M}ary {C}ox},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Cox.html},
}

@misc{cox__gertrude_m:27,
year={year?},
author={Anonymous},
title={{A} legacy of discovery: {C}elebrating 50 years of the {C}ollege of {P}hysical and {M}athematical {S}ciences: {T}railblazers},
addendum={North Carolina State University Libraries},
url={http://www.lib.ncsu.edu/exhibits/pams/index.html},
}

@misc{cox__gertrude_m:29,
year={year?},
author={Anonymous},
title={{G}ertrude {M}ary {C}ox},
booktitle={Agnes {S}cott {C}ollege {W}ebsite},
url={http://www.agnesscott.edu/lriddle/women/cox.htm},
}

@article{cox__gertrude_m:8,
year={1979},
author={Anonymous},
title={{U}ntitled},
journal={IMS Bulletin},
pages={4},
volume={8},
}

@article{cox__gertrude_m:9,
year={1978},
author={Anonymous},
title={{G}ertrude {M}ary {C}ox 1900-1978},
journal={Biometrics},
pages={719-720},
volume={34},
url={http://www.jstor.org/stable/2530397},
}

@article{cox__gertrude_m:10,
year={1979},
author={Yates, F.},
title={{G}ertrude {M}ary {C}ox, 1900-1978},
journal={J. Roy. Statist. Soc. Ser. A},
pages={516-517},
volume={142},
url={http://www.jstor.org/stable/2982571},
}

@article{cox__gertrude_m:11,
year={1979},
author={Cochran, W. G.},
title={{G}ertrude {M}ary {C}ox, 1900-1978},
journal={Internat. Statist. Rev.},
pages={97-98},
volume={47},
url={http://www.jstor.org/stable/1403231},
}

@article{cox__gertrude_m:12,
year={1979},
author={Anonymous},
title={{I}n memoriam, {G}ertrude {M}. {C}ox, 1900-1978},
journal={Biometrics},
pages={v-vi},
volume={35},
url={http://www.jstor.org/stable/2529929},
}

@article{cox__gertrude_m:13,
year={1979},
author={Cochran, W. G.},
title={{S}ome reflections},
journal={Biometrics},
pages={1-2},
volume={35},
url={http://www.jstor.org/stable/2529930},
}

@article{cox__gertrude_m:14,
year={1979},
author={Anderson, R. L. and Monroe, R. J. and Nelson, L. A.},
title={{G}ertrude {M}. {C}ox-{A} modern pioneer in statistics},
journal={Biometrics},
pages={3-7},
volume={35},
url={http://www.jstor.org/stable/2529931},
}

@article{cox__gertrude_m:15,
year={1979},
author={Cady, F. B.},
title={{P}erspectives in biometry},
journal={Biometrics},
pages={8},
volume={35},
url={http://www.jstor.org/stable/2529932},
}

@article{cox__gertrude_m:16,
year={1980},
author={Monroe, R. J. and McVay, F. E.},
title={{G}ertrude {M}ary {C}ox, 1900-1978},
journal={Amer. Statist.},
pages={48},
volume={34},
url={http://www.jstor.org/stable/2682996},
}

@misc{cox__gertrude_m:810066,
year={year?},
author={Anonymous},
title={{G}ertrude {M}. {C}ox, {F}irst {L}ady of {S}tatistics},
addendum={Memorial website, North Carolina State University Libraries},
url={http://www.lib.ncsu.edu/exhibits/cox/career.html},
}
\end{filecontents}

\begin{document}

\Name{Cox, Gertrude M.} \Deceased
\ID{cox__gertrude_m}
\AltID{cox__gertrude}

\DisplayName{Cox, Gertrude}


\DOB{1900-01-13}
\DOD{1978-10-17}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Gertrude_Mary_Cox}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/cox_g_m.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=52385}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:cox.gertrude-m}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=89293}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/51032279}{Microsoft Academic: Cox, G.}
\Profile{http://academic.research.microsoft.com/Author/42787966}{Microsoft Academic: Cox, Gertrude M.}


\subsection*{Education}
\Degree{1931}{M.S.}{Iowa State University}[A Statistical Investigation of a Teacher's Ability as Indicated by the Success of His Students in Subsequent Courses]<http://genealogy.math.ndsu.nodak.edu/id.php?id=89293>


\subsection*{Honors}
\Honor{1944}{IMS Fellow}
\Honor{1975}{National Academy of Sciences, Member}
\Honor{1989}{Gertrude M. Cox Scholarship, American Statistical Association and Caucus for Women in Statistics}


\subsection*{Biographies}
\Biography{cox__gertrude_m:20}
\Biography{cox__gertrude_m:21}
\Biography{cox__gertrude_m:22}
\Biography{cox__gertrude_m:26}
\Biography{cox__gertrude_m:24}
\Biography{cox__gertrude_m:25}
\Biography{cox__gertrude_m:23}
\Biography{cox__gertrude_m:716231}
\Biography{cox__gertrude_m:28}
\Biography{cox__gertrude_m:27}
\Biography{cox__gertrude_m:29}


\subsection*{Death Notice}
\DeathNotice{cox__gertrude_m:8}


\subsection*{Obituary}
\Obituary{cox__gertrude_m:9}


\subsection*{Memorials}
\InMemoriam{cox__gertrude_m:10}
\InMemoriam{cox__gertrude_m:11}
\InMemoriam{cox__gertrude_m:12}
\InMemoriam{cox__gertrude_m:13}
\InMemoriam{cox__gertrude_m:14}
\InMemoriam{cox__gertrude_m:15}
\InMemoriam{cox__gertrude_m:16}
\InMemoriam{cox__gertrude_m:810066}
\end{document}