\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Cramér, Harald

@article{cramer__harald:21,
year={1983},
author={Kendall, D.},
title={{A} tribute to {H}arald {C}ram\{'}{e}r},
journal={J. Roy. Statist. Soc. Ser. A},
pages={211-212},
volume={146},
}

@article{cramer__harald:22,
year={1984},
author={Blom, G. and Mat\'{e}rn, B.},
title={{B}ibliography: {P}ublications by {H}arald {C}ram\{'}{e}r},
journal={Scand. Actuar. J.},
pages={1-10},
volume={1984},
}

@article{cramer__harald:23,
year={1986},
author={Wegman, E. J.},
title={{S}ome personal recollections of {H}arald {C}ram\{'}{e}r on the development of statistics and probability},
journal={Statist. Sci.},
pages={528-535},
volume={1},
}

@article{cramer__harald:24,
year={1995},
author={Grenander, U.},
title={{A} survey of the life and works of {H}arald {C}ram\{'}{e}r},
journal={Scand. Actuar. J.},
pages={2-5},
volume={1995},
}

@article{cramer__harald:25,
year={1995},
author={Leadbetter, M. R.},
title={{A} view of {H}arald {C}ram\{'}{e}r: {W}orking with the master in his later years},
journal={Scand. Actuar. J.},
pages={6-11},
volume={1995},
}

@inwebcollection{cramer__harald:28,
year={2000},
author={O'Connor, J. J. and Robertson, E. F.},
title={{C}arl {H}arald {C}ram\{'}{e}r},
note={MacTutor biography},
}

@incollection{cramer__harald:27,
year={2001},
author={Leadbetter, M. R.},
title={{H}arald {C}ram\{'}{e}r},
pages={439-443},
crossref={booktitle:statisticians-of-the-centuries},
}

@incollection{cramer__harald:26,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@article{cramer__harald:31,
year={1995},
author={Anonymous},
title={{H}arald {C}ram\{'}{e}r {S}ymposium. {P}roceedings of the symposium held in {S}tockholm, {S}eptember 24-25, 1993},
journal={Scand. Actuar. J.},
pages={1-152},
volume={1995},
}

@book{cramer__harald:29,
year={1994},
author={Anonymous},
title={{H}arald {C}ram\{'}{e}r: {C}ollected {W}orks},
note={two volumes},
publisher={Springer},
}

@misc{cramer__harald:30,
year={1980},
author={Cram\'{e}r, H.},
title={{M}athematical probability and statistical inference, some recollections from an important phase of scientific development},
publisher={Pfizer, University of Connecticut-Storrs and American Statistical Association},
series={Distinguished Statistician Video Series},
volume={DS002},
}

@book{cramer__harald:9,
year={1959},
author={Anonymous},
title={{P}robability and {S}tatistics, {T}he {H}arald {C}ram\{'}{e}r {V}olume},
publisher={Almqvist \& Wiksell},
}

@article{cramer__harald:10,
year={1986},
author={Anonymous},
title={{U}ntitled},
journal={IMS Bulletin},
pages={271},
volume={15},
}

@article{cramer__harald:11,
year={1985},
author={Bohman, H.},
title={{H}arald {C}ram\{'}{e}r in memoriam},
journal={Scand. Actuar. J.},
pages={129-130},
volume={1985},
}

@article{cramer__harald:12,
year={1986},
author={Kingman, J. F. C.},
title={{H}arald {C}ram\{'}{e}r, 1893-1985},
journal={J. Roy. Statist. Soc. Ser. A},
pages={186},
volume={149},
}

@article{cramer__harald:13,
year={1986},
author={Jung, J.},
title={{I}n memoriam: {H}arald {C}ram\{'}{e}r},
journal={Mitt. Verein. Schweiz. Versicherungsmath.},
pages={121-122},
volume={1986},
}

@article{cramer__harald:14,
year={1986},
author={Lundberg, O.},
title={{H}arald {C}ram\{'}{e}r, 25th {S}eptember 1893-5th {O}ctober 1985},
journal={Astin Bull.},
pages={9-10},
volume={16},
}

@article{cramer__harald:15,
year={1987},
author={Blom, G.},
title={{H}arald {C}ram\{'}{e}r 1893-1985},
journal={Ann. Statist.},
pages={1335-1350},
volume={15},
}

@article{cramer__harald:16,
year={1988},
author={Leadbetter, M. R.},
title={{H}arald {C}ram\{'}{e}r, 1893-1985},
journal={Internat. Statist. Rev.},
pages={89-97},
volume={56},
}
\end{filecontents}

\begin{document}

\subsection*{Education}
\Degree{1917}{Ph.D.}{Stockholm University}{Sur une classe de series de Dirichlet}{http://genealogy.math.ndsu.nodak.edu/id.php?id=20611}


\subsection*{Honors}
\Honor{Royal}{Spanish Academy of Sciences}
\Honor{1946}{IMS Fellow}
\Honor{1953}{Rietz Lecturer}
\Honor{1961}{American Academy of Arts and Sciences, Foreign Honorary Member}
\Honor{1972}{Guy Medal in Gold}
\Honor{1984}{National Academy of Sciences, Foreign Associate}


\subsection*{Biographies}
\Biography{cramer__harald:21}
\Biography{cramer__harald:22}
\Biography{cramer__harald:23}
\Biography{cramer__harald:24}
\Biography{cramer__harald:25}
\Biography{cramer__harald:28}
\Biography{cramer__harald:27}
\Biography{cramer__harald:26}


\subsection*{Symposium}
\Symposium{cramer__harald:31}


\subsection*{Collected Works}
\CollectedWorks{cramer__harald:29}


\subsection*{DVD}
\DVD{cramer__harald:30}


\subsection*{Festschrift}
\Festschrift{cramer__harald:9}


\subsection*{Death Notice}
\DeathNotice{cramer__harald:10}


\subsection*{Memorials}
\InMemoriam{cramer__harald:11}
\InMemoriam{cramer__harald:12}
\InMemoriam{cramer__harald:13}
\InMemoriam{cramer__harald:14}
\InMemoriam{cramer__harald:15}
\InMemoriam{cramer__harald:16}
\end{document}