% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Csörgő, Sándor

@article{csorgo__sandor:9,
year={2008},
author={Bolyai Institute and Mason, D. M.},
title={{S}\'{a}ndor {C}s\"{o}rg\H{o}, 1947-2008},
journal={IMS Bulletin},
pages={16},
volume={37(4)},
}

@article{csorgo__sandor:10,
year={2008},
author={K\'{e}rchy, Cz\'{e}dli, G. and Hajnal, P. and others},
title={{S}\'{a}ndor {C}s\"{o}rg\H{o}, 1947-2008},
journal={Acta Sci. Math. (Szeged)},
pages={3-5},
volume={74},
}

@article{csorgo__sandor:11,
year={2008},
author={Anonymous},
title={{P}ublications of {S}\'{a}ndor {C}s\"{o}rg\H{o}},
journal={Acta Sci. Math. (Szeged)},
pages={7-21},
volume={74},
}

@misc{csorgo__sandor:496792,
year={2008},
author={Anonymous},
title={{I}n {M}emoriam {S}\'{a}ndor {C}s\"{o}rg\H{o}, 1947-2008},
addendum={Bolyai Institute, University of Szeged},
url={http://www.math.u-szeged.hu/portal/en/in-memoriam/in-memoriam-sandor-csorgo.html},
}

@misc{csorgo__sandor:509188,
year={2008},
author={Bolyai Institute and Mason, D. M.},
title={{P}rofessor {S}\'{a}ndor {C}s\"{o}rg\H{o} (1947-2008)},
addendum={International Statistical Institute Newsletter, Vol. 32(2)},
}
\end{filecontents}

\begin{document}

\Name{Cs\"{o}rg\H{o}, S\'{a}ndor} \Deceased
\ID{csorgo__sandor}




\DOB{1947-07-16}
\DOD{2008-02-14}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/S%C3%A1ndor_Cs%C3%B6rg%C5%91}{Wikipedia}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=53165}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:csorgo.sandor}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=51758}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/55065641}{Microsoft Academic: S. Csorgo (S. Cs\"{o}rg\H{o})}
\Profile{http://academic.research.microsoft.com/Author/18753770}{Microsoft Academic: Sandor Csorgo Bolyai (S\'{a}ndor Cs\"{o}rg\"{o} Bolyai)}
\Profile{http://academic.research.microsoft.com/Author/3416526}{Microsoft Academic: Sandor Csorgo (S\'{a}ndor Cs\"{o}rg\H{o})}


\subsection*{Education}
\Degree{1971}{Dr.}{rer. nat. University of Szeged}[Weak Convergence of the Random Sample Size Empirical Process]<http://genealogy.math.ndsu.nodak.edu/id.php?id=51758>


\subsection*{Honors}
\Honor{1984}{IMS Fellow}


\subsection*{Obituary}
\Obituary{csorgo__sandor:9}


\subsection*{Memorials}
\InMemoriam{csorgo__sandor:10}
\InMemoriam{csorgo__sandor:11}
\InMemoriam{csorgo__sandor:496792}
\InMemoriam{csorgo__sandor:509188}
\end{document}