% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Daniel, Cuthbert

@article{daniel__cuthbert:12,
year={1988},
author={Tufte, E. R.},
title={{A} conversation with {C}uthbert {D}aniel},
journal={Statist. Sci.},
pages={413-424},
volume={3},
url={http://www.jstor.org/stable/2245394},
}

@misc{daniel__cuthbert:13,
year={1988},
author={Hunter, J. S.},
title={{A}n interview with {C}uthbert {D}aniel, parts {I} and {I}{I}},
addendum={Distinguished Statistician Video Series, DS018. Pfizer, University of Connecticut-Storrs and American Statistical Association. Available at},
url={http://www.amstat.org},
}

@book{daniel__cuthbert:7,
year={1987},
author={Anonymous},
title={{D}esign, {D}ata and {A}nalysis, by {S}ome {F}riends of {C}uthbert {D}aniel},
addendum={contain biography and bibliography},
publisher={Wiley},
}

@article{daniel__cuthbert:8,
year={1998},
author={Hunter, J. S.},
title={{C}uthbert {D}aniel: {I}ndustrial statistician},
journal={Amer. Statist.},
pages={89-92},
volume={52},
url={http://www.jstor.org/stable/2685465},
}

@article{daniel__cuthbert:9,
year={2000},
author={Mallows, C.},
title={{C}uthbert {D}aniel, 1905-1997},
journal={J. Roy. Statist. Soc. Ser. D},
pages={111},
volume={49},
url={http://www.jstor.org/stable/2681261},
}
\end{filecontents}

\begin{document}

\Name{Daniel, Cuthbert} \Deceased
\ID{daniel__cuthbert}




\DOB{1904-08-27}
\DOD{1997-08-08}


\Homepage{http://www.irsst.qc.ca/fr/_personne_0723.html}


\subsection*{Profiles}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/daniel.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=431378}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:daniel.cuthbert}{zbMATH}
\Profile{http://academic.research.microsoft.com/Author/12526350}{Microsoft Academic: Cuthbert Daniel}


\subsection*{Honors}
\Honor{1963}{IMS Fellow}
\Honor{1971}{R. A. Fisher Lecturer}
\Honor{1974}{Samuel S. Wilks Award}


\subsection*{Biography}
\Biography{daniel__cuthbert:12}


\subsection*{DVD}
\DVD{daniel__cuthbert:13}


\subsection*{Festschrift}
\Festschrift{daniel__cuthbert:7}


\subsection*{Memorials}
\InMemoriam{daniel__cuthbert:8}
\InMemoriam{daniel__cuthbert:9}
\end{document}