% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Daniels, Henry E.

@article{daniels__henry_e:14,
year={1993},
author={Whittle, P.},
title={{A} conversation with {H}enry {D}aniels},
journal={Statist. Sci.},
pages={342-353},
volume={8},
url={http://www.jstor.org/stable/2245982},
}

@article{daniels__henry_e:15,
year={2003},
author={Cox, D.},
title={{H}enry {E}llis {D}aniels, 2 {O}ctober 1912-16 {A}pril 2000},
journal={Biogr. Mems. Fell. R. Soc.},
pages={133-146},
volume={49},
url={http://www.jstor.org/stable/3650218},
}

@incollection{daniels__henry_e:16,
year={2004},
author={Cox, D. R.},
title={{U}ntitled},
author={Cox, D. R.},
year={2004},
crossref={booktitle:oxford-dictionary-of-national-biography-in-association-with-the-british-academy-from-the-earliest-times-to-the-year-2000},
url={http://www.oxforddnb.com/view/article/74126},
}

@incollection{daniels__henry_e:17,
year={2006},
author={Cox, D. R.},
title={{U}ntitled},
author={Cox, D. R.},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@misc{daniels__henry_e:715997,
year={2000},
author={Anonymous},
title={{W}hittle, {P}. {H}enry {D}aniels},
addendum={The Guardian, May 4, 2000, p. 24},
}

@misc{daniels__henry_e:976486,
year={2000},
author={Anonymous},
title={{P}rofessor {H}enry {D}aniels},
addendum={The Times, May 23, 2000},
}

@misc{daniels__henry_e:204388,
year={2000},
author={Barnard, G.},
title={{P}rofessor {H}enry {D}aniels},
addendum={The Independent, Jun. 20, 2000, p. 6},
}

@article{daniels__henry_e:11,
year={2000},
author={Anonymous},
title={{H}enry {D}aniels, 1912-2000},
journal={IMS Bulletin},
pages={409-410},
volume={29},
}

@article{daniels__henry_e:12,
year={2001},
author={Whittle, P.},
title={{H}enry {D}aniels},
journal={J. Roy. Statist. Soc. Ser. D},
pages={213-214},
volume={50},
url={http://www.jstor.org/stable/2681096},
}
\end{filecontents}

\begin{document}

\Name{Daniels, Henry E.} \Deceased
\ID{daniels__henry_e}
\AltID{daniels__henry}



\DOB{1912-10-02}
\DOD{2000-04-16}


\Homepage{http://en.wikipedia.org/wiki/Henry_Daniels}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Henry_Daniels}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/daniels.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=54475}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:daniels.henry-e}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=57769}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/12866433}{Microsoft Academic: Daniels, H. E.}
\Profile{http://academic.research.microsoft.com/Author/54218635}{Microsoft Academic: Daniels, Henry E.}


\subsection*{Education}
\Degree{1943}{Ph.D.}{University of Edinburgh}[On the Strength Distribution of Bundles of Threads, and Its Asymptotic Distribution]<http://genealogy.math.ndsu.nodak.edu/id.php?id=57769>


\subsection*{Honors}
\Honor{1954}{IMS Fellow}
\Honor{1957}{Guy Medal in Silver}
\Honor{1980}{The Royal Society, Fellow}
\Honor{1984}{Guy Medal in Gold}


\subsection*{Biographies}
\Biography{daniels__henry_e:14}
\Biography{daniels__henry_e:15}
\Biography{daniels__henry_e:16}
\Biography{daniels__henry_e:17}


\subsection*{Obituaries}
\Obituary{daniels__henry_e:715997}
\Obituary{daniels__henry_e:976486}
\Obituary{daniels__henry_e:204388}
\Obituary{daniels__henry_e:11}


\subsection*{In Memoriam}
\InMemoriam{daniels__henry_e:12}
\end{document}