% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Dantzig, George B.

@article{dantzig__george_b:32,
year={1986},
author={Albers, D. J. and Reid, C.},
title={{A}n interview with {G}eorge {B}. {D}antzig: {T}he father of linear programming},
journal={College Math. J.},
pages={292-314},
volume={17},
url={http://www.jstor.org/stable/2686279},
}

@incollection{dantzig__george_b:33,
year={1990},
author={Anonymous},
title={{G}eorge {B}. {D}antzig},
pages={61-79},
crossref={booktitle:more-mathematical-people-contemporary-conversations},
}

@incollection{dantzig__george_b:39,
year={2003},
author={O'Connor, J. J. and Robertson, E. F.},
title={{G}eorge {B}ernard {D}antzig},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Dantzig_George.html},
}

@article{dantzig__george_b:34,
year={2008},
author={Gill, P. E. and Murray, W. and Saunders, M. A. and Tomlin, J. A. and Wright, M. H.},
title={{G}eorge {B}. {D}antzig and systems optimization},
journal={Discrete Optim.},
pages={151-158},
volume={5},
}

@article{dantzig__george_b:35,
year={2008},
author={Arrow, K. J.},
title={{G}eorge {D}antzig in the development of economic analysis},
journal={Discrete Optim.},
pages={159-167},
volume={5},
}

@article{dantzig__george_b:36,
year={2008},
author={Gr\"{o}tschel, M. and Nemhauser, G. L.},
title={{G}eorge {D}antzig{'}s contributions to integer programming},
journal={Discrete Optim.},
pages={168-173},
volume={5},
}

@article{dantzig__george_b:37,
year={2008},
author={Karp, R. M.},
title={{G}eorge {D}antzig{'}s impact on the theory of computation},
journal={Discrete Optim.},
pages={174-185},
volume={5},
}

@article{dantzig__george_b:38,
year={2011},
author={Todd, M. J.},
title={{B}ook review of {T}he {B}asic {G}eorge {B}. {D}antzig},
journal={Bull. Amer. Math. Soc.},
pages={123-129},
volume={48},
url={http://www.ams.org/journals/bull/2011-48-01/S0273-0979-2010-01303-3/S0273-0979-2010-01303-3.pdf},
}

@book{dantzig__george_b:41,
year={2003},
author={Anonymous},
title={{T}he {B}asic {G}eorge {B}. {D}antzig},
addendum={Includes introduction by Cottle},
publisher={Stanford Business Books},
}

@article{dantzig__george_b:15,
year={2005},
author={Anonymous},
title={{O}ptimization community mourns loss of two linear programming giants},
journal={SIAM News},
volume={Jun. 10,},
url={http://www.siam.org/news/news.php?id=110},
}

@misc{dantzig__george_b:627513,
year={2005},
author={Anonymous},
title={{U}ntitled},
addendum={Levy, D. (2005). George B. Dantzig, operations research professor, dies at 90. Stanford University News, May 25, 2005},
url={http://news.stanford.edu/news/2005/may25/dantzigobit-052505.html},
}

@misc{dantzig__george_b:216354,
year={2005},
author={Anonymous},
title={{U}ntitled},
addendum={George Bernard Dantzig -- Stanford math professor. San Francisco Chronicle, May 16, 2005},
url={http://www.sfgate.com/cgi-bin/article.cgi?f=/c/a/2005/05/16/BAGGVCPO811.DTL},
}

@misc{dantzig__george_b:530111,
year={2005},
author={Anonymous},
title={{U}ntitled},
addendum={Holley, J. Vanguard mathematician George Dantzig dies. The Washington Post, May 19, 2005},
url={http://www.washingtonpost.com/wp-dyn/content/article/2005/05/18/AR2005051802171.html},
}

@misc{dantzig__george_b:965738,
year={2005},
author={Anonymous},
title={{U}ntitled},
addendum={Pearce, J. George B. Dantzig, 90; devised math solution to broad problems. The New York Times, May 23, 2005, p. 7},
url={http://www.nytimes.com/2005/05/23/national/23dantzig.html},
}

@article{dantzig__george_b:16,
year={2005},
author={Bickel, P.},
title={{U}ntitled},
journal={IMS Bulletin},
pages={6},
volume={34(7)},
}

@article{dantzig__george_b:17,
year={2005},
author={Allende, S. M. and Bouza, C. N.},
title={{P}rofessor {G}eorge {B}ernard {D}antzig, life and legend},
journal={Investigaci\'{o}n Oper.},
pages={205-211},
volume={26},
}

@article{dantzig__george_b:18,
year={2005},
author={Cottle, R. W.},
title={{G}eorge {B}. {D}antzig: operations research icon},
journal={Oper. Res.},
pages={892-898},
volume={53},
}

@article{dantzig__george_b:19,
year={2005},
author={Albers, D.},
title={{G}eorge {D}antzig 1914-2005},
journal={Focus: Newsletter of the Math. Assoc. America},
pages={8-10},
volume={25(6)},
}

@article{dantzig__george_b:20,
year={2005},
author={Escudero, L. F.},
title={{E}n la muerte de {G}eorge {B}. {D}antzig},
journal={Bol. Estad. Investig. Oper.},
pages={29-31},
volume={21},
}

@article{dantzig__george_b:21,
year={2006},
author={Cottle, R. W.},
title={{G}eorge {B}. {D}antzig: a legendary life in mathematical programming},
journal={Math Program. Ser. A},
pages={1-8},
volume={105(1)},
}

@article{dantzig__george_b:22,
year={2006},
author={Cottle, R. W. and Wright, M. H.},
title={{R}emembering {G}eorge {D}antzig},
journal={SIAM News},
volume={Apr. 12,},
url={http://www.siam.org/news/news.php?id=928},
}

@article{dantzig__george_b:23,
year={2007},
author={Cottle, R. and Johnson, E. and Wets, R.},
title={{G}eorge {B}. {D}antzig (1914-2005)},
journal={Notices Amer. Math. Soc.},
pages={344-362},
volume={54},
url={http://www.stanford.edu/group/SOL/cottle-johnson-wetts-2007.pdf},
}

@article{dantzig__george_b:24,
year={2008},
author={Balas, E. and Hoffman, A. J. and McCormick, S. T.},
title={{A} special issue in memory of {G}eorge {B}. {D}antzig},
journal={Discrete Optim.},
pages={145-150},
volume={5},
}

@misc{dantzig__george_b:310753,
year={year?},
author={Anonymous},
title={{U}ntitled},
addendum={Systems Optimization Laboratory, Stanford University Dept of Management Science and Engineering},
url={http://www.stanford.edu/group/SOL/GBD.html},
}
\end{filecontents}

\begin{document}

\Name{Dantzig, George B.} \Deceased
\ID{dantzig__george_b}
\AltID{dantzig__george}



\DOB{1914-11-08}
\DOD{2005-05-13}


\Homepage{http://en.wikipedia.org/wiki/George_Dantzig}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/George_Dantzig}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/dantzig.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=54520}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:dantzig.george-b}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=32292}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/48332547}{Microsoft Academic: George B. Dantzig}
\Profile{http://academic.research.microsoft.com/Author/23408343}{Microsoft Academic: G. B. Dantzig}
\Profile{http://academic.research.microsoft.com/Author/51243458}{Microsoft Academic: George B. Dantzig}
\Profile{http://academic.research.microsoft.com/Author/904139}{Microsoft Academic: George Dantzig}
\Profile{http://academic.research.microsoft.com/Author/10558155}{Microsoft Academic: G. B. Dantzig}


\subsection*{Education}
\Degree{1946}{Ph.D.}{University of California, Berkeley}[I. Complete Form Neyman-Pearson Fundamental Lemma. II. On the Non-Existence of Tests of Student's Hypothesis Having Power Functions Independent of Sigma]<http://genealogy.math.ndsu.nodak.edu/id.php?id=32292>


\subsection*{Honors}
\Honor{1959}{IMS Fellow}
\Honor{1971}{National Academy of Sciences, Member}
\Honor{1975}{American Academy of Arts and Sciences, Fellow}
\Honor{1975}{John von Neumann Theory Prize}
\Honor{1975}{National Medal of Science}
\Honor{1979}{The George B. Dantzig Prize, Mathematical Optimization Society and the Society for Industrial and Applied Mathematics}
\Honor{1985}{National Academy of Engineering, Member}


\subsection*{Biographies}
\Biography{dantzig__george_b:32}
\Biography{dantzig__george_b:33}
\Biography{dantzig__george_b:39}
\Biography{dantzig__george_b:34}
\Biography{dantzig__george_b:35}
\Biography{dantzig__george_b:36}
\Biography{dantzig__george_b:37}
\Biography{dantzig__george_b:38}


\subsection*{Selected Works}
\SelectedWorks{dantzig__george_b:41}


\subsection*{Death Notice}
\DeathNotice{dantzig__george_b:15}


\subsection*{Obituaries}
\Obituary{dantzig__george_b:627513}
\Obituary{dantzig__george_b:216354}
\Obituary{dantzig__george_b:530111}
\Obituary{dantzig__george_b:965738}


\subsection*{Memorials}
\InMemoriam{dantzig__george_b:16}
\InMemoriam{dantzig__george_b:17}
\InMemoriam{dantzig__george_b:18}
\InMemoriam{dantzig__george_b:19}
\InMemoriam{dantzig__george_b:20}
\InMemoriam{dantzig__george_b:21}
\InMemoriam{dantzig__george_b:22}
\InMemoriam{dantzig__george_b:23}
\InMemoriam{dantzig__george_b:24}
\InMemoriam{dantzig__george_b:310753}
\end{document}