% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Darmois, Georges

@incollection{darmois__georges:12,
year={2001},
author={Bru, B.},
title={{G}eorges {D}armois},
pages={382-385},
crossref={booktitle:statisticians-of-the-centuries},
}

@incollection{darmois__georges:13,
year={2011},
author={O'Connor, J. J. and Robertson, E. F.},
title={{G}eorges {D}armois},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Darmois.html},
}

@article{darmois__georges:7,
year={1960},
author={Roy, R.},
title={{G}eorges {D}armois, 1888-1960},
journal={J. Roy. Statist. Soc. Ser. A},
pages={520-522},
volume={123},
url={http://www.jstor.org/stable/2343305},
}

@article{darmois__georges:8,
year={1961},
author={Dugu\'{e}, D.},
title={{G}eorges {D}armois, 1888-1960},
journal={Ann. Math. Statist.},
pages={357-360},
volume={32},
url={http://www.jstor.org/stable/2237749},
}

@article{darmois__georges:9,
year={1961},
author={Roy, R.},
title={{G}eorges {D}armois, 1888-1960},
journal={Econometrica},
pages={80-83},
volume={29},
url={http://www.jstor.org/stable/1907690},
}

@misc{darmois__georges:828064,
year={year?},
author={Anonymous},
title={{G}eorges {D}armois},
addendum={Acad\'{e}mie des sciences},
url={http://www.academie-sciences.fr/activite/archive/dossiers/eloges/darmoisg_notice.pdf},
}
\end{filecontents}

\begin{document}

\Name{Darmois, Georges} \Deceased
\ID{darmois__georges}




\DOB{1888-06-24}
\DOD{1960-01-03}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Georges_Darmois}{Wikipedia}
\Profile{http://fr.wikipedia.org/wiki/Georges_Darmois}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/darmois.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=431600}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:darmois.georges}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=81193}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/271945}{Microsoft Academic: G. Darmois}
\Profile{http://academic.research.microsoft.com/Author/48520503}{Microsoft Academic: Georges Darmois}


\subsection*{Education}
\Degree{1921}{Doctorat}{\`{e}s Sciences Universit\'{e} de Paris}[Sur les courbes alg\'{e}briques \`{a} torsion constante]<http://genealogy.math.ndsu.nodak.edu/id.php?id=81193>


\subsection*{Honors}
\Honor{1947}{IMS Fellow}
\Honor{1956}{Acad\'{e}mie des sciences, Member}


\subsection*{Biographies}
\Biography{darmois__georges:12}
\Biography{darmois__georges:13}


\subsection*{Memorials}
\InMemoriam{darmois__georges:7}
\InMemoriam{darmois__georges:8}
\InMemoriam{darmois__georges:9}
\InMemoriam{darmois__georges:828064}
\end{document}