\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for David, Florence N.

@article{david__florence_n:17,
year={1989},
author={Laird, N. M.},
title={{A} conversation with {F}. {N}. {D}avid},
journal={Statist. Sci.},
pages={235-246},
volume={4},
}

@article{david__florence_n:18,
year={1990},
author={Stinnett, S., et al.},
title={{W}omen in statistics: {S}esquicentennial activities},
journal={Amer. Statist.},
pages={74-80},
volume={44},
}

@article{david__florence_n:19,
year={1993},
author={Anonymous},
title={{F}. {N}. {D}avid wins first {E}lizabeth {L}. {S}cott {A}ward},
journal={Association for Women in Mathematics Newsletter},
pages={5-6},
volume={23(3)},
}

@incollection{david__florence_n:23,
year={1993},
author={Anonymous},
title={{K}ruse, {M}. and {L}aird, {N}. {F}lorence {N}. {D}avid, 1909-1993},
publisher={American {S}tatistical {A}ssociation},
booktitle={Statisticians in {H}istory},
}

@misc{david__florence_n:20,
year={1996},
author={O'Sullivan, C.},
title={{F}lorence {N}ightingale {D}avid},
booktitle={Agnes {S}cott {C}ollege {W}ebsite},
}

@incollection{david__florence_n:21,
year={1997},
author={Utts, J.},
title={{D}avid, {F}lorence {N}ightingale},
pages={91-93},
crossref={booktitle:leading-personalities-in-statistical-sciences-from-the-17th-century-to-the-present},
}

@incollection{david__florence_n:24,
year={2004},
author={O'Connor, J. J. and Robertson, E. F.},
title={{F}lorence {N}ightingale {D}avid},
note={MacTutor biography},
}

@incollection{david__florence_n:22,
year={2006},
author={Utts, J.},
title={{D}avid, {F}lorence {N}ightingale},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@misc{david__florence_n:115183,
year={1993},
author={Anonymous},
title={{U}ntitled},
}

@misc{david__florence_n:417900,
year={1993},
author={Anonymous},
title={{U}ntitled},
}

@article{david__florence_n:10,
year={1993},
author={Le Cam, L.},
title={{F}lorence {N}ightingale {D}avid, 1909-1993},
journal={IMS Bulletin},
pages={447-448},
volume={22},
}

@article{david__florence_n:11,
year={1993},
author={Utts, J.},
title={{F}lorence {N}ightingale {D}avid, 1909-1993},
journal={Biometrics},
pages={1289-1291},
volume={49},
}

@article{david__florence_n:12,
year={1994},
author={Barton, D.},
title={{F}lorence {N}ightingale {D}avid},
journal={J. Roy. Statist. Soc. Ser. A},
pages={299-301},
volume={157},
}

@article{david__florence_n:13,
year={1994},
author={Anonymous},
title={{I}n memoriam, {P}rofessor {F}lorence {N}. {D}avid},
journal={Association for Women in Mathematics Newsletter},
pages={16},
volume={24(1)},
}

@misc{david__florence_n:701330,
year={1995},
author={Anonymous},
title={{U}ntitled},
}
\end{filecontents}

\begin{document}

\Name{David, Florence N.}
\DOB{1909-08-23}
\DOD{1993-07-23}


\subsection*{Education}
\Degree{1938}{Ph.D.}{University of London}{http://genealogy.math.ndsu.nodak.edu/id.php?id=49989}


\subsection*{Honors}
\Honor{Florence}{Nightingale David Award, Committee of Presidents of Statistical Societies}
\Honor{1946}{IMS Fellow}
\Honor{1992}{Elizabeth L. Scott Award}


\subsection*{Biographies}
\Biography{david__florence_n:17}
\Biography{david__florence_n:18}
\Biography{david__florence_n:19}
\Biography{david__florence_n:23}
\Biography{david__florence_n:20}
\Biography{david__florence_n:21}
\Biography{david__florence_n:24}
\Biography{david__florence_n:22}


\subsection*{Obituaries}
\Obituary{david__florence_n:115183}
\Obituary{david__florence_n:417900}
\Obituary{david__florence_n:10}


\subsection*{Memorials}
\InMemoriam{david__florence_n:11}
\InMemoriam{david__florence_n:12}
\InMemoriam{david__florence_n:13}
\InMemoriam{david__florence_n:701330}
\end{document}