% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for de Finetti, Bruno

@article{de_finetti__bruno:15,
year={1985},
author={Scardovi, I.},
title={{S}alute to {B}runo de {F}inetti},
addendum={in Italian},
journal={Statistica,},
pages={149-152},
volume={45},
}

@article{de_finetti__bruno:16,
year={1996},
author={Cifarelli, D. M. and Regazzini, E.},
title={{D}e {F}inetti{'}s contribution to probability and statistics},
journal={Statist. Sci.},
pages={253-282},
volume={11},
url={http://www.jstor.org/stable/2246020},
}

@article{de_finetti__bruno:18,
year={2001},
author={Rossi, C.},
title={{B}runo de {F}inetti: {T}he mathematician, the statistician, the economist, the forerunner},
journal={Stat. Med.},
pages={3651-3666},
volume={20},
}

@incollection{de_finetti__bruno:19,
year={2001},
author={Hill, B. M.},
title={{D}e {F}inetti, {B}runo (1906-85).},
pages={3260-3263},
crossref={booktitle:international-encyclopedia-of-the-social-behavioral-sciences},
}

@incollection{de_finetti__bruno:25,
year={2004},
author={Luca La Rocca and Reggio Emilia},
title={{L}. {B}runo de {F}inetti},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/De_Finetti.html},
}

@incollection{de_finetti__bruno:20,
year={2005},
author={Lindley, D. V.},
title={de {F}inetti, {B}runo},
crossref={booktitle:encyclopedia-of-biostatistics},
}

@incollection{de_finetti__bruno:17,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@article{de_finetti__bruno:21,
year={2006},
author={Anichini, G.},
title={{B}runo de {F}inetti---a great probabilist and a great man},
journal={European Mathematical Society Newsletter},
pages={24-28},
}

@article{de_finetti__bruno:22,
year={2007},
author={Anichini, G.},
title={{P}rofile: {B}runo de {F}inetti},
journal={IMS Bulletin},
pages={7},
volume={36(3)},
}

@incollection{de_finetti__bruno:23,
year={2008},
author={Weirich, P.},
title={de {F}inetti, {B}runo},
pages={255-258},
volume={20},
crossref={booktitle:complete-dictionary-of-scientific-biography},
}

@incollection{de_finetti__bruno:24,
year={2010},
author={Cifarelli, D. M.},
title={{B}runo de {F}inetti: {T}he foundations of probability},
pages={109-113},
crossref={booktitle:mathematical-lives-protagonists-of-the-twentieth-century-from-hilbert-to-wiles},
}

@book{de_finetti__bruno:8,
year={1986},
author={Anonymous},
title={{B}ayesian {I}nference and {D}ecision {T}echniques: {E}ssays in {H}onor of {B}runo de {F}inetti},
publisher={North-Holland},
}

@article{de_finetti__bruno:9,
year={1986},
author={Lindley, D. V.},
title={{B}runo de {F}inetti, 1906-1985},
journal={J. Roy. Statist. Soc. Ser. A},
pages={252},
volume={149},
url={http://www.jstor.org/stable/2981556},
}

@article{de_finetti__bruno:10,
year={1986},
author={Ferrara, G.},
title={{B}runo de {F}inetti, 13th {J}une 1906-20th {J}uly 1985},
journal={Astin Bull.},
pages={11-12},
volume={16},
}

@article{de_finetti__bruno:11,
year={1987},
author={Daboni, L.},
title={{B}runo de {F}inetti},
addendum={in Italian},
journal={Boll. Un. Mat. Ital. A (7)},
pages={283-308},
volume={1},
}

@article{de_finetti__bruno:12,
year={1987},
author={Daboni, L.},
title={{I}n memory of {B}runo de {F}inetti},
addendum={in Italian},
journal={Riv. Mat. Sci. Econom. Social.},
pages={91-127},
volume={10},
}

@misc{de_finetti__bruno:512297,
year={year?},
author={Anonymous},
title={{U}ntitled},
addendum={Bruno de Finetti memorial website},
url={http://www.brunodefinetti.it/},
}
\end{filecontents}

\begin{document}

\Name{de Finetti, Bruno} \Deceased
\ID{de_finetti__bruno}




\DOB{1906-06-13}
\DOD{1985-07-20}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Bruno_de_Finetti}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/de_finetti.gif}{www.york.ac.uk}
\Profile{http://zbmath.org/authors/?q=ai:finetti.bruno-de}{zbMATH}
\Profile{http://zbmath.org/authors/?q=ai:de-finetti.bruno}{zbMATH}
\Profile{http://academic.research.microsoft.com/Author/45509087}{Microsoft Academic: Bruno De Finetti}
\Profile{http://academic.research.microsoft.com/Author/55253084}{Microsoft Academic: Bruno De Finetti}
\Profile{http://academic.research.microsoft.com/Author/51891495}{Microsoft Academic: De Finetti B}


\subsection*{Honors}
\Honor{1951}{IMS Fellow}
\Honor{1974}{Accademia Nazionale dei Lincei, Member}


\subsection*{Biographies}
\Biography{de_finetti__bruno:15}
\Biography{de_finetti__bruno:16}
\Biography{de_finetti__bruno:18}
\Biography{de_finetti__bruno:19}
\Biography{de_finetti__bruno:25}
\Biography{de_finetti__bruno:20}
\Biography{de_finetti__bruno:17}
\Biography{de_finetti__bruno:21}
\Biography{de_finetti__bruno:22}
\Biography{de_finetti__bruno:23}
\Biography{de_finetti__bruno:24}


\subsection*{Festschrift}
\Festschrift{de_finetti__bruno:8}


\subsection*{Memorials}
\InMemoriam{de_finetti__bruno:9}
\InMemoriam{de_finetti__bruno:10}
\InMemoriam{de_finetti__bruno:11}
\InMemoriam{de_finetti__bruno:12}
\InMemoriam{de_finetti__bruno:512297}
\end{document}