% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Donoho, David L.

@article{donoho__david_l:16,
year={1998},
author={Anonymous},
title={{P}rofessor {D}avid {L}. {D}onoho},
journal={IMS Bulletin},
pages={138},
volume={27},
}

@misc{donoho__david_l:413451,
year={2009},
author={Anonymous},
title={{U}ntitled},
addendum={David L. Donoho receives honorary degree. Amstat News, Dec. 2009, p. 55},
}

@article{donoho__david_l:17,
year={2010},
author={Anonymous},
title={2010 {W}iener {P}rize},
journal={Notices Amer. Math. Soc.},
pages={519-520},
volume={57},
url={http://www.ams.org/notices/201004/rtx100400519p.pdf},
}

@misc{donoho__david_l:924299,
year={5},
author={Anonymous},
title={{U}ntitled},
addendum={2013 Shaw Prize laureate. IMS Bulletin, Vol. 42(5), p. 2},
}
\end{filecontents}

\begin{document}

\Name{Donoho, David L.}
\ID{donoho__david_l}
\AltID{donoho__david}

\DisplayName{Donoho, David}


\Homepage{http://www-stat.stanford.edu/~donoho/}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/David_Donoho}{Wikipedia}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=59130}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:donoho.david-l}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=18642}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/848706}{Microsoft Academic: Donoho, David}


\subsection*{Education}
\Degree{1983}{Ph.D.}{Harvard University}[A Tool for Research in Data Analysis]<http://genealogy.math.ndsu.nodak.edu/id.php?id=18642>


\subsection*{Honors}
\Honor{1990}{IMS Fellow}
\Honor{1991}{IMS Medallion Lecturer}
\Honor{1991}{IMS Medallion Lecturer}
\Honor{1991}{MacArthur Fellow}
\Honor{1992}{American Academy of Arts and Sciences, Fellow}
\Honor{1994}{COPSS Presidents' Award}
\Honor{1997}{Wald Lecturer}
\Honor{1998}{National Academy of Sciences, Member}
\Honor{2001}{John von Neumann Lecturer}
\Honor{2003}{Le Cam Lecturer}
\Honor{2009}{Acad\'{e}mie des sciences, Foreign Associate}
\Honor{2010}{Norbert Wiener Prize in Applied Mathematics}
\Honor{2013}{Shaw Prize}


\subsection*{Biographies}
\Biography{donoho__david_l:16}
\Biography{donoho__david_l:413451}
\Biography{donoho__david_l:17}
\Biography{donoho__david_l:924299}
\end{document}