% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Doob, Joseph L.

@article{doob__joseph_l:24,
year={1997},
author={Snell, J. L.},
title={{A} conversation with {J}oe {D}oob},
journal={Statist. Sci.},
pages={301-311},
volume={12},
url={http://www.jstor.org/stable/2246220},
}

@misc{doob__joseph_l:657909,
year={1998},
author={Chung, K. L.},
title={{P}robability and {D}oob},
addendum={Amer. Math. Monthly, Vol. 105, pp. 28-35},
url={http://www.jstor.org/stable/2589523},
}

@incollection{doob__joseph_l:25,
year={2004},
author={O'Connor, J. J. and Robertson, E. F.},
title={{J}oseph {L}eo {D}oob},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Doob.html},
}

@misc{doob__joseph_l:486246,
year={2009},
author={Yor, M.},
title={{J}. {L}. {D}oob (27 {F}ebruary 1910---7 {J}une 2004)},
addendum={Ann. Probab., Vol. 37, pp. 1664-1670},
url={http://www.jstor.org/stable/30244336},
}

@misc{doob__joseph_l:723565,
year={2009},
author={Locker, B.},
title={{D}oob at {L}yon},
addendum={J. \'{E}lectron. Hist. Probab. Stat., Vol. 5(1) (translated by R. Sverdlove)},
url={http://www.jehps.net/juin2009/Locker.pdf},
}

@misc{doob__joseph_l:956764,
year={2009},
author={Doob, Joseph L.},
title={{L}etter from {J}oseph {L}. {D}oob, dated {J}une 6, 1985},
addendum={J. \'{E}lectron. Hist. Probab. Stat., Vol. 5(1)},
url={http://www.jehps.net/juin2009/Doob.pdf},
}

@misc{doob__joseph_l:783464,
year={2004},
author={Anonymous},
title={{U}ntitled},
addendum={(2004). In Memoriam archive, Mathematical Association of America},
url={http://www.maa.org/news/inmemoriam_archive.html},
}

@misc{doob__joseph_l:242472,
year={2004},
author={Pearce, J.},
title={{J}oseph {D}oob, 94, expert on probability theory},
addendum={The New York Times, Jun. 28, 2004},
}

@misc{doob__joseph_l:765788,
year={2004},
author={Anonymous},
title={{J}oseph {D}oob},
addendum={The Times, Jul. 26, 2004},
}

@misc{doob__joseph_l:960670,
year={2004},
author={Doob, S. and Burkholder, D. and Blackwell, D. and Haken, W. and Jain, N. and Wagstaff, S. and Snell, L.},
title={{R}ecord of the celebration of the life of {J}oseph {L}eo {D}oob},
addendum={Department of Mathematics, University of Illinois at Urbana-Champaign},
url={http://www.math.uiuc.edu/People/doob_record.html},
}

@article{doob__joseph_l:11,
year={2004},
author={Burkholder, D.},
title={{J}oseph {L}. {D}oob, 1910-2004},
journal={IMS Bulletin},
pages={8},
volume={33(6)},
}

@misc{doob__joseph_l:983147,
year={2004},
author={Anonymous},
title={{J}oseph {L}eo {D}oob (1910-2004)},
addendum={Department of Mathematics, University of Illinois},
url={http://www.math.uiuc.edu/People/doob_obit.html},
}

@article{doob__joseph_l:13,
year={2005},
author={Burkholder, D. and Protter, P.},
title={{J}oseph {L}eo {D}oob, 1910-2004},
journal={Stochastic Process. Appl.},
pages={1061-1072},
volume={115},
}

@article{doob__joseph_l:14,
year={2005},
author={Snell, J. L.},
title={{J}oseph {L}eonard {D}oob},
journal={J. Appl. Probab.},
pages={247-256},
volume={42},
url={http://www.jstor.org/stable/30040783},
}

@misc{doob__joseph_l:467916,
year={2005},
author={Bingham, N. H.},
title={{D}oob: {A} half-century on},
addendum={J. Appl. Probab., Vol. 42, pp. 257-266},
url={http://www.jstor.org/stable/30040784},
}

@misc{doob__joseph_l:944565,
year={2006},
author={Burkholder, D.},
title={{S}pecial {V}olume in {M}emory of {J}oseph {D}oob (1910-2004)},
addendum={Illinois J. Math., Vol. 50. Also issued as Burkholder, D., ed. (2007). Joseph Doob: A Collection of Mathematical Articles in His Memory. Institute of Mathematical Statistics, Beachwood, OH},
}

@misc{doob__joseph_l:910312,
year={2006},
author={Burkholder, D.},
title={{J}oseph {L}eo {D}oob (1910-2004)},
addendum={Illinois J. Math., Vol. 50, pp. vii-viii},
}

@misc{doob__joseph_l:551039,
year={2007},
author={Yor, M.},
title={{J}oseph {L}eo {D}oob (27 f\'{e}vrier 1910---7 juin 2004)},
addendum={Gaz. Math., no. 114, pp. 33-39 (in French)},
url={http://smf4.emath.fr/en/Publications/Gazette/2007/114/smf_gazette_114_33-39.pdf},
}

@misc{doob__joseph_l:91996,
year={year?},
author={Anonymous},
title={{J}oseph {D}oob},
addendum={Acad\'{e}mie des sciences},
url={http://www.academie-sciences.fr/academie/membre/Doob_Joseph.htm},
}
\end{filecontents}

\begin{document}

\Name{Doob, Joseph L.} \Deceased
\ID{doob__joseph_l}
\AltID{doob__joseph}



\DOB{1910-02-27}
\DOD{2004-06-07}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Joseph_L._Doob}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/doob.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=59155}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:doob.joseph-leo}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=4598}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/12869844}{Microsoft Academic: Doob, J. L.}
\Profile{http://academic.research.microsoft.com/Author/54980422}{Microsoft Academic: Doob, J. L.}
\Profile{http://academic.research.microsoft.com/Author/54980421}{Microsoft Academic: Doob, J. L.}


\subsection*{Education}
\Degree{1932}{Ph.D.}{Harvard University}[Boundary Values of Analytic Functions]<http://genealogy.math.ndsu.nodak.edu/id.php?id=4598>


\subsection*{Honors}
\Honor{Joseph}{L. Doob Prize, American Mathematical Society}
\Honor{1950}{IMS President}
\Honor{1957}{National Academy of Sciences, Member}
\Honor{1965}{American Academy of Arts and Sciences, Fellow}
\Honor{1965}{Rietz Lecturer}
\Honor{1975}{Acad\'{e}mie des sciences, Foreign Associate}
\Honor{1979}{National Medal of Science}
\Honor{1984}{Steele Prize, American Mathematical Society}
\Honor{before 1943}{IMS Fellow}


\subsection*{Biographies}
\Biography{doob__joseph_l:24}
\Biography{doob__joseph_l:657909}
\Biography{doob__joseph_l:25}
\Biography{doob__joseph_l:486246}
\Biography{doob__joseph_l:723565}


\subsection*{Autobiography}
\Autobiography{doob__joseph_l:956764}


\subsection*{Death Notice}
\DeathNotice{doob__joseph_l:783464}


\subsection*{Obituaries}
\Obituary{doob__joseph_l:242472}
\Obituary{doob__joseph_l:765788}


\subsection*{Memorials}
\InMemoriam{doob__joseph_l:960670}
\InMemoriam{doob__joseph_l:11}
\InMemoriam{doob__joseph_l:983147}
\InMemoriam{doob__joseph_l:13}
\InMemoriam{doob__joseph_l:14}
\InMemoriam{doob__joseph_l:467916}
\InMemoriam{doob__joseph_l:944565}
\InMemoriam{doob__joseph_l:910312}
\InMemoriam{doob__joseph_l:551039}
\InMemoriam{doob__joseph_l:91996}
\end{document}