% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Eisenhart, Churchill

@misc{eisenhart__churchill:9,
year={1985},
author={Anonymous},
title={{U}ntitled},
addendum={Aspray, W. (1985). Joseph Daly and Churchill Eisenhart. The Princeton Mathematics Community in the 1930s, no. 7. Seeley G. Mudd Manuscript Library, Princeton University},
url={http://www.princeton.edu/~mudd/finding_aids/mathoral/pmc07.htm},
}

@misc{eisenhart__churchill:10,
year={1985},
author={Anonymous},
title={{U}ntitled},
addendum={Aspray, W. (1985). Churchill Eisenhart. The Princeton Mathematics Community in the 1930s, no. 9. Seeley G. Mudd Manuscript Library, Princeton University},
url={http://www.princeton.edu/~mudd/finding_aids/mathoral/pmc09.htm},
}

@misc{eisenhart__churchill:576597,
year={1994},
author={Anonymous},
title={{U}ntitled},
addendum={Churchill Eisenhart, statistics expert, 82. The New York Times, Jul. 1, 1994},
}

@article{eisenhart__churchill:7,
year={1995},
author={Cameron, J. M. and Rosenblatt, J. R.},
title={{C}hurchill {E}isenhart: 1913-94},
journal={IMS Bulletin},
pages={4-5},
volume={24},
}
\end{filecontents}

\begin{document}

\Name{Eisenhart, Churchill} \Deceased
\ID{eisenhart__churchill}




\DOB{1913-03-11}
\DOD{1994-06-25}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=288707}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:eisenhart.churchill}{zbMATH}
\Profile{http://academic.research.microsoft.com/Author/54273632}{Microsoft Academic: Eisenhart, Churchill}
\Profile{http://academic.research.microsoft.com/Author/51708737}{Microsoft Academic: Eisenhart, Churchill}


\subsection*{Honors}
\Honor{1943}{IMS Fellow}
\Honor{1977}{Samuel S. Wilks Award}


\subsection*{Oral History}
\OralHistory{eisenhart__churchill:9}
\OralHistory{eisenhart__churchill:10}


\subsection*{Obituaries}
\Obituary{eisenhart__churchill:576597}
\Obituary{eisenhart__churchill:7}
\end{document}