% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Fienberg, Stephen E.

@misc{fienberg__stephen_e:413531,
year={2012},
author={Anonymous},
title={{U}ntitled},
addendum={Biele, J. Stephen Fienberg: Applying statistics to make a difference. Amstat News, Sept. 2012, pp. 6-8},
}

@misc{fienberg__stephen_e:828756,
year={2013},
author={Anonymous},
title={{U}ntitled},
addendum={Straf, M. L. and Tanur, J. M. (2013). A conversation with Stephen E. Fienberg. Statist. Sci., Vol. 28, pp. 447-463},
}
\end{filecontents}

\begin{document}

\Name{Fienberg, Stephen E.}
\ID{fienberg__stephen_e}
\AltID{fienberg__stephen}

\DisplayName{Fienberg, Stephen}


\Homepage{http://www.stat.cmu.edu/~fienberg/DLindex.html}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=66725}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:fienberg.stephen-e}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=58815}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/320510}{Microsoft Academic: Fienberg, Stephen E.}


\subsection*{Education}
\Degree{1968}{Ph.D.}{Harvard University}[The Estimation of Cell Probabilities in Two-Way Contingency Tables]<http://genealogy.math.ndsu.nodak.edu/id.php?id=58815>


\subsection*{Honors}
\Honor{1973}{IMS Fellow}
\Honor{1982}{COPSS Presidents' Award}
\Honor{1999}{IMS President}
\Honor{1999}{National Academy of Sciences, Member}
\Honor{2000}{Samuel S. Wilks Award}
\Honor{2004}{The Royal Society of Canada, Fellow}
\Honor{2007}{American Academy of Arts and Sciences, Fellow}


\subsection*{Biographies}
\Biography{fienberg__stephen_e:413531}
\Biography{fienberg__stephen_e:828756}
\end{document}