% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Geisser, Seymour

@incollection{geisser__seymour:9,
year={2005},
author={Christensen, R. and Johnson, W.},
title={{G}eisser, {S}eymour},
crossref={booktitle:encyclopedia-of-biostatistics},
}

@article{geisser__seymour:10,
year={2007},
author={Christensen, R. and Johnson, W.},
title={{A} conversation with {S}eymour {G}eisser},
journal={Statist. Sci.},
pages={621-636},
volume={22},
url={http://www.jstor.org/stable/pdfplus/27645866.pdf},
}

@article{geisser__seymour:7,
year={2005},
author={Berry, D. A.},
title={{S}eymour {G}eisser, 1929-2004},
journal={J. Roy. Statist. Soc. Ser. A},
pages={245-246},
volume={168},
url={http://www.jstor.org/stable/3559719},
}

@misc{geisser__seymour:428222,
year={year?},
author={Anonymous},
title={{U}ntitled},
addendum={Website, School of Statistics, University of Minnesota},
url={http://www.stat.umn.edu/Seymour_Geisser_note.html},
}
\end{filecontents}

\begin{document}

\Name{Geisser, Seymour} \Deceased
\ID{geisser__seymour}




\DOB{1929-10-05}
\DOD{2004-03-11}


\Homepage{http://www.stat.umn.edu/Seymour_Geisser_note.html}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Seymour_Geisser}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/geisser.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=72245}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:geisser.seymour}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=41382}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/18641515}{Microsoft Academic: Geisser, Seymour}


\subsection*{Education}
\Degree{1955}{Ph.D.}{The University of North Carolina at Chapel Hill}[On the Exact Distributions of Certain Statistics Related to the Mean Square Successive Difference]<http://genealogy.math.ndsu.nodak.edu/id.php?id=41382>


\subsection*{Honors}
\Honor{1967}{IMS Fellow}


\subsection*{Biographies}
\Biography{geisser__seymour:9}
\Biography{geisser__seymour:10}


\subsection*{Memorials}
\InMemoriam{geisser__seymour:7}
\InMemoriam{geisser__seymour:428222}
\end{document}