% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Hall, W. Jackson

@misc{hall__w_j:518624,
year={2003},
author={Kolassa, J. E. and Oakes, D.},
title={{P}reface},
addendum={In: Crossing Boundaries: Statistical Essays in Honor of Jack Hall (J. E. Kolassa and D. Oakes, eds.). Lecture Notes-Monograph Series, Vol. 43, pp. iv-v. Institute of Mathematical Statistics, Beachwood, OH},
url={http://www.jstor.org/stable/4356257},
}

@misc{hall__w_j:725138,
year={2003},
author={Anonymous},
title={{U}ntitled},
addendum={Kolassa, J. E. and Oakes, D., eds. (2003). Crossing Boundaries: Statistical Essays in Honor of Jack Hall. Lecture Notes-Monograph Series, Vol. 43. Institute of Mathematical Statistics, Beachwood, OH, with portrait},
url={http://www.jstor.org/stable/i397637},
}

@misc{hall__w_j:332659,
year={2012},
author={Anonymous},
title={{U}ntitled},
addendum={Jack Hall, influential statistics expert and former university chair, dies. University of Rochester Medical Center, Oct. 17, 2012},
url={http://www.urmc.rochester.edu/news/story/index.cfm?id=3649},
}

@article{hall__w_j:1,
year={2013},
author={David Oakes and Jon Wellner and Robert Strawderman and Siddhartha Dalal},
title={{O}bituary: {W}. {J}ackson {H}all},
journal={IMS Bulletin},
url={http://bulletin.imstat.org/wp-content/uploads/Bulletin42_1.pdf},
}

@misc{hall__w_j:524999,
year={2013},
author={Anonymous},
title={{U}ntitled},
addendum={Oakes, D., Wellner, J., Strawderman, R. and Dalal, S. (2013). W. Jackson, Hall, 1930-2012. IMS Bulletin, Vol. 42(1), p. 5},
}

@misc{hall__w_j:901945,
year={2013},
author={Anonymous},
title={{U}ntitled},
addendum={Oakes, D., Wellner, J., Strawderman, R. and Dalal, S. (2013). W. Jackson, Hall, 1930-2012. IMS Bulletin, Vol. 42(1), p. 5. Also in Amstat News, Jan. 2013, pp. 34-35},
}
\end{filecontents}

\begin{document}

\Name{Hall, W. Jackson} \Deceased
\ID{hall__w_j}
\AltID{hall__w}

\DisplayName{Hall, W. J.}


\DOB{1929-11-13}
\DOD{2012-10-14}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=80130}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:hall.william-j}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=13421}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/54095274}{Microsoft Academic: Hall, Wm. Jackson}


\subsection*{Education}
\Degree{1955}{Ph.D.}{The University of North Carolina at Chapel Hill}[Most Economical Multiple-Decision Rules]<http://genealogy.math.ndsu.nodak.edu/id.php?id=13421>


\subsection*{Honors}
\Honor{1966}{IMS Fellow}


\subsection*{Biography}
\Biography{hall__w_j:518624}


\subsection*{Festschrift}
\Festschrift{hall__w_j:725138}


\subsection*{Obituaries}
\Obituary{hall__w_j:332659}
\Obituary{hall__w_j:1}


\subsection*{Memorials}
\InMemoriam{hall__w_j:524999}
\InMemoriam{hall__w_j:901945}
\end{document}