% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Johnson, Norman L.

@incollection{johnson__norman_l:10,
year={2006},
author={Read, C. B. and Stokes, L.},
title={{J}ohnson, {N}orman {L}loyd},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@misc{johnson__norman_l:25343,
year={1983},
author={Anonymous},
title={{U}ntitled},
addendum={Sen, P. K., ed. (1983). Contributions to Statistics: Essays in Honor of Norman Lloyd Johnson. North-Holland, Amsterdam.},
}

@article{johnson__norman_l:8,
year={2005},
author={Jasso, G. and Kotz, S.},
title={{N}orman {L}loyd {J}ohnson, 1917-2004},
journal={IMS Bulletin},
pages={9},
volume={34(2)},
}

@misc{johnson__norman_l:577555,
year={2005},
author={Anonymous},
title={{U}ntitled},
addendum={Jasso, G. and Kotz, S. (2005). In memoriam. International Statistical Institute Newsletter, Vol. 29(1)},
}
\end{filecontents}

\begin{document}

\Name{Johnson, Norman L.} \Deceased
\ID{johnson__norman_l}
\AltID{johnson__norman}



\DOB{1917-01-09}
\DOD{2004-11-18}


\Homepage{http://www.math.uiowa.edu/%7Enjohnson/}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=193190}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:johnson.norman-lloyd}{zbMATH}
\Profile{http://zbmath.org/authors/?q=ai:johnson.norman-l}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=10991}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/17917942}{Microsoft Academic: Johnson, Norman L.}


\subsection*{Education}
\Degree{1968}{Ph.D.}{Washington State University}[A Classification of Semi-Translation Planes]<http://genealogy.math.ndsu.nodak.edu/id.php?id=10991>


\subsection*{Honors}
\Honor{1956}{IMS Fellow}
\Honor{1993}{Samuel S. Wilks Award}


\subsection*{Biography}
\Biography{johnson__norman_l:10}


\subsection*{Festschrift}
\Festschrift{johnson__norman_l:25343}


\subsection*{Memorials}
\InMemoriam{johnson__norman_l:8}
\InMemoriam{johnson__norman_l:577555}
\end{document}