% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Kendall, David G.

@incollection{kendall__david_g:15,
year={1998},
author={O'Connor, J. J. and Robertson, E. F.},
title={{D}avid {G}eorge {K}endall},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Kendall.html},
}

@article{kendall__david_g:13,
year={2009},
author={Kingman, J.},
title={{D}avid {G}eorge {K}endall, 15 {J}anuary 1918-23 {O}ctober 2007},
journal={Biogr. Mems. Fell. R. Soc.},
pages={121-138},
volume={55},
}

@incollection{kendall__david_g:14,
year={2011},
author={Kingman, J. F. C.},
title={{K}endall, {D}avid {G}eorge (1918-2007)},
crossref={booktitle:oxford-dictionary-of-national-biography-in-association-with-the-british-academy-from-the-earliest-times-to-the-year-2000},
url={http://www.oxforddnb.com/view/article/99232},
}

@misc{kendall__david_g:352060,
year={2007},
author={Anonymous},
title={{U}ntitled},
addendum={Bingham, N. H. Professor David Kendall, father of British probability. The Independent, Nov. 1, 2007, p. 46},
}

@misc{kendall__david_g:662052,
year={2007},
author={Anonymous},
title={{U}ntitled},
addendum={Professor David Kendall. The Times, Nov. 21, 2007, p. 72; letter, Nov. 29, 2007, p. 80},
}

@article{kendall__david_g:10,
year={2008},
author={Teugels, J.},
title={{D}avid {K}endall remembered},
journal={Bernoulli News},
volume={15(1)},
}

@article{kendall__david_g:11,
year={2008},
author={Bingham, N. H.},
title={{D}avid {G}eorge {K}endall, 1918-2007},
journal={IMS Bulletin},
pages={8},
volume={37(1)},
}

@misc{kendall__david_g:66017,
year={2008},
author={Anonymous},
title={{U}ntitled},
addendum={Bingham, N. H. (2008). Professor D. G. Kendall (1918-2007). International Statistical Institute Newsletter, Vol. 32(2)},
}
\end{filecontents}

\begin{document}

\Name{Kendall, David G.} \Deceased
\ID{kendall__david_g}
\AltID{kendall__david}



\DOB{1918-01-15}
\DOD{2007-10-23}


\Homepage{http://en.wikipedia.org/wiki/David_George_Kendall}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=100195}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:kendall.david-g}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=15004}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/54305929}{Microsoft Academic: Kendall, David G.}
\Profile{http://academic.research.microsoft.com/Author/54305928}{Microsoft Academic: Kendall, David G.}
\Profile{http://academic.research.microsoft.com/Author/12607031}{Microsoft Academic: Kendall, David G.}


\subsection*{Education}
\Degree{1943}{M.A.}{University of Oxford}<http://genealogy.math.ndsu.nodak.edu/id.php?id=15004>


\subsection*{Honors}
\Honor{1955}{Guy Medal in Silver}
\Honor{1964}{The Royal Society, Fellow}
\Honor{1981}{Guy Medal in Gold}
\Honor{19??}{IMS Fellow}


\subsection*{Biographies}
\Biography{kendall__david_g:15}
\Biography{kendall__david_g:13}
\Biography{kendall__david_g:14}


\subsection*{Obituaries}
\Obituary{kendall__david_g:352060}
\Obituary{kendall__david_g:662052}


\subsection*{Memorials}
\InMemoriam{kendall__david_g:10}
\InMemoriam{kendall__david_g:11}
\InMemoriam{kendall__david_g:66017}
\end{document}