% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Kou, S. C. Samuel

@misc{kou__s_c_samuel:995504,
year={2008},
author={Anonymous},
title={{U}ntitled},
addendum={(2008). Samuel Kou appointed Professor of Statistics. Harvard Gazette, Aug. 28},
url={http://news.harvard.edu/gazette/story/2008/08/samuel-kou-appointed-professor-of-statistics/},
}

@article{kou__s_c_samuel:7,
year={2009},
author={Ireland, C.},
title={{K}ou is shaking up the world of statistics},
journal={Harvard Gazette},
}

@misc{kou__s_c_samuel:653762,
year={2009},
author={Anonymous},
title={{U}ntitled},
addendum={Ireland, C. (2009). Kou is shaking up the world of statistics. Harvard Gazette, Feb. 2},
url={http://news.harvard.edu/gazette/story/2009/02/kou-is-shaking-up-the-world-of-statistics/},
}

@misc{kou__s_c_samuel:75090,
year={2009},
author={Anonymous},
title={{U}ntitled},
addendum={Samuel Kou. Amstat News, May 2009, p. 43},
}

@misc{kou__s_c_samuel:594919,
year={2012},
author={Anonymous},
title={{U}ntitled},
addendum={Mukherjee, B. (2012). COPSS Presidents' Award: Samuel Kou. IMS Bulletin, Vol. 41(7), pp. 10-11},
}
\end{filecontents}

\begin{document}

\Name{Kou, S. C. Samuel}
\ID{kou__s_c_samuel}
\AltID{kou__samuel}

\DisplayName{Kou, Samuel}


\Homepage{http://www.stat.harvard.edu/faculty_page.php?page=kou.html}


\subsection*{Profiles}
\Profile{http://zbmath.org/authors/?q=ai:kou.samuel}{zbMATH}
\Profile{http://academic.research.microsoft.com/Author/2853373}{Microsoft Academic: Kou, Samuel}


\subsection*{Honors}
\Honor{2007}{Tweedie New Researcher Award}
\Honor{2009}{IMS Medallion Lecturer}
\Honor{2012}{COPSS Presidents' Award}
\Honor{2012}{IMS Fellow}{For influential and pioneering contributions to stochastic modeling and statistical inference in biophysics, and to Monte Carlo, Bayesian and nonparametric methods}


\subsection*{Biographies}
\Biography{kou__s_c_samuel:995504}
\Biography{kou__s_c_samuel:7}
\Biography{kou__s_c_samuel:653762}
\Biography{kou__s_c_samuel:75090}
\Biography{kou__s_c_samuel:594919}
\end{document}