% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Kurtz, Thomas G.

@misc{kurtz__thomas_g:793012,
year={2008},
author={Anonymous},
title={{U}ntitled},
addendum={Ethier, S. N., Feng, J., and Stockbridge, R. H. (2008). Preface. In Markov Processes and Related Topics: A Festschrift for Thomas G. Kurtz (S. N. Ethier, J. Feng, and R. H. Stockbridge, eds.). Institute of Mathematical Statistics Collections, Vol. 4, pp. vii-viii. Institute of Mathematical Statistics, Beachwood, OH},
}

@misc{kurtz__thomas_g:956547,
year={2008},
author={Anonymous},
title={{U}ntitled},
addendum={Ethier, S. N., Feng, J., and Stockbridge, R. H., eds. (2008). Markov Processes and Related Topics: A Festschrift for Thomas G. Kurtz. Institute of Mathematical Collections, Vol. 4. Institute of Mathematical Statistics, Beachwood, OH},
}
\end{filecontents}

\begin{document}

\Name{Kurtz, Thomas G.}
\ID{kurtz__thomas_g}
\AltID{kurtz__thomas}



\Homepage{http://www.math.wisc.edu/~kurtz/}


\subsection*{Profiles}
\Profile{http://zbmath.org/authors/?q=ai:kurtz.thomas-g}{zbMATH}
\Profile{http://academic.research.microsoft.com/Author/52727579}{Microsoft Academic: Kurtz, T. C.}
\Profile{http://academic.research.microsoft.com/Author/379869}{Microsoft Academic: Kurtz, Thomas G.}


\subsection*{Honors}
\Honor{1979}{IMS Fellow}
\Honor{1980}{IMS Medallion Lecturer}
\Honor{1989}{IMS Medallion Lecturer}
\Honor{2005}{American Academy of Arts and Sciences, Fellow}
\Honor{2006}{IMS President}


\subsection*{Biography}
\Biography{kurtz__thomas_g:793012}


\subsection*{Festschrift}
\Festschrift{kurtz__thomas_g:956547}
\end{document}