% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Lancaster, Henry O.

@misc{lancaster__henry_o:22,
year={1913-2001},
author={Anonymous},
title={{U}ntitled},
addendum={Lancaster, Henry Oliver (1913-2001). Encyclopedia of Australian Science},
url={http://www.eoas.info/biogs/P000556b.htm},
}

@article{lancaster__henry_o:20,
year={2004},
author={Seneta, E. and Eagleson, G. K.},
title={{H}enry {O}liver {L}ancaster 1913-2001},
journal={Historical Records of Australian Science},
pages={223-250},
volume={15},
url={http://www.science.org.au/fellows/memoirs/lancaster.html},
}

@incollection{lancaster__henry_o:21,
year={2005},
author={Armitage, P.},
title={{L}ancaster, {H}enry {O}liver},
crossref={booktitle:encyclopedia-of-biostatistics},
}

@misc{lancaster__henry_o:23,
year={1947},
author={Anonymous},
title={{H}enry {O}liver {L}ancaster-{R}ecords, 1934-1947,},
addendum={MS 103.  Adolph Basser Library, Australian Academy of Science},
}

@misc{lancaster__henry_o:24,
year={1974},
author={Anonymous},
title={{U}ntitled},
addendum={Henry Oliver Lancaster-Records, 1933-1974, DeB 760. National Library of Australia Oral History Collection},
}

@misc{lancaster__henry_o:841488,
year={2001},
author={Anonymous},
title={{U}ntitled},
addendum={Seneta, E. Professor Henry Oliver Lancaster, AO FAA, 1 February 1913-2 December 2001. The University of Sydney News, Mar. 1, 2002},
url={http://www.maths.usyd.edu.au/u/About/lancaster.htm},
}

@misc{lancaster__henry_o:10,
year={2001},
author={Anonymous},
title={{P}rofessor {H}enry {O}liver {L}ancaster, {A}{O}, {F}{A}{A} (1913-2001)},
publisher={Faculty of Science, The University of Sydney},
url={http://sydney.edu.au/science/about_us/fame_lancaster.shtml},
}

@article{lancaster__henry_o:11,
year={2002},
author={Weber, N.},
title={{H}enry {O}liver {L}ancaster, {A}{O}, {F}{A}{A} 1913-2001},
journal={Austral. Math. Soc. Gaz.},
pages={36-37},
volume={29},
}

@article{lancaster__henry_o:12,
year={2002},
author={Seneta, E.},
title={{H}enry {O}liver {L}ancaster, {A}{O}, {F}{A}{A}, {D}{S}c, {M}{D}, {P}h{D}, {M}{B}, {B}{S}, {B}{A}},
journal={Medical J. Australia},
pages={439},
volume={176},
}

@article{lancaster__henry_o:13,
year={2002},
author={Eagleson, G.},
title={{H}enry {O}liver {L}ancaster, {A}{O}, 1913-2001},
journal={IMS Bulletin},
pages={16},
volume={31(2)},
}

@article{lancaster__henry_o:14,
year={2002},
author={Armitage, P.},
title={{P}rofessor {H}enry {O}liver {L}ancaster, 1913-2001},
journal={The Statistician},
pages={566-568},
volume={51},
url={http://www.jstor.org/stable/3650357},
}

@article{lancaster__henry_o:15,
year={2002},
author={Seneta, E.},
title={{I}n memoriam: {P}rofessor {H}enry {O}liver {L}ancaster, {A}{O} {F}{A}{A}, 1 {F}ebruary 1913-2 {D}ecember 2001},
journal={Aust. N. Z. J. Stat.},
pages={385-400},
volume={44},
}

@misc{lancaster__henry_o:506918,
year={2002},
author={Anonymous},
title={{U}ntitled},
addendum={Seneta, E. (2002). Henry Oliver Lancaster (1 February 1913-2 December 2001). International Statistical Institute Newsletter, Vol. 26(1), p. 7},
}

@misc{lancaster__henry_o:191325,
year={2008},
author={Anonymous},
title={{U}ntitled},
addendum={Mellor, L. (2008). Lancaster, Henry Oliver. Faculty of Medicine Online Museum and Archive, University of Sydney},
url={http://sydney.edu.au/medicine/museum/mwmuseum/index.php/Lancaster,_Henry_Oliver},
}
\end{filecontents}

\begin{document}

\Name{Lancaster, Henry O.} \Deceased
\ID{lancaster__henry_o}
\AltID{lancaster__henry}

\DisplayName{Lancaster, Henry Oliver}


\DOB{1913-02-01}
\DOD{2001-12-02}


\Homepage{http://sydney.edu.au/science/about_us/fame_lancaster.shtml}


\subsection*{Profiles}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/lancaster.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=109735}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:lancaster.henry-oliver}{zbMATH}
\Profile{http://academic.research.microsoft.com/Author/12882071}{Microsoft Academic: Lancaster, H. O.}
\Profile{http://academic.research.microsoft.com/Author/54583369}{Microsoft Academic: Lancaster, H. O.}
\Profile{http://academic.research.microsoft.com/Author/54583368}{Microsoft Academic: Lancaster, H. O.}


\subsection*{Honors}
\Honor{1961}{Australian Academy of Science, Fellow}
\Honor{1966}{IMS Fellow}
\Honor{1992}{Officer of the Order of Australia}


\subsection*{Biographies}
\Biography{lancaster__henry_o:22}
\Biography{lancaster__henry_o:20}
\Biography{lancaster__henry_o:21}


\subsection*{Archive}
\Archive{lancaster__henry_o:23}


\subsection*{Oral History}
\OralHistory{lancaster__henry_o:24}


\subsection*{Obituaries}
\Obituary{lancaster__henry_o:841488}
\Obituary{lancaster__henry_o:10}
\Obituary{lancaster__henry_o:11}
\Obituary{lancaster__henry_o:12}


\subsection*{Memorials}
\InMemoriam{lancaster__henry_o:13}
\InMemoriam{lancaster__henry_o:14}
\InMemoriam{lancaster__henry_o:15}
\InMemoriam{lancaster__henry_o:506918}
\InMemoriam{lancaster__henry_o:191325}
\end{document}