% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Lehmann, Erich L.

@misc{lehmann__erich_l:206275,
year={1986},
author={Anonymous},
title={{U}ntitled},
addendum={DeGroot, M. H. (1986). A conversation with Erich L. Lehmann. Statist. Sci., Vol. 1, pp. 243-258},
url={http://www.jstor.org/stable/2245448},
}

@misc{lehmann__erich_l:104568,
year={2009},
author={Anonymous},
title={{U}ntitled},
addendum={Rojo, J. (2009). Erich L. Lehmann, the Lehmann Symposia, and November 20th, 1917. In Optimality: The Third Erich L. Lehmann Symposium (J. Rojo, ed.). Lecture Notes-Monograph Series, Vol. 57, pp. 1-7. Institute of Mathematical Statistics, Beachwood, OH},
url={http://www.jstor.org/stable/30250030},
}

@misc{lehmann__erich_l:984418,
year={2009},
author={Anonymous},
title={{U}ntitled},
addendum={Stigler, S. (2009). The Honorable Erich L. Lehmann. In Optimality: The Third Erich L. Lehmann Symposium (J. Rojo, ed.). Lecture Notes-Monograph Series, Vol. 57, pp. 8-10. Institute of Mathematical Statistics, Beachwood, OH},
url={http://www.jstor.org/stable/30250031},
}

@article{lehmann__erich_l:8,
year={2010},
author={Anonymous},
title={{U}ntitled},
journal={Notices Amer. Math. Soc.},
pages={767},
volume={57},
}

@article{lehmann__erich_l:9,
year={2009},
author={Bickel, P.},
title={{E}rich {L}ehmann, 1917-2009},
journal={IMS Bulletin},
pages={10},
volume={38(9)},
}

@article{lehmann__erich_l:10,
year={2009},
author={Bickel, P. and Lehmann family},
title={{E}rich {L}. {L}ehmann, 1917-2009},
journal={Bernoulli News},
volume={16(2)},
}

@misc{lehmann__erich_l:934620,
year={2010},
author={Anonymous},
title={{U}ntitled},
addendum={Erich Lehmann. Amstat News, Feb. 2010, p. 26},
}
\end{filecontents}

\begin{document}

\Name{Lehmann, Erich L.} \Deceased
\ID{lehmann__erich_l}
\AltID{lehmann__erich}

\DisplayName{Lehmann, Erich}


\DOB{1917-11-20}
\DOD{2009-09-12}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=112000}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:lehmann.erich-l}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=12693}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/17955845}{Microsoft Academic: Lehmann, Erich Leo}


\subsection*{Education}
\Degree{1946}{Ph.D.}{University of California, Berkeley}[Optimum Tests of a Certain Class of Hypotheses Specifying the Value of a Correlation Coefficient]<http://genealogy.math.ndsu.nodak.edu/id.php?id=12693>


\subsection*{Honors}
\Honor{1948}{IMS Fellow}
\Honor{1961}{IMS President}
\Honor{1964}{Wald Lecturer}
\Honor{1975}{American Academy of Arts and Sciences, Fellow}
\Honor{1978}{National Academy of Sciences, Member}
\Honor{1988}{R. A. Fisher Lecturer}
\Honor{1996}{Samuel S. Wilks Award}


\subsection*{Biographies}
\Biography{lehmann__erich_l:206275}
\Biography{lehmann__erich_l:104568}
\Biography{lehmann__erich_l:984418}


\subsection*{Death Notice}
\DeathNotice{lehmann__erich_l:8}


\subsection*{Memorials}
\InMemoriam{lehmann__erich_l:9}
\InMemoriam{lehmann__erich_l:10}
\InMemoriam{lehmann__erich_l:934620}
\end{document}