\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Neyman, Jerzy

@article{neyman__jerzy:16,
year={1974},
author={Le Cam, L. and Lehmann, E. L.},
title={{J}. {N}eyman: {O}n the occasion of his 80th birthday},
journal={Ann. Statist.},
pages={vii-xiii},
volume={2(3)},
}

@inwebcollection{neyman__jerzy:25,
year={1981},
author={Chiang, C. L.},
title={{J}erzy {N}eyman, 1894-1981},
publisher={American {S}tatistical {A}ssociation},
booktitle={Statisticians in {H}istory},
}

@book{neyman__jerzy:17,
year={1982},
author={Reid, C.},
title={{N}eyman—from {L}ife},
publisher={Springer},
}

@article{neyman__jerzy:18,
year={1982},
author={Kendall, D. G., Bartlett, M. S. and Page, T. L.},
title={{J}erzy {N}eyman, 16 {A}pril 1894-5 {A}ugust 1981},
journal={Biogr. Mems. Fell. R. Soc.},
pages={379-412},
volume={28},
}

@article{neyman__jerzy:19,
year={1994},
author={Lehmann, E. L.},
title={{J}erzy {N}eyman, {A}pril 16, 1894-{A}ugust 5, 1981},
journal={Biographical Memoirs},
pages={394-420},
publisher={National Academies Press},
}

@incollection{neyman__jerzy:20,
year={1997},
author={Scott, E. L.},
title={{N}eyman, {J}erzy},
pages={137-145},
crossref={booktitle:leading-personalities-in-statistical-sciences-from-the-17th-century-to-the-present},
}

@incollection{neyman__jerzy:21,
year={2001},
author={Fienberg, S. E. and Tanur, J. M.},
title={{J}erzy {N}eyman},
pages={444-448},
crossref={booktitle:statisticians-of-the-centuries},
}

@inwebcollection{neyman__jerzy:26,
year={2003},
author={O'Connor, J. J. and Robertson, E. F.},
title={{J}erzy {N}eyman},
note={MacTutor biography},
}

@incollection{neyman__jerzy:22,
year={2005},
author={Chiang, C. L.},
title={{N}eyman, {J}erzy},
crossref={booktitle:encyclopedia-of-biostatistics},
}

@incollection{neyman__jerzy:23,
year={2006},
author={Scott, E. L.},
title={{N}eyman, {J}erzy},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@incollection{neyman__jerzy:24,
year={2008},
author={Lehmann, E. L.},
title={{N}eyman, {J}erzy},
pages={669-675},
volume={18},
crossref={booktitle:complete-dictionary-of-scientific-biography},
}

@article{neyman__jerzy:7,
year={1981},
author={Anonymous},
title={{U}ntitled},
journal={IMS Bulletin},
pages={240},
volume={10},
}

@article{neyman__jerzy:8,
year={1982},
author={Hammersley, J. M.},
title={{J}. {N}eyman, 1894-1981},
journal={J. Roy. Statist. Soc. Ser. A},
pages={523-524},
volume={145},
}
\end{filecontents}

\begin{document}

\subsection*{Education}
\Degree{1924}{Ph.D.}{Uniwersytet Warszawski}{Justification of Applications of Calculus of Probability to the Solution of Certain Questions of Agricultural Experimentation}{http://genealogy.math.ndsu.nodak.edu/id.php?id=12694}


\subsection*{Honors}
\Honor{1949}{IMS President}
\Honor{1949}{Rietz Lecturer}
\Honor{1963}{National Academy of Sciences, Member}
\Honor{1966}{Guy Medal in Gold}
\Honor{1968}{National Medal of Science}
\Honor{1968}{Samuel S. Wilks Award}
\Honor{1976}{American Academy of Arts and Sciences, Fellow}
\Honor{1979}{The Royal Society, Foreign Member}
\Honor{before 1943}{IMS Fellow}


\subsection*{Biographies}
\Biography{neyman__jerzy:16}
\Biography{neyman__jerzy:25}
\Biography{neyman__jerzy:17}
\Biography{neyman__jerzy:18}
\Biography{neyman__jerzy:19}
\Biography{neyman__jerzy:20}
\Biography{neyman__jerzy:21}
\Biography{neyman__jerzy:26}
\Biography{neyman__jerzy:22}
\Biography{neyman__jerzy:23}
\Biography{neyman__jerzy:24}


\subsection*{Death Notice}
\DeathNotice{neyman__jerzy:7}


\subsection*{In Memoriam}
\InMemoriam{neyman__jerzy:8}
\end{document}