% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Pearson, Egon S.

@article{pearson__egon_s:12,
year={1981},
author={Bartlett, M. S.},
title={{E}gon {S}harpe {P}earson, 11 {A}ugust 1895-12 {J}une 1980},
journal={Biogr. Mems. Fell. R. Soc.},
pages={425-443},
volume={27},
url={http://www.jstor.org/stable/769879},
}

@incollection{pearson__egon_s:14,
year={2001},
author={Bartholomew, D. J.},
title={{E}gon {S}harpe {P}earson},
pages={373-376},
crossref={booktitle:statisticians-of-the-centuries},
}

@incollection{pearson__egon_s:17,
year={2003},
author={O'Connor, J. J. and Robertson, E. F.},
title={{E}gon {S}harpe {P}earson},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Pearson_Egon.html},
}

@incollection{pearson__egon_s:15,
year={2004},
author={Bartlett, M. S.},
title={{P}earson, {E}gon {S}harpe (1895-1980)},
crossref={booktitle:oxford-dictionary-of-national-biography-in-association-with-the-british-academy-from-the-earliest-times-to-the-year-2000},
url={http://www.oxforddnb.com/view/article/31535},
}

@incollection{pearson__egon_s:16,
year={2005},
author={Anonymous},
title={{P}earson, {E}gon {S}harpe},
crossref={booktitle:encyclopedia-of-biostatistics},
}

@incollection{pearson__egon_s:13,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@misc{pearson__egon_s:302903,
year={1980},
author={Anonymous},
title={{U}ntitled},
addendum={The Times, Jun. 20, 1980, p. 16f},
}

@article{pearson__egon_s:9,
year={year?},
author={Anonymous},
title={{U}ntitled},
publisher={American {S}tatistical {A}ssociation},
booktitle={Statisticians in {H}istory},
url={http://www.amstat.org/about/statisticiansinhistory/bios/pearsonkarl.pdf},
}
\end{filecontents}

\begin{document}

\Name{Pearson, Egon S.} \Deceased
\ID{pearson__egon_s}
\AltID{pearson__egon}



\DOB{1895-08-11}
\DOD{1980-06-12}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=345332}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:pearson.egon-s}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=29652}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/56774510}{Microsoft Academic: Pearson, E. S.}
\Profile{http://academic.research.microsoft.com/Author/56774477}{Microsoft Academic: Pearson, E. S.}


\subsection*{Education}
\Degree{year?}{Ph.D.}{}<http://genealogy.math.ndsu.nodak.edu/id.php?id=29652>


\subsection*{Honors}
\Honor{1944}{IMS Fellow}
\Honor{1946}{Commander of the Order of the British Empire}
\Honor{1955}{Guy Medal in Gold}
\Honor{1966}{The Royal Society, Fellow}


\subsection*{Biographies}
\Biography{pearson__egon_s:12}
\Biography{pearson__egon_s:14}
\Biography{pearson__egon_s:17}
\Biography{pearson__egon_s:15}
\Biography{pearson__egon_s:16}
\Biography{pearson__egon_s:13}


\subsection*{Obituary}
\Obituary{pearson__egon_s:302903}


\subsection*{In Memoriam}
\InMemoriam{pearson__egon_s:9}
\end{document}