% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Pitman, Edwin J. G.

@article{pitman__edwin_j_g:14,
year={1992},
author={Brown, B. M. and Williams, E. J.},
title={{C}onversations with {E}dwin {J}. {G}. {P}itman},
journal={Austral. J. Statist.},
pages={345-360},
volume={34},
url={http://dx.doi.org/10.1111/j.1467-842X.1992.tb01052.x},
}

@misc{pitman__edwin_j_g:18,
year={1993},
author={Anonymous},
title={{P}itman, {E}dwin {J}ames {G}eorge (1897-1993)},
addendum={Encyclopedia of Australian Science},
url={http://www.eoas.info/biogs/P000713b.htm},
}

@article{pitman__edwin_j_g:15,
year={1994},
author={Williams, E. J.},
title={{E}dwin {J}ames {G}eorge {P}itman 1897-1993},
journal={Historical Records of Australian Science},
pages={163-185},
volume={10},
url={http://www.science.org.au/fellows/memoirs/pitman.html},
}

@incollection{pitman__edwin_j_g:17,
year={2001},
author={Williams, E. J.},
title={{E}dwin {J}ames {G}eorge {P}itman},
pages={468-471},
crossref={booktitle:statisticians-of-the-centuries},
}

@incollection{pitman__edwin_j_g:16,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@incollection{pitman__edwin_j_g:19,
year={2011},
author={O'Connor, J. J. and Robertson, E. F.},
title={{E}dwin {J}ames {G}eorge {P}itman, 1897-1993},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Pitman.html},
}

@misc{pitman__edwin_j_g:22,
year={1993},
author={Anonymous},
title={{E}dwin {J}ames {G}eorge {P}itman -- {R}ecords, 1922-1993},
addendum={University of Tasmania Library, Special/Rare Collection UT543},
}

@incollection{pitman__edwin_j_g:8,
year={1982},
author={Pitman, E. J. G.},
title={{R}eminiscences of a mathematician who strayed into statistics},
pages={112-125},
crossref={booktitle:making-of-statisticians},
}

@misc{pitman__edwin_j_g:21,
year={1981},
author={Pitman, E. J. G.},
title={{R}eminiscences of a mathematician who strayed into statistics},
addendum={Distinguished Statistician Video Series, DS004. Pfizer, University of Connecticut-Storrs and American Statistical Association.},
url={http://www.amstat.org},
}

@article{pitman__edwin_j_g:9,
year={1993},
author={Williams, E. J.},
title={{E}dward {J}ames {G}eorge {P}itman, 1897-1993},
journal={IMS Bulletin},
pages={448-449},
volume={22},
}

@article{pitman__edwin_j_g:11,
year={1993},
author={Lipton, S.},
title={{E}. {J}. {G}. {P}itman},
journal={Austral. J. Statist.},
pages={246},
volume={35},
}

@article{pitman__edwin_j_g:10,
year={1994},
author={Sprent, P.},
title={{E}. {J}. {G}. {P}itman, 1897-1993},
journal={J. Roy. Statist. Soc. Ser. A},
volume={157},
url={http://www.jstor.org/stable/2983511},
}
\end{filecontents}

\begin{document}

\Name{Pitman, Edwin J. G.} \Deceased
\ID{pitman__edwin_j_g}
\AltID{pitman__edwin}



\DOB{1897-10-29}
\DOD{1993-07-21}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/E._J._G._Pitman}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/pitman.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=140075}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:pitman.e-j-g}{zbMATH}
\Profile{http://zbmath.org/authors/?q=ai:pitman.e-g-j}{zbMATH}
\Profile{http://academic.research.microsoft.com/Author/55081613}{Microsoft Academic: Pitman, E. J. G.}
\Profile{http://academic.research.microsoft.com/Author/10864537}{Microsoft Academic: Pitman, E. J. G.}


\subsection*{Honors}
\Honor{1948}{IMS Fellow}
\Honor{1954}{Australian Academy of Science, Member}
\Honor{1978}{Pitman Medal, Statistical Society of Australia}


\subsection*{Biographies}
\Biography{pitman__edwin_j_g:14}
\Biography{pitman__edwin_j_g:18}
\Biography{pitman__edwin_j_g:15}
\Biography{pitman__edwin_j_g:17}
\Biography{pitman__edwin_j_g:16}
\Biography{pitman__edwin_j_g:19}


\subsection*{Archive}
\Archive{pitman__edwin_j_g:22}


\subsection*{Autobiography}
\Autobiography{pitman__edwin_j_g:8}


\subsection*{DVD}
\DVD{pitman__edwin_j_g:21}


\subsection*{Obituary}
\Obituary{pitman__edwin_j_g:9}


\subsection*{Memorials}
\InMemoriam{pitman__edwin_j_g:11}
\InMemoriam{pitman__edwin_j_g:10}
\end{document}