% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Raghavarao, Damaraju

@misc{raghavarao__damaraju:497301,
year={2001},
author={Anonymous},
title={{U}ntitled},
addendum={Altan, S. and Singh, J., eds. (2001). Recent Advances in Experimental Design and Related Topics. Nova Science Publishers, Huntington, NY},
}

@misc{raghavarao__damaraju:247254,
year={2013},
author={Anonymous},
title={{U}ntitled},
addendum={Lausch, B. (2013). Fox mourns the passing of longtime Statistics Professor Damaraju Raghavarao. Fox School of Business, Temple University, Feb. 11},
url={http://www.fox.temple.edu/posts/2013/02/fox-school-mourns-the-passing-of-longtime-statistics-professor-damaraju-raghavarao/},
}

@misc{raghavarao__damaraju:923222,
year={2013},
author={Anonymous},
title={{U}ntitled},
addendum={Singh, J. and Altan, S. (2013). Damaraju Raghavarao, 1938-2013. IMS Bulletin, Vol. 42(3), p. 6. Also in Amstat News, April 2013},
}
\end{filecontents}

\begin{document}

\Name{Raghavarao, Damaraju} \Deceased
\ID{raghavarao__damaraju}




\DOB{1938-01-05}
\DOD{2013-02-06}


\subsection*{Profiles}
\Profile{https://en.wikipedia.org/wiki/D._Raghavarao}{Wikipedia}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=143940}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:raghavarao.damaraju}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=48224}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/53959228}{Microsoft Academic: Raghavarao, Damaraju}


\subsection*{Education}
\Degree{1961}{Ph.D.}{University of Mumbai}[Some Contributions to the Design of Experiments]<http://genealogy.math.ndsu.nodak.edu/id.php?id=48224>


\subsection*{Honors}
\Honor{1975}{IMS Fellow}


\subsection*{Festschrift}
\Festschrift{raghavarao__damaraju:497301}


\subsection*{Memorials}
\InMemoriam{raghavarao__damaraju:247254}
\InMemoriam{raghavarao__damaraju:923222}
\end{document}