% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Rota, Gian-Carlo

@article{rota__gian-carlo:16,
year={1979},
author={Kolata, G. B.},
title={{G}ian-{C}arlo {R}ota and combinatorial math},
journal={Science},
pages={44-45},
volume={204},
url={http://www.jstor.org/stable/1747960},
}

@incollection{rota__gian-carlo:20,
year={2000},
author={O'Connor, J. J. and Robertson, E. F.},
title={{G}ian-{C}arlo {R}ota},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Rota.html},
}

@article{rota__gian-carlo:17,
year={2001},
author={Anonymous},
title={{I}nterview with {G}ian-{C}arlo {R}ota},
journal={Lect. Mat.},
pages={67-79},
volume={22},
}

@incollection{rota__gian-carlo:18,
year={2008},
author={Stanley, R.},
title={{R}ota, {G}ian-{C}arlo},
pages={285-287},
volume={24},
crossref={booktitle:complete-dictionary-of-scientific-biography},
}

@incollection{rota__gian-carlo:19,
year={2010},
author={Senato, D.},
title={{G}ian-{C}arlo {R}ota: {M}athematician and philosopher},
pages={181-189},
crossref={booktitle:mathematical-lives-protagonists-of-the-twentieth-century-from-hilbert-to-wiles},
}

@article{rota__gian-carlo:7,
year={1999},
author={Anonymous},
title={{U}ntitled},
journal={Notices Amer. Math. Soc.},
pages={686},
volume={46},
}

@misc{rota__gian-carlo:137503,
year={1999},
author={Anonymous},
title={{U}ntitled},
addendum={MIT professor Gian-Carlo Rota, mathematician and philosopher, is dead at 66. MIT news, April 22, 1999},
url={http://web.mit.edu/newsoffice/1999/rota.html},
}

@misc{rota__gian-carlo:826914,
year={1999},
author={Anonymous},
title={{U}ntitled},
addendum={Gian-Carlo Rota, 66, professor of mathematics and philosophy. The New York Times, May 1, 1999},
}

@article{rota__gian-carlo:11,
year={2000},
author={Di Crescenzo, A.},
title={{G}ian-{C}arlo {R}ota},
journal={Math. Sci.},
pages={61-62},
volume={25},
}

@misc{rota__gian-carlo:994945,
year={21},
author={Anonymous},
title={{U}ntitled},
addendum={Gian-Carlo Rota. The Tech, Vol. 19(21), April 23, 1999},
url={http://tech.mit.edu/V119/N21/21rota.21n.html},
}

@article{rota__gian-carlo:12,
year={2000},
author={Beschler, E. F. and Buchsbaum, D. A. and Schwartz, J. T. and Stanley, R. P. and Taylor, B. D. and Waterman, M.},
title={{G}ian-{C}arlo {R}ota (1932-1999)},
journal={Notices Amer. Math. Soc.},
pages={203-216},
volume={47},
url={http://www.ams.org/notices/200002/mem-rota.pdf},
}
\end{filecontents}

\begin{document}

\Name{Rota, Gian-Carlo} \Deceased
\ID{rota__gian-carlo}




\DOB{1932-04-27}
\DOD{1999-04-18}


\Homepage{http://www.ruf.rice.edu/~dulab/}
\Homepage{http://faculty.uml.edu/dklain/rota.html}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Gian-Carlo_Rota}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/rota.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=150900}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:rota.gian-carlo}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=7721}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/23351374}{Microsoft Academic: Rota, Gian-Carlo}
\Profile{http://academic.research.microsoft.com/Author/55574557}{Microsoft Academic: Rota, Gian-Carlo}


\subsection*{Education}
\Degree{1956}{Ph.D.}{Yale University}[Extension Theory of Differential Operators]<http://genealogy.math.ndsu.nodak.edu/id.php?id=7721>


\subsection*{Honors}
\Honor{1963}{American Academy of Arts and Sciences, Fellow}
\Honor{1970}{IMS Fellow}
\Honor{1982}{National Academy of Arts and Sciences, Member}
\Honor{1988}{Steele Prize, American Mathematical Society}


\subsection*{Biographies}
\Biography{rota__gian-carlo:16}
\Biography{rota__gian-carlo:20}
\Biography{rota__gian-carlo:17}
\Biography{rota__gian-carlo:18}
\Biography{rota__gian-carlo:19}


\subsection*{Death Notice}
\DeathNotice{rota__gian-carlo:7}


\subsection*{Obituaries}
\Obituary{rota__gian-carlo:137503}
\Obituary{rota__gian-carlo:826914}
\Obituary{rota__gian-carlo:11}
\Obituary{rota__gian-carlo:994945}


\subsection*{In Memoriam}
\InMemoriam{rota__gian-carlo:12}
\end{document}