% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Rubin, Herman

@misc{rubin__herman:51858,
year={2004},
author={Anonymous},
title={{U}ntitled},
addendum={Chernoff, H. (2004). Some reminiscences of my friendship with Herman Rubin. In A Festschrift for Herman Rubin (A. DasGupta, ed.). Lecture Notes-Monograph Series, Vol. 45, pp. 1-4. Institute of Mathematical Statistics, Beachwood, OH},
url={http://www.jstor.org/stable/4356294},
}

@misc{rubin__herman:694299,
year={2004},
author={Anonymous},
title={{U}ntitled},
addendum={Bock, M. E. (2004). Conversations with Herman Rubin. In A Festschrift for Herman Rubin (A. DasGupta, ed.). Lecture Notes-Monograph Series, Vol. 45, pp. 408-417. Institute of Mathematical Statistics, Beachwood, OH},
url={http://www.jstor.org/stable/4356327},
}

@misc{rubin__herman:2977,
year={2004},
author={Anonymous},
title={{U}ntitled},
addendum={DasGupta, A. ed. (2004). A Festschrift for Herman Rubin. Lecture Notes-Monograph Series, Vol. 45. Institute of Mathematical Statistics, Beachwood, OH, with portrait},
url={http://www.jstor.org/stable/i397659},
}
\end{filecontents}

\begin{document}

\Name{Rubin, Herman}
\ID{rubin__herman}




\Homepage{http://www.math.purdue.edu/people/bio/hrubin}
\Homepage{http://www.math.purdue.edu/people/bio/hrubin/Publications}
\Homepage{http://www.math.purdue.edu/people/bio/hrubin/Publications}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=192890}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:rubin.herman}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=6399}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/18644235}{Microsoft Academic: Rubin, Herman}
\Profile{http://academic.research.microsoft.com/Author/53363633}{Microsoft Academic: Rubin, Herman}
\Profile{http://academic.research.microsoft.com/Author/53363646}{Microsoft Academic: Rubin, Herman}


\subsection*{Education}
\Degree{1948}{Ph.D.}{The University of Chicago}[Systems of Linear Stochastic Equations]<http://genealogy.math.ndsu.nodak.edu/id.php?id=6399>


\subsection*{Honors}
\Honor{1950}{IMS Fellow}


\subsection*{Biographies}
\Biography{rubin__herman:51858}
\Biography{rubin__herman:694299}


\subsection*{Festschrift}
\Festschrift{rubin__herman:2977}
\end{document}