\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Scott, Elizabeth L.

@article{scott__elizabeth_l:15,
year={1990},
author={Stinnett, S., et al.},
title={{W}omen in statistics: {S}esquicentennial activities},
note={see p. 78},
journal={Amer. Statist.},
pages={74-80},
volume={44},
}

@article{scott__elizabeth_l:16,
year={1991},
author={Billard, L. and Ferber, M. A.},
title={{E}lizabeth {S}cott: {S}cholar, teacher, administrator},
journal={Statist. Sci.},
pages={206-216},
volume={6},
}

@incollection{scott__elizabeth_l:17,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@incollection{scott__elizabeth_l:19,
year={2007},
author={Webb, F. and Robertson, E. F.},
title={{E}lizabeth {L}eonard {S}cott},
note={MacTutor biography},
}

@misc{scott__elizabeth_l:18,
year={year?},
author={Anonymous},
title={{E}lizabeth {S}cott},
booktitle={Agnes {S}cott {C}ollege {W}ebsite},
}

@misc{scott__elizabeth_l:177620,
year={1983},
author={Anonymous},
title={{U}ntitled},
}

@misc{scott__elizabeth_l:468458,
year={1988},
author={Anonymous},
title={{U}ntitled},
}

@article{scott__elizabeth_l:9,
year={1989},
author={Le Cam, L.},
title={{E}lizabeth {L}eonard {S}cott, 1917-1988},
journal={IMS Bulletin},
pages={80},
volume={18},
}

@article{scott__elizabeth_l:10,
year={1990},
author={David, F. N.},
title={{E}lizabeth {S}cott, 1917-88},
journal={J. Roy. Statist. Soc. Ser. A},
pages={100},
volume={153},
}

@article{scott__elizabeth_l:11,
year={1989},
author={Flournoy, N.},
title={{I}n memory of {E}lizabeth {S}cott},
journal={Newsletter of the Caucus for Women in Statistics},
pages={5-6},
volume={19},
}

@misc{scott__elizabeth_l:9922,
year={1989},
author={Anonymous},
title={{U}ntitled},
}
\end{filecontents}

\begin{document}

\Name{Scott, Elizabeth L.}
\DOB{1917-11-23}
\DOD{1988-12-20}


\subsection*{Education}
\Degree{1981}{Ph.D.}{University of Oxford}{Finitely presented infinite simple groups}{http://genealogy.math.ndsu.nodak.edu/id.php?id=30379}


\subsection*{Honors}
\Honor{Elizabeth}{L. Scott Award, Committee of Presidents of Statistical Societies}
\Honor{1951}{IMS Fellow}
\Honor{1978}{IMS President}


\subsection*{Biographies}
\Biography{scott__elizabeth_l:15}
\Biography{scott__elizabeth_l:16}
\Biography{scott__elizabeth_l:17}
\Biography{scott__elizabeth_l:19}
\Biography{scott__elizabeth_l:18}


\subsection*{Oral History}
\OralHistory{scott__elizabeth_l:177620}


\subsection*{Obituaries}
\Obituary{scott__elizabeth_l:468458}
\Obituary{scott__elizabeth_l:9}
\Obituary{scott__elizabeth_l:10}


\subsection*{Memorials}
\InMemoriam{scott__elizabeth_l:11}
\InMemoriam{scott__elizabeth_l:9922}
\end{document}