% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Scott, Elizabeth L.

@article{scott__elizabeth_l:15,
year={1990},
author={Stinnett, S., et al.},
title={{W}omen in statistics: {S}esquicentennial activities},
addendum={see p. 78},
journal={Amer. Statist.},
pages={74-80},
volume={44},
url={http://www.jstor.org/stable/2684131},
}

@article{scott__elizabeth_l:16,
year={1991},
author={Billard, L. and Ferber, M. A.},
title={{E}lizabeth {S}cott: {S}cholar, teacher, administrator},
journal={Statist. Sci.},
pages={206-216},
volume={6},
url={http://www.jstor.org/stable/2245598},
}

@incollection{scott__elizabeth_l:17,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@incollection{scott__elizabeth_l:19,
year={2007},
author={Webb, F. and Robertson, E. F.},
title={{E}lizabeth {L}eonard {S}cott},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Scott_Elizabeth.html},
}

@misc{scott__elizabeth_l:18,
year={year?},
author={Anonymous},
title={{E}lizabeth {S}cott},
booktitle={Agnes {S}cott {C}ollege {W}ebsite},
url={http://www.agnesscott.edu/lriddle/women/escott.htm},
}

@misc{scott__elizabeth_l:177620,
year={1983},
author={Scott, E.},
title={{A}n oral history with {E}lizabeth {S}cott},
addendum={Interview conducted by S. B. Riess in 1981. In The Women's Faculty Club of the University of California, Berkeley, 1919-1982, pp. 149-169. Regional Oral History Office, The Bancroft Library, University of California, Berkeley},
url={http://www.ebooksread.com/authors-eng/bancroft-library-regional-oral-history-office/the-womens-faculty-club-of-the-unversity-of-california-berkeley-1919-1982--o-hci/1-the-womens-faculty-club-of-the-unversity-of-california-berkeley-1919-1982--o-hci.shtml},
}

@misc{scott__elizabeth_l:468458,
year={1988},
author={Anonymous},
title={{E}lizabeth {S}cott; {P}rofessor and feminist},
addendum={Los Angeles Times, Dec. 22, 1988},
}

@article{scott__elizabeth_l:9,
year={1989},
author={Le Cam, L.},
title={{E}lizabeth {L}eonard {S}cott, 1917-1988},
journal={IMS Bulletin},
pages={80},
volume={18},
}

@article{scott__elizabeth_l:10,
year={1990},
author={David, F. N.},
title={{E}lizabeth {S}cott, 1917-88},
journal={J. Roy. Statist. Soc. Ser. A},
pages={100},
volume={153},
url={http://www.jstor.org/stable/2983101},
}

@article{scott__elizabeth_l:11,
year={1989},
author={Flournoy, N.},
title={{I}n memory of {E}lizabeth {S}cott},
journal={Newsletter of the Caucus for Women in Statistics},
pages={5-6},
volume={19},
}

@misc{scott__elizabeth_l:9922,
year={1989},
author={Blackwell, D. and Colson, E. and Ervin-Tripp, S. and Le Cam, L. and Lehmann, E. and Nader, L.},
title={{E}lizabeth {L}eonard {S}cott, {S}tatistics: {B}erkeley},
addendum={University of California: In memoriam},
url={http://content.cdlib.org/view?docId=hb4t1nb2bd&doc.view=frames&chunk.id=div00061&toc.depth=1&toc.id=},
}
\end{filecontents}

\begin{document}

\Name{Scott, Elizabeth L.} \Deceased
\ID{scott__elizabeth_l}
\AltID{scott__elizabeth}

\DisplayName{Scott, Elizabeth}


\DOB{1917-11-23}
\DOD{1988-12-20}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Elizabeth_Scott_%28mathematician%29}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/neyman_and_s.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=290141}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:scott.elizabeth-l}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=30379}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/54240741}{Microsoft Academic: Elizabeth L. Scott}
\Profile{http://academic.research.microsoft.com/Author/42500538}{Microsoft Academic: Elizabeth L. Scott}
\Profile{http://academic.research.microsoft.com/Author/56327645}{Microsoft Academic: Elizabeth L. Scott}
\Profile{http://academic.research.microsoft.com/Author/46979978}{Microsoft Academic: Elizabeth L. Scott}
\Profile{http://academic.research.microsoft.com/Author/52870914}{Microsoft Academic: ELIZABETH L SCOTT}
\Profile{http://academic.research.microsoft.com/Author/46971491}{Microsoft Academic: Elizabeth L. Scott}


\subsection*{Education}
\Degree{1981}{Ph.D.}{University of Oxford}[Finitely presented infinite simple groups]<http://genealogy.math.ndsu.nodak.edu/id.php?id=30379>


\subsection*{Honors}
\Honor{Elizabeth}{L. Scott Award, Committee of Presidents of Statistical Societies}
\Honor{1951}{IMS Fellow}
\Honor{1978}{IMS President}


\subsection*{Biographies}
\Biography{scott__elizabeth_l:15}
\Biography{scott__elizabeth_l:16}
\Biography{scott__elizabeth_l:17}
\Biography{scott__elizabeth_l:19}
\Biography{scott__elizabeth_l:18}


\subsection*{Oral History}
\OralHistory{scott__elizabeth_l:177620}


\subsection*{Obituaries}
\Obituary{scott__elizabeth_l:468458}
\Obituary{scott__elizabeth_l:9}
\Obituary{scott__elizabeth_l:10}


\subsection*{Memorials}
\InMemoriam{scott__elizabeth_l:11}
\InMemoriam{scott__elizabeth_l:9922}
\end{document}