% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Sen, Pranab K.

@misc{sen__pranab_k:654435,
year={2008},
author={Anonymous},
title={{U}ntitled},
addendum={Balakrishnan, N., Pe\~{n}a, E. A., and M. J. Silvapulle. (2008). Pranab Kumar Sen: Life and works. In Beyond Parametrics in Interdisciplinary Research: Festschrift in Honor of Pranab K. Sen (N. Balakrishnan, E. A. Pe\~{n}a, and M. J. Silvapulle, eds.). Institute of Mathematical Statistics Collections, Vol. 1, pp. 1-16. Institute of Mathematical Statistics, Beachwood, OH},
}

@misc{sen__pranab_k:369354,
year={2008},
author={Anonymous},
title={{U}ntitled},
addendum={Balakrishnan, N., Pe\~{n}a, E. A., and Silvapulle, M. J., eds. (2008). Beyond Parametrics in Interdisciplinary Research: Festschrift in Honor of Pranab K. Sen. Institute of Mathematical Collections, Vol. 1. Institute of Mathematical Statistics, Beachwood, OH, with portrait},
}
\end{filecontents}

\begin{document}

\Name{Sen, Pranab K.}
\ID{sen__pranab_k}
\AltID{sen__pranab}



\Homepage{http://www.sph.unc.edu/?option=com_profiles&amp;profileAction=ProfDetail&amp;pid=704289903}
\Homepage{http://stat-or.unc.edu/people/faculty/pranab-k.-sen}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=190086}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:kumar-sen.pranab}{zbMATH}
\Profile{http://zbmath.org/authors/?q=ai:sen.pranab-kumari}{zbMATH}
\Profile{http://zbmath.org/authors/?q=ai:sen.pranab-kumar}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=18736}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/12597789}{Microsoft Academic: Sen, Pranab Kumar}
\Profile{http://academic.research.microsoft.com/Author/1063050}{Microsoft Academic: Sen, Pranab}


\subsection*{Education}
\Degree{1962}{Ph.D.}{Calcutta University}[Order Statistics and Their Role in Some Problems of Statistical Inference]<http://genealogy.math.ndsu.nodak.edu/id.php?id=18736>


\subsection*{Honors}
\Honor{1968}{IMS Fellow}
\Honor{2010}{Samuel S. Wilks Award}


\subsection*{Biography}
\Biography{sen__pranab_k:654435}


\subsection*{Festschrift}
\Festschrift{sen__pranab_k:369354}
\end{document}