% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Snell, J. Laurie

@misc{snell__j_laurie:307701,
year={2008},
author={Snell, J. Laurie},
title={{U}ntitled},
addendum={Dartmouth College website},
url={http://www.dartmouth.edu/~chance/Lauriev.html},
}

@article{snell__j_laurie:8,
year={2011},
author={Anonymous},
title={{U}ntitled},
journal={Notices Amer. Math. Soc.},
pages={844},
volume={58},
}

@misc{snell__j_laurie:414933,
year={2011},
author={Anonymous},
title={{U}ntitled},
addendum={(2011). Notices Amer. Math. Soc., Vol. 58, p. 844},
}

@misc{snell__j_laurie:329025,
year={2011},
author={Anonymous},
title={{J}ames {L}aurie {S}nell, {M}arch 19, 2011},
addendum={Rand-Wilson Funeral Home.},
url={http://rand-wilson.com/obituaries/obit_view.php?id=9},
}

@misc{snell__j_laurie:683789,
year={2011},
author={Anonymous},
title={{I}n memory of {J}. {L}aurie {S}nell (1925-2011)},
addendum={Newsletter, Department of Mathematics, Dartmouth College. Sept. 2011},
}

@misc{snell__j_laurie:870392,
year={2011},
author={Anonymous},
title={{U}ntitled},
addendum={Rockmore, D. J. Laurie Snell. Amstat News, June 2011, p. 35},
}

@misc{snell__j_laurie:432376,
year={2012},
author={Rockmore, D.},
title={{O}ne in a million---remembrances of {L}aurie {S}nell (1925-2011)},
addendum={Notices Amer. Math. Soc., Vol. 59, pp. 1256-1260},
url={http://www.ams.org/notices/201209/rtx120901256p.pdf},
}
\end{filecontents}

\begin{document}

\Name{Snell, J. Laurie} \Deceased
\ID{snell__j_laurie}
\AltID{snell__j}



\DOB{1925-01-15}
\DOD{2011-03-19}


\Homepage{http://www.jsnell.com/}


\subsection*{Profiles}
\Profile{https://en.wikipedia.org/wiki/J._Laurie_Snell}{Wikipedia}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=246030}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:snell.j-laurie}{zbMATH}
\Profile{http://zbmath.org/authors/?q=ai:snell.james-l}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=4213}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/115312}{Microsoft Academic: Snell, J. Laurie}


\subsection*{Education}
\Degree{1951}{Ph.D.}{University of Illinois at Urbana-Champaign}[Applications of Martingale System Theorems]<http://genealogy.math.ndsu.nodak.edu/id.php?id=4213>


\subsection*{Honors}
\Honor{1972}{IMS Fellow}


\subsection*{Autobiography}
\Autobiography{snell__j_laurie:307701}


\subsection*{Death Notices}
\DeathNotice{snell__j_laurie:8}
\DeathNotice{snell__j_laurie:414933}


\subsection*{Obituary}
\Obituary{snell__j_laurie:329025}


\subsection*{Memorials}
\InMemoriam{snell__j_laurie:683789}
\InMemoriam{snell__j_laurie:870392}
\InMemoriam{snell__j_laurie:432376}
\end{document}