% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Speed, Terence P.

@misc{speed__terence_p:718636,
year={2003},
author={Anonymous},
title={{U}ntitled},
addendum={(2003). Preface. In Statistics and Science: A Festschrift for Terry Speed (D. R. Goldstein, ed.). Lecture Notes-Monograph Series, Vol. 40, pp. i-ii. Institute of Mathematical Statistics, Beachwood, OH},
url={http://www.jstor.org/stable/4356175},
}

@misc{speed__terence_p:895299,
year={2003},
author={Anonymous},
title={{U}ntitled},
addendum={Goldstein, D. R., ed. (2003). Statistics and Science: A Festschrift for Terry Speed. Lecture Notes-Monograph Series, Vol. 40. Institute of Mathematical Statistics, Beachwood, OH, with portrait},
url={http://www.jstor.org/stable/i397614},
}
\end{filecontents}

\begin{document}

\Name{Speed, Terence P.}
\ID{speed__terence_p}
\AltID{speed__terence}

\DisplayName{Speed, Terence}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=190612}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:speed.terence-p}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=30979}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/42297999}{Microsoft Academic: Speed, Terry}
\Profile{http://academic.research.microsoft.com/Author/12600871}{Microsoft Academic: Speed, T. P.}
\Profile{http://scholar.google.be/citations?user=Sg6_CmwAAAAJ&hl=en}{Google Scholar}


\subsection*{Education}
\Degree{1968}{Ph.}{D. Monash University}[Some Topics in the Theory of Distributive Lattices]<http://genealogy.math.ndsu.nodak.edu/id.php?id=30979>


\subsection*{Honors}
\Honor{1984}{IMS Fellow}
\Honor{1986}{IMS Medallion Lecturer}
\Honor{1991}{Rietz Lecturer}
\Honor{2001}{Australian Academy of Science, Fellow}
\Honor{2001}{Wald Lecturer}
\Honor{2004}{IMS President}
\Honor{2006}{R. A. Fisher Lecturer}
\Honor{2012}{Faculty Research Lecturer, University of California, Berkeley}
\Honor{2013}{The Royal Society, Fellow}


\subsection*{Biography}
\Biography{speed__terence_p:718636}


\subsection*{Festschrift}
\Festschrift{speed__terence_p:895299}
\end{document}