% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Strawderman, William E.

@misc{strawderman__william_e:612046,
year={2012},
author={Anonymous},
title={{U}ntitled},
addendum={(2012). Biography of William E. Strawderman. In Contemporary Developments in Bayesian Analysis and Statistical Decision Theory: A Festschrift for William E. Strawderman (D. Fourdrinier, E. Marchand, and A. L. Rukhin, eds.). Institute of Mathematical Statistics Collections, Vol. 8, pp. viii-ix. Institute of Mathematical Statistics, Beachwood, OH},
}

@misc{strawderman__william_e:206071,
year={2012},
author={Anonymous},
title={{U}ntitled},
addendum={Fourdrinier, D., Marchand, E., and Rukhin, A. L., eds. (2012). Contemporary Developments in Bayesian Analysis and Statistical Decision Theory: A Festschrift for William E. Strawderman. Institute of Mathematical Collections, Vol. 8. Institute of Mathematical Statistics, Beachwood, OH, with portrait},
}
\end{filecontents}

\begin{document}

\Name{Strawderman, William E.}
\ID{strawderman__william_e}
\AltID{strawderman__william}



\Homepage{http://stat.rutgers.edu/people/faculty/straw.html}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=168090}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:strawderman.william-edward}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=46338}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/8200469}{Microsoft Academic: Strawderman, William E.}


\subsection*{Education}
\Degree{1969}{Ph.D.}{Rutgers University, New Brunswick}[Generalized Bayes Estimators and Admissibility of Estimators of the Mean Vector of a Multivariate Normal Distribution with Quadratic Loss]<http://genealogy.math.ndsu.nodak.edu/id.php?id=46338>


\subsection*{Honors}
\Honor{1980}{IMS Fellow}
\Honor{2001}{IMS Medallion Lecturer}


\subsection*{Biography}
\Biography{strawderman__william_e:612046}


\subsection*{Festschrift}
\Festschrift{strawderman__william_e:206071}
\end{document}