% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Tukey, John W.

@incollection{tukey__john_w:23,
year={2000},
author={Kafadar, K. and Grier, D. A.},
title={{J}ohn {W}. {T}ukey, 1915-2000},
publisher={American {S}tatistical {A}ssociation},
booktitle={Statisticians in {H}istory},
url={http://www.amstat.org/about/statisticiansinhistory/index.cfm?fuseaction=biosinfo&BioID=14},
}

@article{tukey__john_w:19,
year={2003},
author={McCullagh, P.},
title={{J}ohn {W}ilder {T}ukey, 16 {J}une 1915-26 {J}uly 2000},
journal={Biogr. Mems. Fell. R. Soc.},
pages={537-555},
volume={49},
url={http://www.jstor.org/stable/3650242},
}

@incollection{tukey__john_w:24,
year={2004},
author={O'Connor, J. J. and Robertson, E. F.},
title={{J}ohn {W}ilder {T}ukey},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Tukey.html},
}

@incollection{tukey__john_w:20,
year={2005},
author={Kafadar, K.},
title={{T}ukey, {J}ohn {W}ilder},
crossref={booktitle:encyclopedia-of-biostatistics},
}

@article{tukey__john_w:21,
year={2005},
author={Mosteller, F.},
title={{J}ohn {W}. {T}ukey, 16 {J}une 1915-26 {J}uly 2000},
journal={Proc. Amer. Philos. Soc.},
pages={625-630},
volume={149},
url={http://www.jstor.org/stable/4598966},
}

@incollection{tukey__john_w:22,
year={2006},
author={Brillinger, D. R.},
title={{T}ukey, {J}ohn {W}ilder},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@incollection{tukey__john_w:25,
year={2000},
author={Anonymous},
title={{J}ohn {W}. {T}ukey {P}apers, 1937-2000},
addendum={Site includes biographical entry},
volume={Mss.{M}s.{C}oll.117},
booktitle={Library, {A}merican {P}hilosophical {S}ociety},
url={http://www.amphilsoc.org/mole/view?docId=ead/Mss.Ms.Coll.117-ead.xml},
}

@misc{tukey__john_w:26,
year={1985},
author={Anonymous},
title={{U}ntitled},
addendum={Aspray, W. and Tucker, A. (1985). John Tukey. The Princeton Mathematics Community in the 1930s, no. 41. Seeley G. Mudd Manuscript Library, Princeton University},
url={http://www.princeton.edu/~mudd/finding_aids/mathoral/pmc41.htm},
}

@article{tukey__john_w:8,
year={2000},
author={Anonymous},
title={{U}ntitled},
journal={IMS Bulletin},
pages={467-468},
volume={29},
year={2000},
}
\end{filecontents}

\begin{document}

\Name{Tukey, John W.} \Deceased
\ID{tukey__john_w}
\AltID{tukey__john}



\DOB{1915-06-16}
\DOD{2000-07-26}


\Homepage{http://en.wikipedia.org/wiki/John_Tukey}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=175155}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:tukey.john-wilder}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=15860}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/39015}{Microsoft Academic: Tukey, John W.}
\Profile{http://www.math.utah.edu/pub/bibnet/authors/t/tukey-john-w.bib}{biblio BibTeX compiled by Nelson Beebe}
\Profile{http://www.math.utah.edu/pub/bibnet/authors/t/tukey-john-w.html}{biblio HTML compiled by Nelson Beebe}


\subsection*{Education}
\Degree{1939}{Ph.D.}{Princeton University}[On Denumerability in Topology]<http://genealogy.math.ndsu.nodak.edu/id.php?id=15860>


\subsection*{Honors}
\Honor{1946}{IMS Fellow}
\Honor{1958}{Wald Lecturer}
\Honor{1960}{IMS President}
\Honor{1961}{National Academy of Sciences, Member}
\Honor{1962}{American Philosophical Society, Member}
\Honor{1964}{American Academy of Arts and Sciences, Fellow}
\Honor{1965}{Samuel S. Wilks Award}
\Honor{1967}{R. A. Fisher Lecturer}
\Honor{1973}{National Medal of Science}
\Honor{1985}{John von Neumann Lecturer}
\Honor{1991}{The Royal Society, Foreign Member}


\subsection*{Biographies}
\Biography{tukey__john_w:23}
\Biography{tukey__john_w:19}
\Biography{tukey__john_w:24}
\Biography{tukey__john_w:20}
\Biography{tukey__john_w:21}
\Biography{tukey__john_w:22}


\subsection*{Archive}
\Archive{tukey__john_w:25}


\subsection*{Oral History}
\OralHistory{tukey__john_w:26}


\subsection*{Obituary}
\Obituary{tukey__john_w:8}
\end{document}