% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for van Zwet, Willem R.

@article{van_zwet__willem_r:9,
year={1997},
author={Jure\v{c}kov\'{a}, J.},
title={{W}illem {R}utger van {Z}wet},
journal={IMS Bulletin},
pages={356-357},
volume={26},
}

@misc{van_zwet__willem_r:93972,
year={2001},
author={Anonymous},
title={{U}ntitled},
addendum={(2001). Curriculum vitae Willem Rutger van Zwet. In State of the Art in Probability and Statistics: Festschrift for Willem R. van Zwet (M. de Gunst, C. Klaassen, and A. van der Vaart, eds.). Lecture Notes-Monograph Series, Vol. 36, pp. xii-xiii. Institute of Mathematical Statistics, Beachwood, OH},
url={http://www.jstor.org/stable/4356101},
}

@misc{van_zwet__willem_r:295366,
year={2001},
author={Anonymous},
title={{U}ntitled},
addendum={van Eeden, C. (2001). The scientific family tree of Willem R. van Zwet. In State of the Art in Probability and Statistics: Festschrift for Willem R. van Zwet (M. de Gunst, C. Klaassen, and A. van der Vaart, eds.). Lecture Notes-Monograph Series, Vol. 36, pp. 244-254. Institute of Mathematical Statistics, Beachwood, OH},
url={http://www.jstor.org/stable/4356115},
}

@misc{van_zwet__willem_r:444153,
year={2001},
author={Anonymous},
title={{U}ntitled},
addendum={de Gunst, M., Klaassen, C., and van der Vaart, A., eds. (2001). State of the Art in Probability and Statistics: Festschrift for Willem R. van Zwet. Lecture Notes-Monograph Series, Vol. 36. Institute of Mathematical Statistics, Beachwood, OH, with portrait},
url={http://www.jstor.org/stable/i397611},
}
\end{filecontents}

\begin{document}

\Name{van Zwet, Willem R.}
\ID{van_zwet__willem_r}
\AltID{van_zwet__willem}



\Homepage{http://www.stat.unc.edu/faculty/vanz.html}


\subsection*{Profiles}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=187795}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:van-zwet.willem-r}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=68841}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/52739127}{Microsoft Academic: W. R. van Zwet}
\Profile{http://academic.research.microsoft.com/Author/52739128}{Microsoft Academic: Willem R. van Zwet}
\Profile{http://academic.research.microsoft.com/Author/54572944}{Microsoft Academic: W. R. van Zwet}
\Profile{http://academic.research.microsoft.com/Author/17914253}{Microsoft Academic: Willem R. van Zwet}
\Profile{http://academic.research.microsoft.com/Author/56967240}{Microsoft Academic: W. R. van Zwet}
\Profile{http://academic.research.microsoft.com/Author/26820246}{Microsoft Academic: W. R. van Zwet}


\subsection*{Education}
\Degree{1964}{Ph.D.}{Universiteit van Amsterdam}[Convex Transformations of Random Variables]<http://genealogy.math.ndsu.nodak.edu/id.php?id=68841>


\subsection*{Honors}
\Honor{1972}{IMS Fellow}
\Honor{1979}{The Royal Netherlands Academy of Arts and Sciences, Member}
\Honor{1986}{IMS Medallion Lecturer}
\Honor{1992}{IMS President}
\Honor{1992}{Wald Lecturer}


\subsection*{Biographies}
\Biography{van_zwet__willem_r:9}
\Biography{van_zwet__willem_r:93972}
\Biography{van_zwet__willem_r:295366}


\subsection*{Festschrift}
\Festschrift{van_zwet__willem_r:444153}
\end{document}