% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for van Dantzig, David

@article{van_dantzig__david:15,
year={1959},
author={Hemelrijk, J.},
title={{D}avid van {D}antzig{'}s statistical work},
journal={Synthese},
pages={335-351},
volume={11},
url={http://www.jstor.org/stable/20114311},
}

@misc{van_dantzig__david:189521,
year={1960},
author={Anonymous},
title={{U}ntitled},
addendum={Freudenthal, H. (1960). Levensbericht van D. van Dantzig (23 september 1900-22 juli 1959). In Jaarboek, 1959-1960, pp. 295-299. Royal Netherlands Academy of Arts and Sciences, Amsterdam, with portrait},
url={http://www.dwc.knaw.nl/DL/levensberichten/PE00004760.pdf},
}

@incollection{van_dantzig__david:17,
year={1978},
author={Hemelrijk, J.},
title={van {D}antzig, {D}avid},
pages={1211-1215},
crossref={booktitle:international-encyclopedia-of-statistics},
}

@incollection{van_dantzig__david:19,
year={2000},
author={O'Connor, J. J. and Robertson, E. F.},
title={{D}avid van {D}antzig},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Dantzig.html},
}

@incollection{van_dantzig__david:18,
year={2008},
author={Freudenthal, H.},
title={{D}antzig, {D}avid van},
pages={202-203},
volume={17},
crossref={booktitle:complete-dictionary-of-scientific-biography},
}

@article{van_dantzig__david:7,
year={1959},
author={Anonymous},
title={{D}avid {V}an {D}antzig},
journal={Amer. Statist.},
pages={41},
volume={13(4)]},
}

@article{van_dantzig__david:8,
year={1959},
author={Anonymous},
title={{I}n memoriam {P}rof. {D}r. {D}. van {D}antzig},
addendum={(in Dutch)},
journal={Nieuw. Arch. Wisk.},
pages={90},
volume={7},
}

@article{van_dantzig__david:9,
year={1959},
author={Anonymous},
title={{M}emorial to {D}avid van {D}antzig, van {D}antzig as a significist},
journal={Synthese},
pages={319-328},
volume={11},
url={http://www.jstor.org/stable/20114309},
}

@article{van_dantzig__david:10,
year={1959},
author={Koksma, J. F.},
title={{I}n memoriam {D}avid van {D}antzig, 23 {S}eptember 1900-22 {J}uly 1959},
journal={Synthese},
pages={329-334},
volume={11},
url={http://www.jstor.org/stable/20114310},
}

@article{van_dantzig__david:11,
year={1959},
author={Hemelrijk, J.},
title={memoriam {P}rof. {D}r. {D}. van {D}antzig},
addendum={in Dutch},
journal={Statistica Neerlandica},
pages={415-432},
volume={13},
}

@article{van_dantzig__david:12,
year={1960},
author={Hemelrijk, J.},
title={{T}he statistical work of {D}avid van {D}antzig (1900-1959)},
journal={Ann. Math. Statist.},
pages={269-275},
volume={31},
url={http://www.jstor.org/stable/2237946},
}

@article{van_dantzig__david:13,
year={1960},
author={Freudenthal, H.},
title={{I}n memoriam {D}avid van {D}antzig},
journal={Nieuw. Arch. Wisk.},
pages={57-73},
volume={8},
}
\end{filecontents}

\begin{document}

\Name{van Dantzig, David} \Deceased
\ID{van_dantzig__david}




\DOB{1900-09-23}
\DOD{1959-07-22}


\subsection*{Profiles}
\Profile{http://zbmath.org/authors/?q=ai:van-dantzig.david}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=49638}{Math. Genealogy}


\subsection*{Education}
\Degree{1931}{Ph.D.}{Rijksuniversiteit Groningen}[Studien over topologische algebra]<http://genealogy.math.ndsu.nodak.edu/id.php?id=49638>


\subsection*{Honors}
\Honor{1949}{The Royal Netherlands Academy of Arts and Sciences, Member}
\Honor{1953}{IMS Fellow}


\subsection*{Biographies}
\Biography{van_dantzig__david:15}
\Biography{van_dantzig__david:189521}
\Biography{van_dantzig__david:17}
\Biography{van_dantzig__david:19}
\Biography{van_dantzig__david:18}


\subsection*{Death Notice}
\DeathNotice{van_dantzig__david:7}


\subsection*{Memorials}
\InMemoriam{van_dantzig__david:8}
\InMemoriam{van_dantzig__david:9}
\InMemoriam{van_dantzig__david:10}
\InMemoriam{van_dantzig__david:11}
\InMemoriam{van_dantzig__david:12}
\InMemoriam{van_dantzig__david:13}
\end{document}