\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Varadhan, S. R. Srinivasa

@article{varadhan__s_r_srinivasa:21,
year={1996},
author={Anonymous},
title={1996 {S}teele {P}rizes},
journal={Notices Amer. Math. Soc.},
pages={1340-1347},
volume={43},
}

@article{varadhan__s_r_srinivasa:22,
year={1997},
author={Stroock, D.},
title={{N}omination for {S}rinivasa {S}. {R}. {V}aradhan},
journal={Notices Amer. Math. Soc.},
pages={955-957},
volume={44},
}

@misc{varadhan__s_r_srinivasa:736422,
year={2007},
author={Anonymous},
title={{U}ntitled},
}

@article{varadhan__s_r_srinivasa:24,
year={2007},
author={Anonymous},
title={{U}ntitled},
journal={IMS Bulletin},
pages={2},
volume={36(6)},
}

@article{varadhan__s_r_srinivasa:25,
year={2007},
author={Stroock, D. W.},
title={{S}. {R}. {S}. {V}aradhan: {D}an {S}troock{'}s tribute},
journal={IMS Bulletin},
pages={6-7},
volume={36(4)},
}

@article{varadhan__s_r_srinivasa:26,
year={2007},
author={Anonymous},
title={{A}bel {P}rize ceremony: {S}. {R}. {S}. {V}aradhan},
journal={IMS Bulletin},
pages={2},
volume={36(6)},
}

@misc{varadhan__s_r_srinivasa:27,
year={2007},
author={Lindstr\o{}m, T. L.},
title={{S}. {R}. {S}. {V}aradhan},
author={Lindstr\o{}m, {T}. {L}.},
title={S. {R}. {S}. {V}aradhan},
year={2007},
}

@article{varadhan__s_r_srinivasa:28,
year={2007},
author={Anonymous},
title={{V}aradhan receives 2007 {A}bel {P}rize},
journal={Notices Amer. Math. Soc.},
pages={738-739},
volume={54},
}

@article{varadhan__s_r_srinivasa:29,
year={2007},
author={Anonymous},
title={{A}bel {P}rize for 2007 to {P}rofessor {S}rinivasa {S}. {R}. {V}aradhan},
journal={Bernoulli News},
volume={14(1)},
}

@article{varadhan__s_r_srinivasa:30,
year={2008},
author={Raussen, M. and Skau, C.},
title={{I}nterview with {S}rinivasa {V}aradhan},
journal={Notices Amer. Math. Soc.},
pages={238-246},
volume={55},
}

@misc{varadhan__s_r_srinivasa:425974,
year={2008},
author={Bhatia, Rajendra},
title={{P}robability no longer a stepchild ({A} conversation with {S}. {R}. {S}. {V}aradhan).},
journal={Math. Intelligencer},
volume={30:2},
}

@incollection{varadhan__s_r_srinivasa:34,
year={2010},
author={O'Connor, J. J. and Robertson, E. F.},
title={{S}athamangalam {R}anga {I}yengar {S}rinivasa {V}aradhan},
note={MacTutor biography},
}

@article{varadhan__s_r_srinivasa:31,
year={2011},
author={Sznitman, A.-S.},
title={{S}. {R}. {S}. {V}aradhan: {N}ational {M}edal of {S}cience},
journal={IMS Bulletin},
pages={6-7},
volume={40(8)},
}

@article{varadhan__s_r_srinivasa:32,
year={2012},
author={Kehoe, E.},
title={{T}apia and {V}aradhan receive {N}ational {M}edal of {S}cience},
journal={Notices Amer. Math. Soc.},
pages={52-54},
volume={59},
}

@misc{varadhan__s_r_srinivasa:33,
year={2012},
author={Fraydoun Rezakhanlou (ed.)},
title={{S}. {R}. {S}rinivasa {V}aradhan},
address={Berkeley, CA},
publisher={Mathematical Sciences Publishers},
}
\end{filecontents}

\begin{document}

\Name{Varadhan, S. R. Srinivasa}


\subsection*{Education}
\Degree{1963}{Ph.D.}{Indian Statistical Institute, Calcutta}{Convolution Properties of Distributions on Topological Groups}{http://genealogy.math.ndsu.nodak.edu/id.php?id=33923}


\subsection*{Honors}
\Honor{1979}{IMS Medallion Lecturer}
\Honor{1979}{IMS Medallion Lecturer}
\Honor{1987}{Rietz Lecturer}
\Honor{1988}{American Academy of Arts and Sciences, Member}
\Honor{1988}{Third World Academy of Sciences, Fellow}
\Honor{1991}{IMS Fellow}
\Honor{1994}{Birkhoff Prize, AMS and SIAM}
\Honor{1995}{National Academy of Sciences, Member}
\Honor{1996}{Steele Prize, American Mathematical Society}
\Honor{1998}{The Royal Society, Fellow}
\Honor{2003}{IMS President}
\Honor{2004}{Indian Academy of Sciences, Honorary Fellow}
\Honor{2005}{Wald Lecturer}
\Honor{2007}{Abel Prize}
\Honor{2008}{Padma Bhushan}
\Honor{2009}{Norwegian Academy of Science and Letters, Foreign Member}
\Honor{2010}{National Medal of Science}


\subsection*{Biographies}
\Biography{varadhan__s_r_srinivasa:21}
\Biography{varadhan__s_r_srinivasa:22}
\Biography{varadhan__s_r_srinivasa:736422}
\Biography{varadhan__s_r_srinivasa:24}
\Biography{varadhan__s_r_srinivasa:25}
\Biography{varadhan__s_r_srinivasa:26}
\Biography{varadhan__s_r_srinivasa:27}
\Biography{varadhan__s_r_srinivasa:28}
\Biography{varadhan__s_r_srinivasa:29}
\Biography{varadhan__s_r_srinivasa:30}
\Biography{varadhan__s_r_srinivasa:425974}
\Biography{varadhan__s_r_srinivasa:34}
\Biography{varadhan__s_r_srinivasa:31}
\Biography{varadhan__s_r_srinivasa:32}
\Biography{varadhan__s_r_srinivasa:33}
\end{document}