\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Wilks, Samuel S.

@misc{wilks__samuel_s:20,
year={1965},
author={Anonymous},
title={{U}ntitled},
}

@article{wilks__samuel_s:21,
year={1965},
author={Stephan, F. F. and Tukey, J. W. and Mosteller, F. and Mood, A. M. and Hansen, M. H. and Simon, L. E. and Dixon, W. J.},
title={{S}amuel {S}. {W}ilks. {J}.},
journal={Amer. Statist.},
pages={939-966},
volume={60},
}

@incollection{wilks__samuel_s:22,
year={1968},
author={Mosteller, F.},
title={{W}ilks, {S}. {S}.},
crossref={booktitle:international-encyclopedia-of-the-social-sciences},
}

@incollection{wilks__samuel_s:24,
year={1978},
author={Mosteller, F.},
title={{W}ilks, {S}. {S}.},
pages={1250-1253},
crossref={booktitle:international-encyclopedia-of-statistics},
}

@misc{wilks__samuel_s:23,
year={197?},
author={Eisenhart, Churchill.},
title={{S}amuel {S}. {W}ilks and the {A}rmy {E}xperiment {D}esign {C}onference {S}eries},
}

@incollection{wilks__samuel_s:25,
year={1989},
author={Eisenhart, C.},
title={{S}. {S}. {W}ilks{'} {P}rinceton appointment, and statistics at {P}rinceton before {W}ilks},
pages={577-587},
crossref={booktitle:century-of-mathematics-in-america-part-iii},
}

@article{wilks__samuel_s:26,
year={1992},
author={Olkin, I.},
title={{A} conversation with {C}hurchill {E}isenhart},
note={see pp. 526-527},
journal={Statist. Sci.},
pages={512-530},
volume={7},
}

@inwebcollection{wilks__samuel_s:30,
year={1997},
author={O'Connor, J. J. and Robertson, E. F.},
title={{S}amuel {S}tanley {W}ilks, 1906-1964},
note={MacTutor biography},
}

@incollection{wilks__samuel_s:27,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@article{wilks__samuel_s:28,
year={2006},
author={David, H. A. and Morrison, D. F.},
title={{S}amuel {S}tanley {W}ilks (1906-1964)},
journal={Amer. Statist.},
pages={46-49},
volume={60},
}

@incollection{wilks__samuel_s:29,
year={2008},
author={Eisenhart, C.},
title={{W}ilks, {S}amuel {S}tanley},
pages={381-386},
volume={14},
crossref={booktitle:complete-dictionary-of-scientific-biography},
}

@misc{wilks__samuel_s:32,
year={Samuel Stanley},
author={Anonymous},
title={{S}. {S}. ({S}amuel {S}tanley) {W}ilks papers, 1940-1963},
note={Site includes biographical entry},
volume={Mss.{B}.{W}665},
booktitle={Library, {A}merican {P}hilosophical {S}ociety},
}

@misc{wilks__samuel_s:584469,
year={1964},
author={Anonymous},
title={{U}ntitled},
}

@article{wilks__samuel_s:11,
year={1964},
author={Cochran, W. G.},
title={{S}amuel {S}tanley {W}ilks, 1906-1964},
journal={Rev. Internat. Statist. Inst.},
pages={189-191},
volume={32},
}

@article{wilks__samuel_s:13,
year={1964},
author={Pearson, E. S.},
title={{O}bituary: {S}amuel {S}tanley {W}ilks, 1906-1964},
journal={J. Roy. Statist. Soc. Ser. A},
pages={597-599},
volume={127},
}

@article{wilks__samuel_s:14,
year={1964},
author={Gulliksen, H.},
title={{S}amuel {S}tanley {W}ilks, 1906-1964},
journal={Psychometrika},
pages={103-104},
volume={29},
}

@article{wilks__samuel_s:15,
year={1964},
author={Craig, C. C.},
title={{P}rofessor {S}amuel {S}. {W}ilks},
journal={Industrial Quality Control},
pages={41},
volume={20(12)},
}

@article{wilks__samuel_s:9,
year={1965},
author={Anderson, T. W.},
title={{S}amuel {S}tanley {W}ilks, 1906-1964},
journal={Ann. Math. Statist.},
pages={1-23},
volume={36},
}

@article{wilks__samuel_s:10,
year={1965},
author={Anderson, T. W.},
title={{T}he publications of {S}. {S}. {W}ilks},
journal={Ann. Math. Statist.},
pages={24-27},
volume={36},
}

@article{wilks__samuel_s:12,
year={year?},
author={Anonymous},
title={{U}ntitled},
publisher={American {S}tatistical {A}ssociation},
booktitle={Statisticians in {H}istory},
}
\end{filecontents}

\begin{document}

\subsection*{Education}
\Degree{1931}{Ph.D.}{University of Iowa}{On the Distributions of Statistics in Samples from a Normal Population of Two Variables with Matched Sampling of One Variable}{http://genealogy.math.ndsu.nodak.edu/id.php?id=34710}


\subsection*{Honors}
\Honor{1940}{IMS President}
\Honor{1948}{American Philosophical Society, Member}
\Honor{1959}{Rietz Lecturer}
\Honor{1963}{American Academy of Arts and Sciences, Fellow}
\Honor{before 1943}{IMS Fellow}


\subsection*{Biographies}
\Biography{wilks__samuel_s:20}
\Biography{wilks__samuel_s:21}
\Biography{wilks__samuel_s:22}
\Biography{wilks__samuel_s:24}
\Biography{wilks__samuel_s:23}
\Biography{wilks__samuel_s:25}
\Biography{wilks__samuel_s:26}
\Biography{wilks__samuel_s:30}
\Biography{wilks__samuel_s:27}
\Biography{wilks__samuel_s:28}
\Biography{wilks__samuel_s:29}


\subsection*{Archive}
\Archive{wilks__samuel_s:32}


\subsection*{Obituary}
\Obituary{wilks__samuel_s:584469}


\subsection*{Memorials}
\InMemoriam{wilks__samuel_s:11}
\InMemoriam{wilks__samuel_s:13}
\InMemoriam{wilks__samuel_s:14}
\InMemoriam{wilks__samuel_s:15}
\InMemoriam{wilks__samuel_s:9}
\InMemoriam{wilks__samuel_s:10}
\InMemoriam{wilks__samuel_s:12}
\end{document}