% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Wilks, Samuel S.

@misc{wilks__samuel_s:20,
year={1965},
author={Anonymous},
title={{U}ntitled},
addendum={Tukey, J. W. (1965). Samuel S. Wilks. Yearbook for 1964, American Philosophical Society, pp. 147-154},
}

@article{wilks__samuel_s:21,
year={1965},
author={Stephan, F. F. and Tukey, J. W. and Mosteller, F. and Mood, A. M. and Hansen, M. H. and Simon, L. E. and Dixon, W. J.},
title={{S}amuel {S}. {W}ilks. {J}.},
journal={Amer. Statist.},
pages={939-966},
volume={60},
url={http://www.jstor.org/stable/2283397},
}

@incollection{wilks__samuel_s:22,
year={1968},
author={Mosteller, F.},
title={{W}ilks, {S}. {S}.},
crossref={booktitle:international-encyclopedia-of-the-social-sciences},
url={http://www.encyclopedia.com/doc/1G2-3045001352.html},
}

@incollection{wilks__samuel_s:24,
year={1978},
author={Mosteller, F.},
title={{W}ilks, {S}. {S}.},
pages={1250-1253},
crossref={booktitle:international-encyclopedia-of-statistics},
}

@misc{wilks__samuel_s:23,
year={197?},
author={Eisenhart, Churchill.},
title={{S}amuel {S}. {W}ilks and the {A}rmy {E}xperiment {D}esign {C}onference {S}eries},
addendum={<abstract>A biography of Professor Samuel Stanley Wilks (1906-1964) of Princeton University, with particular attention to his early life, notes on the persons who shaped his professional development, review of his many facetted professional career, and his role in initiating and launching the U.S. Army's annual series of Conferences on the Design of Experiments in Army Research, Development, and Testing.</abstract>},
url={http://www.armyconference.org/50YEARS/Documents/Typed%20Papers/DOE20Eisenhart.pdf},
}

@incollection{wilks__samuel_s:25,
year={1989},
author={Eisenhart, C.},
title={{S}. {S}. {W}ilks{'} {P}rinceton appointment, and statistics at {P}rinceton before {W}ilks},
pages={577-587},
crossref={booktitle:century-of-mathematics-in-america-part-iii},
}

@article{wilks__samuel_s:26,
year={1992},
author={Olkin, I.},
title={{A} conversation with {C}hurchill {E}isenhart},
addendum={see pp. 526-527},
journal={Statist. Sci.},
pages={512-530},
volume={7},
url={http://www.jstor.org/stable/2246106},
}

@incollection{wilks__samuel_s:30,
year={1997},
author={O'Connor, J. J. and Robertson, E. F.},
title={{S}amuel {S}tanley {W}ilks, 1906-1964},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Wilks.html},
}

@incollection{wilks__samuel_s:27,
year={2006},
author={Anonymous},
title={{U}ntitled},
year={2006},
crossref={booktitle:encyclopedia-of-statistical-sciences},
}

@article{wilks__samuel_s:28,
year={2006},
author={David, H. A. and Morrison, D. F.},
title={{S}amuel {S}tanley {W}ilks (1906-1964)},
journal={Amer. Statist.},
pages={46-49},
volume={60},
}

@incollection{wilks__samuel_s:29,
year={2008},
author={Eisenhart, C.},
title={{W}ilks, {S}amuel {S}tanley},
pages={381-386},
volume={14},
crossref={booktitle:complete-dictionary-of-scientific-biography},
}

@book{wilks__samuel_s:32,
year={1940-1963},
author={Anonymous},
title={{S}. {S}. ({S}amuel {S}tanley) {W}ilks papers, 1940-1963},
addendum={Site includes biographical entry},
publisher={Library, American Philosophical Society},
volume={Mss.B.W665},
url={http://www.amphilsoc.org/mole/view?docId=ead/Mss.B.W665-ead.xml},
}

@misc{wilks__samuel_s:584469,
year={1964},
author={Anonymous},
title={{U}ntitled},
addendum={Dr. Samuel Wilks, Statistician, Dies. The New York Times, Mar. 9, 1964, p. 29},
}

@article{wilks__samuel_s:11,
year={1964},
author={Cochran, W. G.},
title={{S}amuel {S}tanley {W}ilks, 1906-1964},
journal={Rev. Internat. Statist. Inst.},
pages={189-191},
volume={32},
url={http://www.jstor.org/stable/1401992},
}

@article{wilks__samuel_s:13,
year={1964},
author={Pearson, E. S.},
title={{O}bituary: {S}amuel {S}tanley {W}ilks, 1906-1964},
journal={J. Roy. Statist. Soc. Ser. A},
pages={597-599},
volume={127},
url={http://www.jstor.org/stable/2343965},
}

@article{wilks__samuel_s:14,
year={1964},
author={Gulliksen, H.},
title={{S}amuel {S}tanley {W}ilks, 1906-1964},
journal={Psychometrika},
pages={103-104},
volume={29},
}

@article{wilks__samuel_s:15,
year={1964},
author={Craig, C. C.},
title={{P}rofessor {S}amuel {S}. {W}ilks},
journal={Industrial Quality Control},
pages={41},
volume={20(12)},
}

@article{wilks__samuel_s:9,
year={1965},
author={Anderson, T. W.},
title={{S}amuel {S}tanley {W}ilks, 1906-1964},
journal={Ann. Math. Statist.},
pages={1-23},
volume={36},
url={http://www.jstor.org/stable/2238071},
}

@article{wilks__samuel_s:10,
year={1965},
author={Anderson, T. W.},
title={{T}he publications of {S}. {S}. {W}ilks},
journal={Ann. Math. Statist.},
pages={24-27},
volume={36},
url={http://www.jstor.org/stable/2238071},
}

@article{wilks__samuel_s:12,
year={year?},
author={Anonymous},
title={{U}ntitled},
publisher={American {S}tatistical {A}ssociation},
booktitle={Statisticians in {H}istory},
url={http://www.amstat.org/about/statisticiansinhistory/bios/wilkssamuels.pdf},
}
\end{filecontents}

\begin{document}

\Name{Wilks, Samuel S.} \Deceased
\ID{wilks__samuel_s}
\AltID{wilks__samuel}



\DOB{1906-06-17}
\DOD{1964-03-07}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Samuel_S._Wilks}{Wikipedia}
\Profile{http://www.york.ac.uk/depts/maths/histstat/people/wilks.gif}{www.york.ac.uk}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=565625}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:wilks.samuel-s}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=34710}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/18722584}{Microsoft Academic: Wilks, S. S.}
\Profile{http://academic.research.microsoft.com/Author/23217221}{Microsoft Academic: Wilks, Samuel S.}


\subsection*{Education}
\Degree{1931}{Ph.D.}{University of Iowa}[On the Distributions of Statistics in Samples from a Normal Population of Two Variables with Matched Sampling of One Variable]<http://genealogy.math.ndsu.nodak.edu/id.php?id=34710>


\subsection*{Honors}
\Honor{1940}{IMS President}
\Honor{1948}{American Philosophical Society, Member}
\Honor{1959}{Rietz Lecturer}
\Honor{1963}{American Academy of Arts and Sciences, Fellow}
\Honor{before 1943}{IMS Fellow}


\subsection*{Biographies}
\Biography{wilks__samuel_s:20}
\Biography{wilks__samuel_s:21}
\Biography{wilks__samuel_s:22}
\Biography{wilks__samuel_s:24}
\Biography{wilks__samuel_s:23}
\Biography{wilks__samuel_s:25}
\Biography{wilks__samuel_s:26}
\Biography{wilks__samuel_s:30}
\Biography{wilks__samuel_s:27}
\Biography{wilks__samuel_s:28}
\Biography{wilks__samuel_s:29}


\subsection*{Archive}
\Archive{wilks__samuel_s:32}


\subsection*{Obituary}
\Obituary{wilks__samuel_s:584469}


\subsection*{Memorials}
\InMemoriam{wilks__samuel_s:11}
\InMemoriam{wilks__samuel_s:13}
\InMemoriam{wilks__samuel_s:14}
\InMemoriam{wilks__samuel_s:15}
\InMemoriam{wilks__samuel_s:9}
\InMemoriam{wilks__samuel_s:10}
\InMemoriam{wilks__samuel_s:12}
\end{document}