% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Wright, Sewall G.

@book{wright__sewall_g:14,
year={1978},
author={Provine, W. B.},
title={{S}ewall {W}right and {E}volutionary {B}iology},
publisher={Univ. Chicago Press},
}

@article{wright__sewall_g:15,
year={1990},
author={Hill, W. G.},
title={{S}ewall {W}right, 21 {D}ecember 1889-3 {M}arch 1988},
journal={Biogr. Mems. Fell. R. Soc.},
pages={569-579},
volume={36},
url={http://www.jstor.org/stable/770100},
}

@article{wright__sewall_g:16,
year={1994},
author={Crow, J. F.},
title={{S}ewall {W}right, {D}ecember 21, 1889-{M}arch 3, 1988},
journal={Biographical Memoirs},
pages={438-469},
publisher={National Academies Press},
url={http://books.nap.edu/html/biomems/swright.pdf},
}

@misc{wright__sewall_g:17,
year={2002},
author={Anonymous},
title={{U}ntitled},
addendum={Former Fellows of the Royal Society of Edinburgh, 1783-2002, p. 1016},
url={http://www.royalsoced.org.uk/cms/files/fellows/biographical_index/fells_indexp2.pdf},
}

@incollection{wright__sewall_g:19,
year={2005},
author={O'Connor, J. J. and Robertson, E. F.},
title={{S}ewall {G}reen {W}right},
addendum={MacTutor biography},
url={http://www-history.mcs.st-andrews.ac.uk/Biographies/Wright_Sewall.html},
}

@incollection{wright__sewall_g:18,
year={2008},
author={Skipper, R. A. Jr.},
title={{W}right, {S}ewall},
pages={356-363},
volume={25},
crossref={booktitle:complete-dictionary-of-scientific-biography},
}

@misc{wright__sewall_g:21,
year={year?},
author={Anonymous},
title={{S}ewall {W}right papers},
addendum={Site includes biographical entry},
volume={Mss.{B}.{W}665},
booktitle={Library, {A}merican {P}hilosophical {S}ociety},
url={http://www.amphilsoc.org/mole/view?docId=ead/Mss.Ms.Coll.60-ead.xml},
}

@misc{wright__sewall_g:22,
year={1988},
author={Wright, S.},
title={{I}nterviews with {W}ill {P}rovine},
addendum={Acc. 1988 2886ms, 53 cassette tapes. American Philosophical Society Recordings},
}
\end{filecontents}

\begin{document}

\Name{Wright, Sewall G.} \Deceased
\ID{wright__sewall_g}
\AltID{wright__sewall}

\DisplayName{Wright, Sewall}


\DOB{1889-12-21}
\DOD{1988-03-03}


\Homepage{http://psychology.wikia.com/wiki/Sewall_Wright}
\Homepage{http://www.users.muohio.edu/wrightse/}


\subsection*{Profiles}
\Profile{http://en.wikipedia.org/wiki/Sewall_Wright}{Wikipedia}
\Profile{http://www.ams.org/mathscinet/search/author.html?mrauthid=247467}{MathSciNet}
\Profile{http://zbmath.org/authors/?q=ai:wright.sewall}{zbMATH}
\Profile{http://genealogy.math.ndsu.nodak.edu/id.php?id=91602}{Math. Genealogy}
\Profile{http://academic.research.microsoft.com/Author/53917748}{Microsoft Academic: Sewall Wright}
\Profile{http://academic.research.microsoft.com/Author/42969323}{Microsoft Academic: Sewall Wright}
\Profile{http://academic.research.microsoft.com/Author/53917162}{Microsoft Academic: Sewall Wright}
\Profile{http://academic.research.microsoft.com/Author/53916994}{Microsoft Academic: Sewall Wright}
\Profile{http://academic.research.microsoft.com/Author/53917698}{Microsoft Academic: Sewall Wright}
\Profile{http://academic.research.microsoft.com/Author/47783193}{Microsoft Academic: Sewall Wright}
\Profile{http://academic.research.microsoft.com/Author/52177801}{Microsoft Academic: Sewall Wright}
\Profile{http://academic.research.microsoft.com/Author/49723951}{Microsoft Academic: Sewall Wright}
\Profile{http://academic.research.microsoft.com/Author/51939920}{Microsoft Academic: Sewall Wright}
\Profile{http://academic.research.microsoft.com/Author/12591401}{Microsoft Academic: SEWALL WRIGHT}


\subsection*{Education}
\Degree{1915}{Ph.D.}{Harvard University}<http://genealogy.math.ndsu.nodak.edu/id.php?id=91602>


\subsection*{Honors}
\Honor{1932}{American Philosophical Society, Member}
\Honor{1934}{National Academy of Sciences, Member}
\Honor{1948}{American Academy of Arts and Sciences, Fellow}
\Honor{1951}{The Royal Society of Edinburgh, Honorary Fellow}
\Honor{1951}{The Royal Society of Edinburgh, Honorary Foreign Fellow}
\Honor{1963}{The Royal Society, Foreign Member}
\Honor{1966}{National Medal of Science}
\Honor{before 1943}{IMS Fellow}


\subsection*{Biographies}
\Biography{wright__sewall_g:14}
\Biography{wright__sewall_g:15}
\Biography{wright__sewall_g:16}
\Biography{wright__sewall_g:17}
\Biography{wright__sewall_g:19}
\Biography{wright__sewall_g:18}


\subsection*{Archive}
\Archive{wright__sewall_g:21}


\subsection*{Oral History}
\OralHistory{wright__sewall_g:22}
\end{document}