\documentclass[letterpaper]{article}
\usepackage{imscv}
\addbibresource{imsBooks.bib}
\addbibresource{\jobname.bib}
\usepackage{filecontents}
\begin{filecontents}{\jobname.bib}
%% BibTeX file for Wright, Sewall G.

@book{wright__sewall_g:14,
year={1978},
author={Provine, W. B.},
title={{S}ewall {W}right and {E}volutionary {B}iology},
publisher={Univ. Chicago Press},
}

@article{wright__sewall_g:15,
year={1990},
author={Hill, W. G.},
title={{S}ewall {W}right, 21 {D}ecember 1889-3 {M}arch 1988},
journal={Biogr. Mems. Fell. R. Soc.},
pages={569-579},
volume={36},
}

@article{wright__sewall_g:16,
year={1994},
author={Crow, J. F.},
title={{S}ewall {W}right, {D}ecember 21, 1889-{M}arch 3, 1988},
journal={Biographical Memoirs},
pages={438-469},
publisher={National Academies Press},
}

@misc{wright__sewall_g:17,
year={2002},
author={Anonymous},
title={{U}ntitled},
}

@incollection{wright__sewall_g:19,
year={2005},
author={O'Connor, J. J. and Robertson, E. F.},
title={{S}ewall {G}reen {W}right},
note={MacTutor biography},
}

@incollection{wright__sewall_g:18,
year={2008},
author={Skipper, R. A. Jr.},
title={{W}right, {S}ewall},
pages={356-363},
volume={25},
crossref={booktitle:complete-dictionary-of-scientific-biography},
}

@misc{wright__sewall_g:21,
year={year?},
author={Anonymous},
title={{S}ewall {W}right papers},
note={Site includes biographical entry},
volume={Mss.{B}.{W}665},
booktitle={Library, {A}merican {P}hilosophical {S}ociety},
}

@misc{wright__sewall_g:22,
year={1988},
author={Anonymous},
title={{U}ntitled},
}
\end{filecontents}

\begin{document}

\Name{Wright, Sewall G.}
\DOB{1889-12-21}
\DOD{1988-03-03}


\subsection*{Education}
\Degree{1915}{Ph.D.}{Harvard University}{http://genealogy.math.ndsu.nodak.edu/id.php?id=91602}


\subsection*{Honors}
\Honor{1932}{American Philosophical Society, Member}
\Honor{1934}{National Academy of Sciences, Member}
\Honor{1948}{American Academy of Arts and Sciences, Fellow}
\Honor{1951}{The Royal Society of Edinburgh, Honorary Fellow}
\Honor{1951}{The Royal Society of Edinburgh, Honorary Foreign Fellow}
\Honor{1963}{The Royal Society, Foreign Member}
\Honor{1966}{National Medal of Science}
\Honor{before 1943}{IMS Fellow}


\subsection*{Biographies}
\Biography{wright__sewall_g:14}
\Biography{wright__sewall_g:15}
\Biography{wright__sewall_g:16}
\Biography{wright__sewall_g:17}
\Biography{wright__sewall_g:19}
\Biography{wright__sewall_g:18}


\subsection*{Archive}
\Archive{wright__sewall_g:21}


\subsection*{Oral History}
\OralHistory{wright__sewall_g:22}
\end{document}